% !TEX TS-program = lualatex
% !TEX encoding = UTF-8
\def\tenebrae{T}
\newcommand{\ifbook}[1]{#1}
\newcommand{\ifnotbook}[1]{}
%
\documentclass[12pt]{article} % use larger type; default would be 10pt
\usepackage{metalogo}
%\usepackage{hyperref}
\input{../tenebrae/inc_header}

\def\mypreface{
\thispagestyle{empty}
\begin{center}
\Huge Preface
\end{center}
\bigskip
All the chants found herein have been typeset based on those found in the Liber Usualis from 1961.
}

\makeatletter
\def\greversion{
	\gre@gregoriotexversion{}
}
\makeatother

\def\mycopyrightpage{
\thispagestyle{empty}
Tenebrae: \emph{newly typeset, based on \emph{The Liber Usualis}, edited by the Benedictines of Solesmes (Desclee Company, 1961). }

\bigskip

\noindent
First edition, 5 April 2014.

\noindent
Second edition, 10 March 2017.

\noindent
Third edition, 3 June 2019.

\noindent
Fourth edition, 21 April 2021.

\noindent
Fifth edition, 20 April 2022.

\bigskip

\noindent
Many thanks to Elie Roux for creating Gregorio and to all the people who contributed to the codebase and those who have transcribed the chants and made them available on http://gregobase.selapa.net.  I also extend my thanks to my brother Benjamin for his gabc tools <http://bbloomf.github.io/jgabc/psalmtone.html> which have been quite helpful.  And I must not forget to thank Sean Connolly who composed the responsories for Good Friday.

\bigskip

\hfill Albert Bloomfield

\hfill Cincinnati, Ohio

\bigskip

\noindent
http://asbloomf.github.io/gabc-chants


\vfill
	\noindent{}Typeset using \LuaLaTeX{}, Lilypond version 2.19.64, and Gregorio version \greversion{}

\bigskip\noindent
This work is free of known copyright restrictions.

\bigskip

\noindent
ISBN: 978-1-495-36449-5 (Amazon)\\
ISBN: 580-0-134-14737-5 (Lulu)

\pagebreak
}

\def\mytitlepage{
\thispagestyle{empty}
\vspace*{50pt}
\begin{center}{\addfontfeature{Numbers=Lining}%
\Huge \textsc{Tenebrae}
\vspace*{50pt}
\bigskip
\bigskip
\bigskip
}\end{center}
\pagebreak
}

\def\mytoc{%
\thispagestyle{empty}
%\vspace*{50pt}
\def\dotting{\xleaders\hbox to 12pt{\hfil.\hfil}\hfill}
%\def\wdotting{\leaders\hbox to 3em{\hfil.\hfil}\hfill}
\def\wdotting{\hfill}
\noindent
\huge\hfil Contents\hfil\\
\def\heading{Contents}

\vfil
\large
\noindent
\textsc{Maundy Thursday}\dotting \pageref{thursday-1}\\
\hspace*{4em}Resp. 1: In monte Olivéti\wdotting \pageref{in_monte_oliveti}, \pageref{in_monte_oliveti_poly}\\
\hspace*{4em}Resp. 2: Tristis est ánima mea\wdotting \pageref{tristis_est_anima_mea}, \pageref{tristis_est_anima_mea_poly}\\
\hspace*{4em}Resp. 3: Ecce vídimus eum\wdotting \pageref{resp3_ecce_vidimus}\\
\hspace*{2em}\textsc{2nd Nocturn}\dotting \pageref{thursday-2}\\
\hspace*{4em}Resp. 4: Amícus meus\wdotting \pageref{resp4_amicus_meus}\\
\hspace*{4em}Resp. 5: Judas mercátor\wdotting \pageref{resp5_judas_mercator}\\
\hspace*{4em}Resp. 6: Unus ex discípulis meis\wdotting \pageref{resp6_unus_ex_discipulis}\\
\hspace*{2em}\textsc{3rd Nocturn}\dotting \pageref{thursday-3}\\
\hspace*{4em}Resp. 7: Eram quasi agnus ínnocens\wdotting \pageref{resp7_eram_quasi_agnus}\\
\hspace*{4em}Resp. 8: Una hora\wdotting \pageref{resp8_una_hora}\\
\hspace*{4em}Resp. 9: Senióres pópuli\wdotting \pageref{resp9_seniores}\\
\hspace*{2em}\textsc{Lauds}\dotting \pageref{thursday-lauds}\\
\\
\vfil
\noindent
\textsc{Good Friday}\dotting \pageref{friday-1}\\
\hspace*{4em}Resp. 1: Omnes amíci mei\wdotting \pageref{omnes_amici_mei}, \pageref{omnes_amici_mei_poly}\\
\hspace*{4em}Resp. 2: Velum templi scissum est\wdotting \pageref{velum_templi_scissum_est}, \pageref{velum_templi_scissum_est_poly}\\
\hspace*{4em}Resp. 3: Vínea mea elécta\wdotting \pageref{resp3_vinea_mea}\\
\hspace*{2em}\textsc{2nd Nocturn}\dotting \pageref{friday-2}\\
\hspace*{4em}Resp. 4: Tamquam ad latrónem\wdotting \pageref{resp4_tamquam_ad_latronem}\\
\hspace*{4em}Resp. 5: Ténebræ factæ sunt\wdotting \pageref{resp5_tenebrae}\\
\hspace*{4em}Resp. 6: Animam meam diléctam\wdotting \pageref{resp6_animam_meam}\\
\hspace*{2em}\textsc{3rd Nocturn}\dotting \pageref{friday-3}\\
\hspace*{4em}Resp. 7: Tradidérunt me\wdotting \pageref{resp7_tradiderunt}\\
\hspace*{4em}Resp. 8: Jesum trádidit\wdotting \pageref{resp8_jesum_tradidit}\\
\hspace*{4em}Resp. 9: Caligavérunt óculi mei\wdotting \pageref{resp9_caligaverunt}\\
\hspace*{2em}\textsc{Lauds}\dotting \pageref{friday-lauds}\\
\\
\vfil
\pagebreak
\noindent
\textsc{Holy Saturday}\dotting \pageref{saturday-1}\\
\hspace*{4em}Resp. 1: Sicut ovis\wdotting \pageref{resp1_sicut_ovis}\\
\hspace*{4em}Resp. 2: Jerúsalem, surge\wdotting \pageref{resp2_jerusalem}\\
\hspace*{4em}Resp. 3: Plange quasi virgo\wdotting \pageref{resp3_plange}\\
\hspace*{2em}\textsc{2nd Nocturn}\dotting \pageref{saturday-2}\\
\hspace*{4em}Resp. 4: Recéssit pastor noster\wdotting \pageref{resp4_recessit_pastor}\\
\hspace*{4em}Resp. 5: O vos omnes\wdotting \pageref{o_vos_omnes}, \pageref{o_vos_omnes_poly}\\
\hspace*{4em}Resp. 6: Ecce quómodo móritur\wdotting \pageref{resp6_ecce_quomodo_moritur}\\
\hspace*{2em}\textsc{3rd Nocturn}\dotting \pageref{saturday-3}\\
\hspace*{4em}Resp. 7: Astitérunt reges terræ\wdotting \pageref{resp7_astiterunt_reges}\\
\hspace*{4em}Resp. 8: Æstimátus sum\wdotting \pageref{resp8_aestimatus_sum}\\
\hspace*{4em}Resp. 9: Sepúlto Dómino\wdotting \pageref{resp9_sepulto_domino}\\
\hspace*{2em}\textsc{Lauds}\dotting \pageref{saturday-lauds}\\
\\
\textsc{Tone for the Prophecy}\dotting \pageref{prophecytone}\\
\\
\textsc{Christus Factus Est}\dotting \pageref{christus_factus_est}\\
\\
\textsc{Orationes ante et post divinum officium}\dotting \pageref{orationes}\\
\vfil
\pagebreak
\normalsize
}


% here we begin the document
\begin{document}
\mytitlepage
\mycopyrightpage
\mytoc
%\mytitlepage % filler page

%\let\olditem=\item
%\def\item#1{\parbox{\hsize}{\olditem #1}}

%\input{lilypond/in_monte_oliveti-systems}

%\ifnum 1=2{
{\input{../Tenebrae-Thursday/nocturne1}}
{\input{../Tenebrae-Thursday/nocturne2}}
{\input{../Tenebrae-Thursday/nocturne3}}
{\input{../Tenebrae-Thursday/lauds}}
%}\fi
%\ifnum 1=2{
{\input{../Tenebrae-Friday/nocturne1}}
{\input{../Tenebrae-Friday/nocturne2}}
{\input{../Tenebrae-Friday/nocturne3}}
{\input{../Tenebrae-Friday/lauds}}
%}\fi
%\ifnum 1=2{
{\input{../Tenebrae-Saturday/nocturne1}}
{\input{../Tenebrae-Saturday/nocturne2}}
{\input{../Tenebrae-Saturday/nocturne3}}
{\input{../Tenebrae-Saturday/lauds}}
%}\fi

\pagebreak\cleartoleftpage{}
\thispagestyle{empty}
\def\heading{Tone for the Prophecy.}
\input{prophecyTone-main}

\pagebreak
\def\heading{Christus factus est.}
\label{christus_factus_est}
This can be sung in place of the the antiphon \emph{Christus factus est}.~at the end of Lauds on any of the three nights, singing the text indicated for that night.

\bigskip
\includelilypond{christus_factus_est-systems}

\pagebreak
\thispagestyle{empty}
\def\heading{Orationes ante et post divinum officium.}
\input{orationes-main}
%
\end{document}