% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt

\newcommand{\heading}{Christmas at II Vespers.}
\sloppy

\input{Christmas-Vespers2-psalms}

\newcommand{\chapter}{\dropcap{latin}{Multifáriam multísque modis olim Deus loquens pátribus in} pro\-\textbf{phé}\-tis~\dag{} novíssime diébus istis locútus est nobis in Fílio, quem constítuit hærédem ú\-\emph{ni\-ver}\-\textbf{só}\-rum,~* per quem fecit et \textbf{saé}\-cu\-la.}
\newcommand{\chaptertranslation}{God, who at sundry times and in divers manners spoke in times past to the fathers by the prophets, last of all in these days hath spoken to us by His Son, whom He hath appointed heir of all things, by whom also He made the world.}

\newcommand{\vrtex}{vrNotumFecitDominusSolemn}
\newcommand{\vtranslation}{The Lord hath made known, alleluia.}
\newcommand{\rtranslation}{His salvation, alleluia.}
\def\vrnospace{T}

\newcommand{\premag}{
\large
\setgrefactor{15}
}
%\newcommand{\premagtwo}{
%\setgrefactor{16}
%}
\newcommand{\magfontsize}{33}
\newcommand{\magantinitial}{H}
\newcommand{\maganttranslation}{This day Christ is born: this day the Saviour hath appeared: this day the Angels sing on earth, and the Archangels rejoice: this day the just exult, saying: Glory to God in the highest, alleluia.}
\def\magsolemn{T}
\def\magoneline{T}
\definemag{1}{g2}
\newcommand{\premagverses}{\greblockcustos\setgrefactor{15}
\normalsize
%\pagebreak
}

\newcommand{\collect}{Concéde, quaésumus omnípotens Deus~:~* ut nos Unigéniti tui nova per carnem Natívitas líberet; quos sub peccáti jugo vetústa sérvitus tenet. Per eúmdem Dóminum.}
\newcommand{\collecttranslation}{Grant, we beseech Thee, almighty God, that the new birth of Thine only-begotten Son in the flesh may set us free, who are held by the old bondage under the yoke of sin.  Through the same Jesus Christ our Lord.}

\definebenedicamusdomino{1}{2}

\input{../FullVespers}
