\newcommand{\chaptertext}{\dropcap{latin}{Beátus vir qui suffert} ten\-ta\-ti\-\textbf{ó}\-nem~:~\dag{} quóniam cum probátus fúerit, accípiet cor\-\emph{ó\-nam} \textbf{vi}\-tæ,~* quam repromísit Deus di\-li\-\textbf{gén}\-ti\-bus se.}
\newcommand{\chaptertranslation}{Blessed is the man that endureth temptation~: for when he hath been proved, he shall receive the crown of life, which God hath promised to them that love Him.}

\def\hymnlinetwo{\oldstylenums{1.}}
\def\hymntex{hy--deus_tuorum_militum_st_stephen--solesmes}
\def\hymninitial{D}
\def\hymntranslation{\item O Thou, of all thy warriors Lord,
thyself the crown and sure reward;
set us from sinful fetters free,
who sing thy Martyr's victory.

\item In selfish pleasure's worldly round
the taste of bitter gall he found;
but sweet to him was thy dear name,
and so to heavenly joys he came.

\item Right manfully his cross he bore,
and ran his race of torments sore;
for thee he poured his life away;
with thee he lives in endless day.

\item We, then, before thee bending low,
entreat thee, Lord, thy love to show
on this the day thy Martyr died,
who in thy saints art glorified!

\item To God the Father, with the Son,
and Holy Spirit, Three in One,
be praise and glory evermore,
as in th'eternity before.
}

\newcommand{\vrtex}{vrJustusUtPalmaFlorebit}
\newcommand{\vtranslation}{The just shall flourish like the palm-tree.}
\newcommand{\rtranslation}{And shall be multiplied as the cedar of Libanus.}

\newcommand{\maganttex}{an--qui_vult_venire--solesmes}
\newcommand{\magantinitial}{Q}
\newcommand{\maganttranslation}{If any man will come after me, let him deny himself and take up his cross and follow me.}
\def\magsolemn{T}
\definemag{1}{f}

\newcommand{\collect}{Deus, pro cujus Ecclésia gloriósus Póntifex Thomas gládiis impiórum occúbuit~:~\dag{} præsta, quǽsumus; ut omnes qui ejus implórant auxílium,~* petitiónis suæ salutárem consequántur efféctum. Per Dóminum nostrum.}
\newcommand{\collecttranslation}{O God, in the cause of whose Church, at the hands of wicked men, the glorious bishop Thomas laid down his life; grant, we beseech thee, that on all who plead to him for help, what they ask may be plenteously bestowed.}
