% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt

\newcommand{\heading}{Sunday within the Octave of Christmas at II Vespers.}
\sloppy

\input{Christmas-Vespers2-psalms}

\def\deusinadjutoriumsolemn{F}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Quanto témpore hæres párvulus est, nihil differt a servo, cum sit dóminus} {\textbf{óm}\-ni\-um~:~\dag{} sed sub tutóribus et ac\-\emph{tó\-ri}\-\textbf{bus} est,~* usque ad præfinítum tempus a \textbf{pá}tre.}}
\newcommand{\chaptertranslation}{Brethren, as long as the heir is a child, he differeth nothing from a servant, though he be lord of all: but is under tutors and governors until the time appointed by the father.}

\newcommand{\vrtex}{vrVerbumCaroFactumEst}
\newcommand{\vtranslation}{The Word was made flesh, alleluia.}
\newcommand{\rtranslation}{And dwelt among us, alleluia.}
\def\vrnospace{T}

\newcommand{\premag}{
\large
\setgrefactor{17}
\greblockcustos
}
%\newcommand{\premagtwo}{
%\setgrefactor{16}
%}
\newcommand{\magfontsize}{33}
\newcommand{\maganttex}{MagAnt-PuerJesus}
\newcommand{\magantinitial}{P}
\newcommand{\maganttranslation}{The Child Jesus advanced in age and wisdom before God and men.}
\def\magsolemn{F}
\def\magoneline{F}
\definemag{6}{F}
\newcommand{\premagverses}{\greblockcustos\setgrefactor{17}
\large
%\pagebreak
}

\newcommand{\collect}{Omnípotens sempitérne Deus, dírige actus nostros in beneplácito tuo~:~\dag{} ut in nómine dilécti Fílii tui,~* mereámur bonis opéribus abundáre.  Qui tecum vivit et regnat.}
\newcommand{\collecttranslation}{O almighty and everlasting God, direct our actions according to Thy good pleasure; that in the Name of Thy beloved Son we may deserve to abound in good words: Who with Thee liveth and reigneth.}

\definebenedicamusdomino{sunday}{}

\input{../inc_header}
\input{../FullVespers-test}
%\input{../FullVespers}
