% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{book} % use larger type; default would be 10pt
\usepackage{../definepsalms}
\usepackage{titlesec}
\usepackage{titletoc}
\usepackage{titleps}
\usepackage{letltxmacro}
\usepackage{changepage} % gives us \ifoddpage use [strict]
\usepackage{adjustbox}
\usepackage{amsfonts}

\LetLtxMacro{\oldneedspace}{\needspace}
\renewcommand{\needspace}[1]{
	\checkoddpage\ifoddpage\oldneedspace{#1}\else\fi
}
\newcommand{\raisedot}[1]{\adjustbox{raise=1pt,lap=-0.25pt}{#1}}
\newcommand{\pushdotleft}[1]{\adjustbox{lap=-0.5pt}{#1}}
\newcommand{\raisehepisemus}[1]{\adjustbox{raise=2pt}{#1}}
\newcommand{\pushhepisemusright}[1]{\adjustbox{lap=1pt}{#1}}
\newcommand{\pushhepisemusleft}[1]{\adjustbox{lap=-1pt}{#1}}
\newcommand{\lowerepisema}[1]{\adjustbox{raise=-1pt}{#1}}

\def\shouldprintwhointones{F}
\newcommand{\ifprintwhointones}[2]{\if\shouldprintwhointones T#1\else#2\fi}
\newcommand{\ifnotprintwhointones}[2]{\if\shouldprintwhointones T#2\else#1\fi}

%\usepackage{hyperref}
\newcommand{\phantomsection}{}

\setcounter{secnumdepth}{-1}

%\def\mywidth{6in}
%\def\myheight{9in}

\def\mywidth{8.5in}
\def\myheight{11in}

\input{../inc_header}
\setlength\headheight{0.25in+15pt}
\setlength\headsep{1pc}
\setlength\topskip{0pc}
\setlength\footskip{1pc}
\geometry{outer=0.4in,inner=0.85in,top=0pc+\headheight+\headsep,bottom=0.4in,twoside=true}
\newpagestyle{main}{
\sethead[\garamond{\thepage}][\garamond{\chaptertitle}][] % even
{}{\garamond{\sectiontitle}}{\garamond{\thepage}} % odd
\setfoot[][][] % even
{}{}{} % odd
}
\pagestyle{main}


\titleformat
{\section} % command
[block] % shape
{\thispagestyle{empty}\phantomsection
\large\addfontfeature{Numbers=Lining}\scshape} % format
{} % label
{} % sep
{
    % \rule{\textwidth}{1pt}
    % \vspace{1ex}
    \centering
} % before-code
%[
% \vspace{-0.5ex}%
% \rule{\textwidth}{0.3pt}
%] % after-code
 
 
\titleformat{\chapter}[block]
{\thispagestyle{empty}\phantomsection\Large\scshape\addfontfeature{Numbers=Lining}}
{}{0.5em}{\centering}
 
\titlespacing{\chapter}{0pt}{-\headheight}{1pc}
\titlespacing{\section}{0pt}{-\headheight}{1pc}
\titleclass{\chapter}{top}
\newcommand{\chapterbreak}{\clearpage}
\titleclass{\section}{top}
\newcommand{\sectionbreak}{\clearpage}

\contentsmargin{1pc}
\dottedcontents{chapter}[0pc]{}{2pc}{1pc}
\dottedcontents{section}[0pc]{}{0pc}{1pc}

\newcommand{\printnote}[1]{
	{\normalsize \emph{#1}}
}
\newcommand{\subtitle}[1]{
\begin{center}{
	{\addfontfeature{Numbers=Lining} \normalsize \emph{#1}}
}\end{center}
}

\newcommand{\printcollect}[2]{
	\ifx\undefined\begincollectcols\def\begincollectcols{\begin{parcolumns}[rulebetween]{2}}\fi
	\ifx\printcollectheading\undefined\def\printcollectheading{T}\fi
	\if\printcollectheading T
	\needspace{3\baselineskip}
	\begin{center}{\large Collect.}\end{center}
	\vspace{-0.4\baselineskip}
	\fi
	\begincollectcols
	\sloppy
	\prayer{#1}{#2}
	\end{parcolumns}
	\let\begincollectcols=\undefined
}
\newcommand{\psalmcolsoverride}[1][0]{
\def\beginpsalmcols{\begin{parcolumns}[rulebetween,colwidths={1=0.45\linewidth}]{2}}
\ifnum#1=2
\def\beginpsalmcols{\begin{parcolumns}[rulebetween,colwidths={1=0.46\linewidth}]{2}}
\fi
\ifnum#1=18
\def\beginpsalmcols{\begin{parcolumns}[rulebetween,colwidths={1=0.4425\linewidth}]{2}}
\fi
\ifnum#1=44
\def\beginpsalmcols{\begin{parcolumns}[rulebetween,colwidths={1=0.46\linewidth}]{2}}
\fi
\ifnum#1=71
\def\beginpsalmcols{\begin{parcolumns}[rulebetween,colwidths={1=0.4325\linewidth}]{2}}
\fi
\ifnum#1=84
\def\beginpsalmcols{\begin{parcolumns}[rulebetween,colwidths={1=0.5\linewidth}]{2}}
\fi
\ifnum#1=88
\def\beginpsalmcols{\begin{parcolumns}[rulebetween,colwidths={1=0.475\linewidth}]{2}}
\fi
}
\newcommand{\writeheading}[1]{
	\section{#1}
}

\sloppy
\begin{document}
\normalsize
\setgrefactor{15}
%\pagenumbering{roman}
%\frontmatter

%\pagenumbering{arabic}
%\mainmatter

\vspace*{5in}
\pagebreak

\chapter{The Office of Matins}

{
	\def\matins{\emph{Matins}}
	\def\lauds{\emph{Lauds}}
	\def\vespers{\emph{Vespers}}
	\def\compline{\emph{Compline}}
	\def\prime{\emph{Prime}}
	\def\terce{\emph{Terce}}
	\def\sext{\emph{Sext}}
	\def\none{\emph{None}}
	\def\th{\textsuperscript{th}}
	\def\rd{\textsuperscript{rd}}
	\setlength{\parindent}{0cm}
	\setlength{\parskip}{\baselineskip}
	The Liturgy of the Roman Rite is comprised of the rites and ceremonies as described in certain Liturgical books. This
	includes the Sacraments, various rites of blessings, but in particular of the Holy Sacrifice of the Mass and the Divine Office.

	The Divine Office consists of major and minor ``hours'' which are spread throughout the day. Minor hours such as \prime,
	\terce{}, \sext{} and \none{} take their name from the hour of the day. The day was considered to start at around 6:00~AM, so
	\prime{} would correspond to the first hour of the day – or 6:00~AM. \terce{}, the third hour, would be around 9:00~AM; \sext{}
	(6\th{} hour) at noon; and \none{} (9\th{} hour) at 3:00~PM. There is an additional minor hour – that of \compline{} – which is not
	specific to an hour in the day, but which is the final night prayer.

	Major hours are those of \matins{}, \lauds{}, and \vespers{}. \matins{} and \lauds{} are the hours typically associated with the early
	hours of the morning to sunrise, while \vespers{} is an evening prayer. Thus the complete cycle of hours of the Divine office would
	consist of \matins{}, \lauds{}, \prime{}, \terce{}, \sext{}, \none{}, \vespers{}, and \compline{}. In religious communities, \matins{} and \lauds{}
	may actually start around 2:30~AM; \prime{} at 6:00~AM; \terce{} at 9:00~AM; \sext{} at 12:00~noon; \none{} at 3:00~PM; \vespers{}
	around 5:30~PM; and finally \compline{} around 8:00~PM.

	The Divine Office constitutes a continuous outpouring of prayer from Church Militant to her Creator, and ideally spans the
	entirety of the Psalter within the course of a single week. The widespread incorporation of the psalms into the Liturgy of
	the Church demonstrates the connective thread from thousands of years of history – from the Old Testament before Christ
	all the way to the present – something that is also consistent in the Sacrifice of the Mass.

	The authorship of the Psalms is attributed to King David roughly 1000 years before Christ, although modern theories
	ascribe multiple authors over a period of time. Regardless of authorship, the psalms are wonderful songs of praise that
	span all the purposes of prayer – Adoration, Petition, Contrition, and Thanksgiving. Thus their prominence throughout all
	of the Liturgy – including as part of the Sacrifice of the Mass.

	The minor hours of the Office essentially consist of 3 antiphons and 3 psalms, with the antiphons sung before and after
	each psalm. The major hours of \lauds{} and \vespers{} essentially consist of 5 antiphons and 5 psalms (or sections of psalms),
	again with the antiphons sung before and after each psalm. Additionally, \lauds{} and \vespers{} have a hymn and a canticle
	(the \emph{Benedictus} in \lauds{}, the \emph{Magnificat} in \vespers{}). \matins{}, however, is very unique in terms of structure. It is subdivided
	into three nocturns, each consisting not only of 3 antiphons and 3 psalms, but also having 3 lessons and 3 responsories.
	There are additional elements – the hymn as with \lauds{} and \vespers{}, but also an \emph{Invitatory} at the very opening and the
	use of \emph{Te Deum} in lieu of the final responsory on feast days. \matins{} is by far the longest of all of the hours of the Office.

	As mentioned above, the day was divided according to hours from 6:00~AM to 6:00~PM. Thus the reference in the Gospel
	to the owner of the vineyard seeking laborers at the 3\rd{}, 6\th{}, 9\th{}, and 11\th{} hours. The Romans divided the hours of the night
	in similar fashion. The hours from 6:00~PM to 6:00~AM were divided into 4 watches of three hours each – and these were
	called ``vigils'', i.e. when the night watch was kept. This type of division is mimicked in dividing the office into the three
	nocturns.

	The term ``\matins{}'' corresponds to morning, specifically dawn, but the origin of the office had its usage during the night
	as the last part of the ``vigils''. \lauds{} (which take name from the use of the Laudate psalms) was the office actually
	associated with dawn. Somewhat surprisingly, there were periods of time in which \lauds{} preceded \matins{}, though the
	order today is \matins{} followed by \lauds{}, often with \lauds{} immediately following the office of \matins{}. For Christmas,
	however, the offices of \matins{} and \lauds{} are separated from one another. \matins{} is followed by the Midnight Mass after
	which \lauds{} would be celebrated\ldots{} followed by the Mass at Dawn, \prime{}, \terce{}, and then the Mass of the Day\ldots{} followed
	then in due course by the remainder of the office.
}

\chapter{Christmas at Matins.}

{

\centering{Pater noster.\hspace{1em}Ave María.\hspace{1em}Credo.}

}
\bigskip{}
\ifprintwhointones{\noindent\emph{Celebrant intones:}

\smallskip{}
}{}
{% Domine, labia mea aperies...
	\def\annot{\small \Vbar{}}
	\alsetinitialspacing{D}
	\includescore{DomineLabiaMea}

	\emph{\maltese{} on the lips}

	\translation[]{\Vbar{}~Lord, Thou shalt open my lips. \Rbar{}~And my mouth will announce Thy praise.}
	\bigskip
}

%\subtitle{Festal Tone}
\def\includelaustibi{F}
\ifprintwhointones{\noindent\emph{Celebrant intones:}

\smallskip{}
}{}
\printdeusinadjutorium{}

{
	
	\centering{Invitatory.}

}

\newcommand{\printinvitatoryant}{
	\def\annot{\small 4. g}
	\alsetinitialspacing{C}
	\includescore{in-ChristusNatusEst}	
}
\newcommand{\printinvitatoryantparttwo}{
	\includescore{in-VeniteAdoremus}
}

\ifprintwhointones{\noindent\emph{Cantors intone:}

}{}
{
	\printinvitatoryant{}

	\smallskip{}
	\emph{The Choir repeats~:} Christus natus est nobis~:~* Veníte, adorémus.
}

\bigskip{}
%\emph{The Cantors sing the verses together from the center; the Choir sings the antiphon after each verse as indicated.}
\ifprintwhointones{\noindent\emph{The Cantors:}

\smallskip{}
}{}
{
	\def\annot{\small Ps. 94.}
	\alsetinitialspacing{V}
	\includescore{in-ps94-1-Venite}

%	\bigskip
%	\printinvitatoryant{}
}

\bigskip
\ifprintwhointones{\noindent\emph{The Cantors:}

\smallskip
}{}
{
	\def\annot{\small \Vbar{} 2.}
	\alsetinitialspacing{Q}
	\includescore{in-ps94-2-QuoniamDeus}

%	\bigskip
%	\printinvitatoryantparttwo{}
}

{
	\bigskip
	\emph{\small In the following Verse, at the words \emph{Veníte, adorémus et procidámus ante Déum.} the Choir kneels.}

	\ifprintwhointones{\noindent\emph{The Cantors:}
	\smallskip

	}{}
	\def\annot{\small \Vbar{} 3.}
	\alsetinitialspacing{Q}
	\includescore{in-ps94-3-QuoniamIpsius}

%	\bigskip
%	\printinvitatoryant{}
}

\bigskip
\ifprintwhointones{\noindent\emph{The Cantors:}

\smallskip
}{}
{
	\def\annot{\small \Vbar{} 4.}
	\alsetinitialspacing{Q}
	\includescore{in-ps94-4-Hodie}

%	\bigskip
%	\printinvitatoryantparttwo{}
}

\bigskip
\ifprintwhointones{\noindent\emph{The Cantors:}

\smallskip
}{}
{
	\def\annot{\small \Vbar{} 5.}
	\alsetinitialspacing{Q}
	\includescore{in-ps94-5-Quadraginta}

%	\bigskip
%	\printinvitatoryant{}
}

\bigskip
\ifprintwhointones{\needspace{6\baselineskip}
\noindent\emph{The Cantors:}

}{}
{
	\def\annot{\small \Vbar{} 6.}
	\alsetinitialspacing{Q}
	\includescore{in-ps94-6-GloriaPatri}

%	\bigskip
%	\printinvitatoryantparttwo{}

	\bigskip
	\ifprintwhointones{\noindent\emph{The Cantors:}

	}{}
	\printinvitatoryant{}
}

% hymn

{
	\bigskip
	\ifprintwhointones{\noindent\emph{Celebrant intones, alternate verses between Choir 1 (Epistle Side) \& Choir 2 (Gospel Side).}

	}{}
	\printgabc{Hymn.}{1.}{J}{../Christmas/Hymn-JesuRedemptorOmnium}
}

\pagebreak
\def\alwaysrepeatantiphon{T}
{
	\input{nocturn1}
}

{
	\input{nocturn2}
}

{
 	\input{nocturn3}
}

\pagebreak

\end{document}

