{
\newcommand{\lessonwithhomily}[8][\normalsize]{
% 1 - optional for english translation
% 2 - latin first few words
% 3 - latin homily title
% 4 - latin homily start
% 5 - latin homily bulk
%
% 6 - english
% 7 - english homily title
% 8 - english homily
% requires columns environment
%\noindent%\selectlanguage{latin}
\colchunk{\dropcap{latin}{#2}

{

\centering{#3}

}

\dropcapnospace{latin}{#4} #5
} % \selectlanguage{american}
\colchunk{\dropcap[#1]{american}{#6}

{

\centering{#7}

}

\dropcapnospace{american}{#8}} \selectlanguage{latin}
}

  \writeheading{In the 3rd Nocturn}

  {
    \def\preant{\setgrefactor{17}\ifprintwhointones{\noindent\emph{First Cantor intones:}

    }{}
    \large}
    \def\preantafter{\setgrefactor{17}\large}
    \def\prepsalm{\normalsize}
    \def\anttranslation{He shall cry unto Me, alleluia, Thou art My Father, alleluia.}
    %\def\psalmtranslationsmall{T}
    %\def\prerepeatantiphon{\vspace{-20pt}}
    %\def\psalmclef{2}
    \printpsalm{1}{88}{6F}{an--ipse_invocabit_me--solesmes}{I}
  }

  {
    \bigskip
    \def\preant{\setgrefactor{17}\ifprintwhointones{\noindent\emph{Second Cantor intones:}

    }{}\large}
    \def\preantafter{\setgrefactor{17}\large}
    \def\prepsalm{\normalsize}
    \def\anttranslation{Let the heavens rejoice, and let the earth be glad before the Lord, for He cometh.}
    %\def\psalmtranslationsmall{T}
    %\def\prerepeatantiphon{\vspace{-20pt}}
    \printpsalm{2}{95}{4A}{an--laetentur_caeli--solesmes}{L}
  }

  {
    \bigskip
    \needspace{10\baselineskip}
    \def\preant{\setgrefactor{17}\ifprintwhointones{\noindent\emph{First Cantor intones:}

    }{}\large}
    \def\preantafter{\setgrefactor{17}\large}
    \def\prepsalm{\normalsize}
    \def\anttranslation{The Lord hath made known, alleluia, His salvation, alleluia.}
    %\def\psalmtranslationsmall{T}
    %\def\prerepeatantiphon{\vspace{-20pt}}
    \printpsalm{3}{97}{6F}{an--notum_fecit_dominus--solesmes}{N}
  }

  \bigskip
  {
    %\def\vrnospace{T}
    \printvr[\normalsize]{vr-IpseInvocabit}
    {He shall cry unto Me, alleluia.}
    {Thou art My Father, alleluia.}
  }

  {
    {Pater noster.}

    \smallskip
    \emph{Absolution.} A vínculis peccatórum nostrórum~* absólvat nos omnípotens et miséricors Dóminus. \Rbar{}~Amen.

    \emph{The Lector~:} Jube, domne, benedícere.

    \emph{Blessing.} Evangélica léctio~* sit nobis salus et protéctio. \Rbar{}~Amen.
  }

  \bigskip{}
  \needspace{16\baselineskip}
  {

    \centering{Léctio sancti Evangélii secúndum Lucam.}

  }

  {
    \hspace{10ex}{Lesson VII.}\hfill\emph{Chap. 2.}\hspace{10ex}

    \begin{parcolumns}[rulebetween,colwidths={1=.47\linewidth}]{2}
    \lessonwithhomily[\normalsize]{In illo témpore~: Exiit edíctum a Cǽsare Augústo, ut describerétur univérsus orbis. Et réliqua.}{Homilía sancti Gregórii Papæ.}
    {Quia, largiénte Dómino, Missárum solémnia ter hódie celebratúri sumus, loqui diu de evangélica lectióne non póssumus;}{sed nos áliquid vel bréviter dícere, Redemptóris nostri Natívitas ipsa compéllit. Quid est enim, quod nascitúro Dómino mundus descríbitur, nisi hoc, quod apérte monstrátur, quia ille apparébat in carne, ¿qui eléctos suos adscríberet in æter\emph{nitá}te? Quo contra de réprobis per prophétam dícitur~: Deleántur de libro vivéntium, et cum justis non scribántur. Qui bene étiam in Béthlehem náscitur~: Béthlehem quippe domus panis interpretátur. Ipse namque est, qui ait~: Ego sum panis vivus, qui de cælo descéndi. Locus ergo, in quo Dóminus náscitur, domus panis ántea vocátus est; quia futúrum profécto erat, ut ille ibi per matériam carnis apparéret, qui electórum mentes intérna satietáte refíceret. Qui non in paréntum domo, sed in via náscitur; ut profécto osténderet, quia per humanitátem suam, quam assúmpserat, quasi in aliéno nascebátur.
      Tu autem, Dómine, miserére nobis.
      \Rbar{}~Deo~grátias.}
    {At that time, a decree went out from Caesar Augustus, that the whole world should be enrolled. And so on.}
    {Homily by Pope St Gregory the Great.}
    {By God's mercy we are to say three Masses today, so that there is not much time left for preaching; but at the same time the occasion of the Lord's Birth-day itself obliges me to speak a few words. For why, when the Lord was to be born, was the world enrolled? Was it not to herald the appearing of Him by Whom the elect are enrolled in the book of life? Whereas the Prophet saith of the reprobate Let them be blotted out of the book of the living, and not be written with the righteous. It is well that the Lord is born in Bethlehem, for Bethlehem signifieth the House of Bread. He it was who said, I am the Living Bread, Which came down from heaven. The place then in which the Lord is born, was called the House of Bread before, for in the future He was truly to appear in the flesh by Whom the souls of the faithful are fed unto life eternal. He was born, not in His Parents' house, but away from home. And this is a mystery, showing that this our mortality into which He was born was not His home.
      But thou, O Lord, have mercy upon us.}
    \end{parcolumns}

  }

  {
    \bigskip
    \setgrefactor{17}
    \printgabc{7. Resp.}{7.}{B}{re--beata_viscera--solesmes}
    {
      \translationcolumns[\normalsize]{\Rbar{}~Blessed be the womb of the Virgin Mary, which bore the Son of the Eternal Father, and blessed be the paps which give suck to Christ our Lord.
      * Who today for the salvation of the world hath been pleased to be born of a Virgin.
      \Vbar{}~This day which is breaking is holy; O come, ye Gentiles, and worship the Lord.
      \Rbar{}~Who today for the salvation of the world hath been pleased to be born of a Virgin.}
    }
    \medskip

    \emph{The Lector~:} Jube, domne, benedícere.

    \emph{Blessing.} Per evangélica dicta~* deleántur nostra delícta. \Rbar{}~Amen.
  }

  \bigskip{}
  \needspace{16\baselineskip}
  {

    \centering{Léctio sancti Evangélii secúndum Lucam.}

  }

  {
    \hspace{10ex}{Lesson VIII.}\hfill\emph{Chap. 2. b.}\hspace{10ex}

    \begin{parcolumns}[rulebetween,colwidths={1=.45\linewidth}]{2}
    \lessonwithhomily[\normalsize]{In illo témpore~: Pastóres loquebántur ad ínvicem~: Transeámus usque Béthlehem, et videámus hoc verbum, quod factum est, quod Dóminus osténdit nobis. Et réliqua.}{Homilía sancti Ambrósii Epíscopi.}
    {Vidéte Ecclésiae surgéntis exórdium~: Christus náscitur, et pastóres vigiláre cœpérunt; qui Géntium greges,}{pécudum modo ante vivéntes, in caulam Dómini congregárent, ne quos spiritálium bestiárum per offúsas nóctium ténebras pateréntur incúrsus. Et bene pastóres vígilant, quos bonus pastor infórmat. Grex ígitur pópulus, nox sǽculum, pastóres sunt sacerdótes. Aut fortásse étiam ille sit pastor, cui dícitur~: Esto vígilans, et confírma. Quia non solum epíscopos ad tuéndum gregem Dóminus ordinávit, sed étiam Angelos destinávit.
      Tu autem, Dómine, miserére nobis.
      \Rbar{}~Deo~grátias.}
    {At that time, the shepherds said one to another: Let us go over to Bethlehem, and let us see this word that is come to pass, which the Lord hath showed to us. And so on.}
    {Homily by St Ambrose, Bishop of Milan.}
    {Behold the beginning of the Church. Christ is born, and the shepherds watch; shepherds, to gather together the scattered sheep of the Gentiles, and to lead them into the fold of Christ, that they might no longer be a prey to the ravages of spiritual wolves in the night of this world's darkness. And that shepherd is wide awake, whom the Good Shepherd stirreth up. The flock then is the people, the night is the world, and the shepherds are the Priests. And perhaps he is a shepherd to whom it is said, Be watchful and strengthen, for God hath ordained as the shepherds of His flock not Bishops only, but also Angels.
      But thou, O Lord, have mercy upon us.}
    \end{parcolumns}

  }

  {
    \bigskip
    \setgrefactor{17}
    \printgabc{8. Resp.}{8.}{V}{re--verbum_caro--solesmes}
    {
      \translationcolumns[\normalsize]{\Rbar{}~The Word was made flesh, and dwelt among us.
      * And we beheld His glory, the glory as of the Only-begotten of the Father, full of grace and truth.
      \Vbar{}~All things were made by Him, and without Him nothing was made.
      \Rbar{}~And we beheld His glory\dots{}
      \Vbar{}~Glory\dots{}
      \Rbar{}~And we beheld His glory\dots{}
      }
    }
    \medskip

    \emph{The Lector~:} Jube, domne, benedícere.

    \emph{Blessing.} Verba sancti Evangélii~* dóceat nos Christus Fílius Dei. \Rbar{}~Amen.
  }

  \bigskip{}
  \needspace{10\baselineskip}
  {

    \centering{Léctio sancti Evangélii secúndum Joánnem.}

  }

  {
    \hspace{10ex}{Lesson IX.}\hfill\emph{Chap. 1.}\hspace{10ex}

    \begin{parcolumns}[rulebetween,colwidths={1=.45\linewidth}]{2}
    \lessonwithhomily[\normalsize]{In princípio erat Verbum, et Verbum erat apud Deum, et Deus erat Verbum. Et réliqua.}%
    {Homilía sancti Augustíni Epíscopi.}%
    {Ne vile áliquid putáres quale consuevísti cogitáre, cum verba humána soléres audíre, audi quid cógites~: Deus erat Verbum. Exeat nunc néscio quis infidélis Ariánus et dicat quia Verbum Dei factum est.}{Quómodo potest fíeri, ut Verbum Dei factum sit, ¿quando Deus per Verbum fecit \emph{ómni}a? ¿Si et Verbum Dei ipsum factum est; per quod áliud verbum \emph{factum} est? Si hoc dicis, quia hoc est verbum Verbi, per quod factum est illud; ipsum dico ego únicum Fílium Dei. Si autem non dicis verbum Verbi, concéde non factum, per quod facta sunt ómnia. Non enim per seípsum fíeri pótuit, per quod facta sunt ómnia. Crede ergo Evangelístæ.
      Tu autem, Dómine, miserére nobis.
      \Rbar{}~Deo~grátias.}%
    {In the beginning was the Word, and the Word was with God, and the Word was God. And so on.}%
    {Homily by St Augustine, Bishop of Hippo.}%
    {Lest thou shouldest think all things mean, as thou art accustomed to think of things human, hear and digest this: The Word was God. Now perhaps there will come forward some Arian unbeliever, and say that the Word of God was created. How can the Word of God be created, when it was by the Word that God created all things? If the Word of God was created, by what other word was He created. If thou sayest that it was by the word of the Word Himself that He was created, I tell thee that God had no other, but One Only-begotten Son. But if thou say not that it was by the word of the Word Himself that He was created, thou art forced to confess that. He by Whom all things were made was not Himself made at all. Believe therefore the Evangelist.
      But thou, O Lord, have mercy upon us.}
    \end{parcolumns}

  }

  {
    \bigskip
    \setgrefactor{17}
    \printgabc{3.}{}{T}{../misc/te-deum-solemn}
    \medskip
  }

  \Vbar{}~Dóminus vobíscum. \Rbar{}~Et cum spíritu túo.
  \bigskip

  {

    \centering{Prayer.}

  }
  \smallskip

  {
    \begin{columns}
    \prayer{Concéde, quǽsumus, omnípotens Deus~:~† ut nos Unigéniti tui nova per carnem Natívitatis líberet;~* quos sub peccáti jugo vetústa sérvitus tenet. Per eúmdem Dóminum.}
           {Grant, we beseech thee, almighty God, that the new birth of thy Only-begotten Son as man may set us free, who are held by the old bondage under the yoke of sin. Through the same Lord.}
    \end{columns}
  }
  \bigskip{}

  \Vbar{}~Dóminus vobíscum. \Rbar{}~Et cum spíritu túo.

  \bigskip{}
  {
    \def\annot{\small{5.}}
    \alsetinitialspacing{B}
    \large
    \def\breakbeforeresp{T}
    \greblockcustos
    \includescore{../BenedicamusDomino/BenedicamusDomino_1classLauds}

    \bigskip{}

    \noindent{}Matins is concluded and preparations begin for midnight Mass.
  }
}