{
  \writeheading{In the 1st Nocturn}
  %\section{1st Nocturn}

  {
    \def\preant{\setgrefactor{17}\ifprintwhointones{\normalsize\vspace{-\baselineskip}\noindent\emph{Celebrant intones:}

    }{}
    \large}
    \def\preantafter{\setgrefactor{17}\large}
    \def\prepsalm{\normalsize}
    \def\prepsalmtext{\ifprintwhointones{\vspace{-\baselineskip}\noindent\emph{First Cantor intones:}

    }{}}
    \def\anttranslation{The Lord hath said unto me: Thou art My son, this day have I begotten thee.}
    %\def\psalmtranslationsmall{T}
    %\def\prerepeatantiphon{\vspace{-20pt}}
    \def\psalmclef{2}
    \printpsalm{1}{2}{8c}{an--dominus_dixit_ad_me--solesmes}{D}
  }

  {
    \bigskip
    \def\preant{\setgrefactor{17}\ifprintwhointones{\noindent\normalsize\emph{Second Cantor intones:}

    }{}
    \large}
    \def\preantafter{\setgrefactor{17}\large}
    \def\prepsalm{\normalsize}
    \def\anttranslation{The Lord is as a bridegroom coming out of his chamber.}
    %\def\psalmtranslationsmall{T}
    %\def\prerepeatantiphon{\vspace{-20pt}}
    \printpsalm{2}{18}{8G}{an--tamquam_sponsus--solesmes}{T}
  }

  {
    %\smallskip
    \def\preant{\setgrefactor{17}\ifprintwhointones{\noindent\normalsize\emph{First Cantor intones:}

    }{}
    \large}
    \def\preantafter{\setgrefactor{17}\large}
    \def\prepsalm{\normalsize}
    \def\anttranslation{Grace is poured into thy lips, therefore God hath blessed thee for ever.}
    %\def\psalmtranslationsmall{T}
    %\def\prerepeatantiphon{\vspace{-20pt}}
    \printpsalm{3}{44}{1a2}{an--diffusa_est--solesmes}{T}
  }

  \bigskip
  {
    %\def\vrnospace{T}
    \printvr[\normalsize]{vr-TamquamSponsus}
    {The Lord is as a bridegroom.}
    {Coming out of his chamber.}
  }

  {
    \bigskip
    \includescore[a]{paterNoster}

    \medskip
    \emph{Absolution.} Exáudi, Dómine Jesu Christe, preces servórum tuórum~\dag{} et miserére nobis,~* qui cum Patre et Spíritu Sancto vivis et regnas in sǽcula sæculórum. \Rbar{}~Amen.

    \emph{The Lector~:} Jube, domne, benedícere.

    \emph{Blessing.} Benedictióne perpétua~* benedícat nos Pater ætérnus. \Rbar{}~Amen.

    \emph{The following three Lessons of Isaias are read without a Title.}
  }

  \bigskip
  {
    \hspace{10ex}{Lesson I.}\hfill\emph{Chap. 9}\hspace{10ex}

    \begin{parcolumns}[rulebetween,colwidths={1=.44\linewidth}]{2}
    \lesson[\normalsize]{Primo témpore alleviáta est terra Zábulon, et terra Néphthali~: et novíssimo aggraváta est via maris trans Jordánem Galilǽæ géntium.
      Pópulus, qui ambulábat in ténebris, vidit lucem magnam~: habitántibus in regióne umbræ mortis, lux orta est eis.
      Multiplicásti gentem, et non magnificásti lætítiam. Lætabúntur coram te, sicut qui lætántur in messe, sicut exsúltant victóres, capta præda, quando dívidunt spólia.
      Jugum enim óneris ejus, et virgam húmeri ejus, et sceptrum exactóris ejus superásti sicut in die Mádian.
      Quia omnis violénta prædátio cum tumúltu, et vestiméntum mistum sánguine, erit in combustiónem, et cibus ignis.
      Párvulus enim natus est nobis, et fílius datus est nobis, et factus est principátus super húmerum ejus~: et vocábitur nomen ejus, Admirábilis, Consiliárius, Deus, Fortis, Pater futuri sǽculi, Princeps pacis.}{
      Tu autem, Dómine, miserére nobis.
      \Rbar{}~Deo~grátias.}
    {At the first time the land of Zabulon, and the land of Nephtali was lightly touched: and at the last the way of the sea beyond the Jordan of the Galilee of the Gentiles was heavily loaded.
      The people that walked in darkness, have seen a great light: to them that dwelt in the region of the shadow of death, light is risen.
      Thou hast multiplied the nation, and hast not increased the joy. They shall rejoice before thee, as they that rejoice in the harvest, as conquerors rejoice after taking a prey, when they divide the spoils.
      For the yoke of their burden, and the rod of their shoulder, and the sceptre of their oppressor thou hast overcome, as in the day of Median.
      For every violent taking of spoils, with tumult, and garment mingled with blood, shall be burnt, and be fuel for the fire.
      For a child is born to us, and a son is given to us, and the government is upon his shoulder: and his name shall be called, Wonderful, Counsellor, God the Mighty, the Father of the world to come, the Prince of Peace.
      But thou, O Lord, have mercy upon us.}
    \end{parcolumns}

  }

  {
    \bigskip
    \setgrefactor{17}
    \printgabc{1. Resp.}{5.}{H}{re--hodie_nobis_caelorum--solesmes}
    \medskip

    \emph{The Lector~:} Jube, domne, benedícere.

    \emph{Blessing.} Unigénitus Dei Fílius~* nos benedícere et adjuváre dignétur. \Rbar{}~Amen.
  }

  \bigskip
  {
    \hspace{10ex}{Lesson II.}\hfill\emph{Chap. 40}\hspace{10ex}

    \begin{parcolumns}[rulebetween,colwidths={1=.45\linewidth}]{2}
    \lesson[\normalsize]{Consolámini, consolámini, pópule meus, dicit Deus vester.}{
      Loquímini ad cor Jerúsalem, et advocáte eam~: quóniam compléta est malítia ejus, dimíssa est iníquitas illíus~: suscépit de manu Dómini duplícia pro ómnibus peccátis suis.
      Vox clamántis in desérto~: Paráte viam Dómini, rectas fácite in solitúdine sémitas Dei nostri.
      Omnis vallis exaltábitur, et omnis mons et collis humiliábitur~: et erunt prava in dirécta, et áspera in vias planas.
      Et revelábitur glória Dómini~: et vidébit omnis caro páriter quod os Dómini locútum est.
      Vox dicéntis~: Clama. Et dixi~: ¿Quid \emph{clamá}bo? Omnis caro fœnum, et omnis glória ejus quasi flos agri.
      Exsiccátum est fœnum, et cécidit flos~: quia spíritus Dómini sufflávit in eo. Vere fœnum est pópulus~:
      exsiccátum est fœnum, et cécidit flos~: Verbum autem Dómini nostri manet in ætérnum.
      Tu autem, Dómine, miserére nobis.
      \Rbar{}~Deo~grátias.}
    {Be comforted, be comforted, my people, saith your God.
      Speak ye to the heart of Jerusalem, and call to her: for her evil is come to an end, her iniquity is forgiven: she hath received of the hand of the Lord double for all her sins.
      The voice of one crying in the desert: Prepare ye the way of the Lord, make straight in the wilderness the paths of our God.
      Every valley shall be exalted, and every mountain and hill shall be made low, and the crooked shall become straight, and the rough ways plain.
      And the glory of the Lord shall be revealed, and all flesh together shall see, that the mouth of the Lord hath spoken.
      The voice of one, saying: Cry. And I said: What shall I cry? All flesh is grass, and all the glory thereof as the flower of the field.
      The grass is withered, and the flower is fallen, because the spirit of the Lord hath blown upon it. Indeed the people is grass:
      The grass is withered, and the flower is fallen: but the word of our Lord endureth for ever.
      But thou, O Lord, have mercy upon us.}
    \end{parcolumns}

  }

  {
    \bigskip
    \setgrefactor{17}
    \printgabc{2. Resp.}{8.}{H}{re--hodie_nobis_de_caelo--solesmes}
    \medskip

    \emph{The Lector~:} Jube, domne, benedícere.

    \emph{Blessing.} Spíritus Sancti grátia~* illúminet sensus et corda nostra. \Rbar{}~Amen.
  }

  \bigskip
  {
    \hspace{10ex}{Lesson III.}\hfill\emph{Chap. 52}\hspace{10ex}

    \begin{parcolumns}[rulebetween,colwidths={1=.46\linewidth}]{2}
    \lesson[\normalsize]{Consúrge, consúrge, indúere fortitúdine tua, Sion, indúere vestiméntis glóriæ tuæ, Jerúsalem, cívitas sancti~: quia non adjíciet ultra ut pertránseat per te incircumcísus et immúndus.}{
      Excútere de púlvere, consúrge, sede, Jerúsalem~: solve víncula colli tui, captíva fília Sion.
      Quia hæc dicit Dóminus~: Gratis venúmdati estis, et sine argénto redimémini.
      Quia hæc dicit Dóminus Deus~: In Ægýptum descéndit pópulus meus in princípio, ut colónus esset ibi~: et Assur absque ulla causa calumniátus est eum.
      Et nunc quid mihi est hic, dicit Dóminus, ¿quóniam ablátus est pópulus me\emph{us gra}tis? Dominatóres ejus iníque agunt, dicit Dóminus~: et júgiter tota die nomen meum blasphemátur.
      Propter hoc sciet pópulus meus nomen meum in die illa~: quia ego ipse qui loquébar, ecce adsum.
      Tu autem, Dómine, miserére nobis.
      \Rbar{}~Deo~grátias.}
    {Arise, arise, put on thy strength, O Sion, put on the garments of thy glory, O Jerusalem, the city of the Holy One: for henceforth the uncircumcised, and unclean shall no more pass through thee.
      Shake thyself from the dust, arise, sit up, O Jerusalem: loose the bonds from off thy neck, O captive daughter of Sion.
      For thus saith the Lord: You were sold gratis, and you shall be redeemed without money.
      For thus saith the Lord God: My people went down into Egypt at the beginning to sojourn there: and the Assyrian hath oppressed them without any cause at all.
      And now what have I here, saith the Lord: for my people is taken away gratis. They that rule over them treat them unjustly, saith the Lord, and my name is continually blasphemed all the day long.
      Therefore my people shall know my name in that day: for I myself that spoke, behold I am here.
      But thou, O Lord, have mercy upon us.}
    \end{parcolumns}

  }

  {
    \bigskip
    \setgrefactor{17}
    \printgabc{3. Resp.}{4.}{Q}{re--quem_vidistis--solesmes}
    \medskip
  }
}