{
  \writeheading{In the 2nd Nocturn}

  {
    \def\preant{\setgrefactor{17}\ifprintwhointones{\normalsize\vspace{-\baselineskip}\noindent\emph{Second Cantor intones:}

    }{}
    \large}
    \def\preantafter{\setgrefactor{17}\large}
    \def\prepsalm{\normalsize}
    \def\anttranslation{We have received thy mercy, O God, in the midst of thy temple.}
    %\def\psalmtranslationsmall{T}
    %\def\prerepeatantiphon{\vspace{-20pt}}
    %\def\psalmclef{2}
    \printpsalm{1}{47}{8G}{an--suscepimus_deus--solesmes}{S}
  }

  {
    \bigskip
    \needspace{10\baselineskip}
    \def\preant{\setgrefactor{17}\ifprintwhointones{\normalsize\vspace{-\baselineskip}\noindent\emph{First Cantor intones:}

    }{}
    \large}
    \def\preantafter{\setgrefactor{17}\large}
    \def\prepsalm{\normalsize}
    \def\anttranslation{In the Lord's days shall abundance of peace arise and flourish.}
    %\def\psalmtranslationsmall{T}
    %\def\prerepeatantiphon{\vspace{-20pt}}
    \printpsalm{2}{71}{3b}{an--orietur--solesmes}{O}
  }

  {
    \bigskip
    \def\preant{\setgrefactor{17}\ifprintwhointones{\noindent\emph{Second Cantor intones:}

    }{}
    \large}
    \def\preantafter{\setgrefactor{17}\large}
    \def\prepsalm{\normalsize}
    \def\anttranslation{Truth is sprung out of the earth, and justice hath looked down from heaven.}
    %\def\psalmtranslationsmall{T}
    %\def\prerepeatantiphon{\vspace{-20pt}}
    \printpsalm{3}{84}{8c}{an--veritas--solesmes}{V}
  }

  \bigskip
  {
    %\def\vrnospace{T}
    \printvr[\normalsize]{vr-Speciosus}
    {Thou art fairer than the children of men.}
    {Grace is poured into thy lips.}
  }

  {
    {Pater noster.}

    \smallskip
    \emph{Absolution.} Ipsíus píetas et misericórdia nos ádjuvet,~* qui cum Patre et Spíritu Sancto vivit et regnat in sǽcula sæculórum. \Rbar{}~Amen.

    \emph{The Lector~:} Jube, domne, benedícere.

    \emph{Blessing.} Deus Pater omnípotens,~* sit nobis propítius et clemens. \Rbar{}~Amen.
  }

  \bigskip{}
  {

    \centering{Sermo sancti Leónis Papæ.}

  }

  \smallskip
  {
    \noindent\hfil{Lesson IV.}\hfil

    \begin{parcolumns}[rulebetween,colwidths={1=.43\linewidth}]{2}
    \lesson[\normalsize]{Salvátor noster, dilectíssimi, hódie natus est~: gaudeámus. Neque enim fas est locum esse tristítiæ, ubi natális est vitæ~: quæ, consúmpto mortalitátis timóre, nobis íngerit de promíssa æternitáte lætítiam. Nemo ab hujus alacritátis participatióne secérnitur. Una cunctis lætítiæ commúnis est ratio~: quia Dóminus noster, peccáti mortísque destrúctor, sicut nullum a reátu líberum réperit, ita liberándis ómnibus venit. Exsúltet sanctus, quia appropínquat ad palmam~: gáudeat peccátor, quia invitátur ad véniam~: animétur Gentílis, quia vocátur ad vitam. Dei namque Fílius secúndum plenitúdinem témporis, quam divíni consílii inscrutábilis altitúdo dispósuit, reconciliándam auctóri suo natúram géneris assúmpsit humáni, ut invéntor mortis diábolus, per ipsam, quam vícerat, vincerétur.}{%
      Tu autem, Dómine, miserére nobis.
      \Rbar{}~Deo~grátias.}
    {Our Saviour, dearly beloved, today is born to us: Let us rejoice. It would be unlawful to be sad when it is the Birthday of Life; Which, for us mortals, taketh away the sting of death, and bringeth the bright promise of the eternal gladness. It would be unlawful for any man to refuse to partake in our rejoicing. All men have an equal share in the great cause of our joy, for, since our Lord, Who is the destroyer of sin and of death, findeth that all are bound under the condemnation, He is come to make all free. Rejoice, holy one, for thou drawest nearer to thy crown! Rejoice, O sinner, thy Saviour offereth thee pardon! Rejoice also, O thou Gentile, God calleth thee to life! For the Son of God, when the fulness of the time was come, which had been fixed by the unsearchable counsel of God, took upon Him the nature of man, that He might reconcile that nature to Him Who made it, and so the devil, the inventor of death, is conquered by that which he had conquered.
      But thou, O Lord, have mercy upon us.}
    \end{parcolumns}

  }

  {
    \bigskip
    \setgrefactor{17}
    \printgabc{4. Resp.}{3.}{O}{re--o_magnum_mysterium--solesmes}
    {
      \translationcolumns[\normalsize]{\Rbar{}~O great mystery, and wonderful sacrament, that beasts saw the new-born Lord lying in a manger.
      * Blessed is that Virgin whose womb was made meet to bear the Lord Christ.
      \Vbar{}~Hail, Mary, full of grace the Lord is with thee.
      \Rbar{}~Blessed is that Virgin whose womb was made meet to bear the Lord Christ.
    }
    \medskip

    \emph{The Lector~:} Jube, domne, benedícere.

    \emph{Blessing.} Christus perpétuæ~* det nobis gáudia vitæ. \Rbar{}~Amen.
  }

  \bigskip{}
  {
    \noindent\hfil{Lesson V.}\hfil

    \begin{parcolumns}[rulebetween,colwidths={1=.45\linewidth}]{2}
    \lesson[\normalsize]{In quo conflíctu pro nobis ínito, magno et mirábili æquitátis iure certátum est, dum omnípotens Dóminus cum sævíssimo hoste non in sua majestáte, sed in nostra congréditur humilitáte~: objíciens ei eámdem formam, eamdémque natúram, mortalitátis quidem nostræ partícipem, sed peccáti totíus expértem. Aliénum quippe ab hac nativitáte est, quod de ómnibus légitur~: Nemo mundus a sorde, nec infans, cujus est uníus diéi vita super terram. Nihil ergo in istam singulárem nativitátem de carnis concupiscéntia transívit, nihil de peccáti lege manávit. Virgo régia Davídicæ stirpis elígitur, quæ sacro gravidánda fœtu, divínam humanámque prolem prius concíperet mente, quam córpore. Et ne supérni ignára consílii ad inusitátos pavéret affátus, quod in ea operándum erat a Spíritu Sancto, collóquio discit angélico~: nec damnum credit pudóris, Dei Génitrix mox futúra.}{%
      Tu autem, Dómine, miserére nobis.
      \Rbar{}~Deo~grátias.}
    {When our Lord entered the field of battle against the devil, He did so with a great and wonderful fairness. Being Himself the Almighty, He laid aside His uncreated Majesty to fight with our cruel enemy in our weak flesh. He brought against him the very shape, the very nature of our mortality, yet without sin. His birth however was not a birth like other births for no other is born pure, nay, not the little child whose life endureth but a day on the earth. To His birth alone the throes of human passion had not contributed, in His alone no consequence of sin had had part. For His Mother was chosen a Virgin of the kingly lineage of David, and when she was to grow heavy with the sacred Child, her soul had already conceived Him before her body. She knew the counsel of God announced to her by the Angel, lest the unwonted events should alarm her. The future Mother of God knew what was to be wrought in her by the Holy Ghost, and that her modesty was absolutely safe.
      But thou, O Lord, have mercy upon us.}
    \end{parcolumns}

  }

  {
    \bigskip
    \setgrefactor{17}
    \printgabc{5. Resp.}{7.}{B}{re--beata_dei_genitrix--solesmes}
    {
      \translationcolumns[\normalsize]{\Rbar{}~Blessed is God's holy Mother, Mary, maiden undefiled.
      * Today she hath brought forth the Saviour of the world.
      \Vbar{}~Blessed is she that believed; for all those things are accomplished which were told her by the Lord.
      \Rbar{}~Today she hath brought forth the Saviour of the world.}
    }
    \medskip

    \emph{The Lector~:} Jube, domne, benedícere.

    \emph{Blessing.} Ignem sui amóris~* accéndat Deus in córdibus nostris. \Rbar{}~Amen.
  }

  \bigskip{}
  \needspace{8\baselineskip}
  {
    \noindent\hfil{Lesson VI.}\hfil

    \begin{parcolumns}[rulebetween,colwidths={1=.425\linewidth}]{2}
    \lesson[\normalsize]{Agámus ergo, dilectíssimi, grátias Deo Patri, per Fílium ejus in Spíritu Sancto~: qui propter multam caritátem suam, qua diléxit nos, misértus est nostri~: et cum essémus mórtui peccátis, convivificávit nos Christo, ut essémus in ipso nova creatúra, novúmque figméntum. Deponámus ergo véterem hóminem cum áctibus suis~: et adépti participatiónem generatiónis Christi, carnis renuntiémus opéribus. Agnósce, o Christiáne, dignitátem tuam~: et divínæ consors factus natúræ, noli in véterem vilitátem degéneri conversatióne redíre. Meménto, cujus cápitis et cujus córporis sis membrum. Reminíscere, quia érutus de potestáte tenebrárum, translátus es in Dei lumen et regnum.}{%
      Tu autem, Dómine, miserére nobis.
      \Rbar{}~Deo~grátias.}
    {Therefore, dearly beloved, let us give thanks to God the Father, through His Son, in the Holy Ghost: Who, for His great love wherewith He loved us, hath had mercy on us, and even when we were dead in sins, hath quickened us together with Christ, that in Him we might be a new creature, and a new workmanship. Let us then put off the old man with his deeds; and, having obtained a share in the Sonship of Christ, let us renounce the works of the flesh. Learn, O Christian, how great thou art, who hast been made partaker of the Divine nature, and fall not again by corrupt conversation into the beggarly elements above which thou art lifted. Remember Whose Body it is Whereof thou art made a member, and Who is its Head, Remember that it is He That hath delivered thee from the power of darkness and hath translated thee into God's light and kingdom.
      But thou, O Lord, have mercy upon us.}
    \end{parcolumns}

  }

  {
    \bigskip
    \setgrefactor{17}
    \printgabc{6. Resp.}{2.}{S}{re--sancta_et_immaculata--solesmes}
    {
      \translationcolumns[\normalsize]{\Rbar{}~O holy and immaculate virginity, I know not what praises I shall offer!
      * For Him Whom the heavens cannot contain, thou hast borne in thy breast.
      \Vbar{}~Blessed art thou amongst women, and blessed is the fruit of thy womb.
      \Rbar{}~For Him Whom the heavens cannot contain, thou hast borne in thy breast.
      \Vbar{}~Glory be to the Father, and to the Son, * and to the Holy Ghost.
      \Rbar{}~For Him Whom the heavens cannot contain, thou hast borne in thy breast.}
    }
\medskip
  }
}