\newcommand{\antonetex}{an--sacerdos_in_aeternum--solesmes}
\newcommand{\antoneinitial}{S}
\newcommand{\antonetranslation}{Christ the Lord, a Priest for ever according to the order of Melchisedech, offered bread and wine.}
\definepsalm{1}{109}{1}{f}

\newcommand{\anttwotex}{an--miserator_dominus--solesmes}
\newcommand{\anttwoinitial}{M}
\newcommand{\anttwotranslation}{The merciful Lord has given food to those who fear Him, as a memorial of His wonders.}
\definepsalm{2}{110}{2}{D}

\newcommand{\antthreetex}{an--calicem_salutaris--solesmes}
\newcommand{\antthreeinitial}{C}
\newcommand{\antthreetranslation}{I will take the chalice of salvation, and will sacrifice the sacrifice of praise.}
\definepsalm{3}{115}{3}{a2}

\newcommand{\antfourtex}{an--sicut_novellae--solesmes}
\newcommand{\antfourinitial}{S}
\newcommand{\antfourtranslation}{Like the young olive-branches let the Chrich's children be round about the table of the Lord.}
\definepsalm{4}{127}{4}{E}

\newcommand{\antfivetex}{an--qui_pacem_ponit--solesmes}
\newcommand{\antfiveinitial}{Q}
\newcommand{\antfivetranslation}{The Lord, who has set peace in the borders of the Church, fills us with the fatness of wheat.}
\definepsalm{5}{147}{5}{a}

\newcommand{\chaptertext}{\dropcap{latin}{Fratres~: Ego enim accépi a Dómino quod et trádidi} \textbf{vo}\-bis,~\dag{} quóniam Dóminus Jesus, in qua nocte tradebátur, accépit panem, et grátias agens fregit, et dixit~: Accípite, et manducáte~: hoc est corpus meum, quod pro vo\-\emph{bis tra}\-\textbf{dé}\-tur~:~* hoc fácite in meam commemorati\-\textbf{ó}\-nem.}
\newcommand{\chaptertranslation}{Brethren, I have rececived of the Lord, that which also I delivered to you, that the Lord Jesus, the same night in which He was betrayed, took bread, and giving thanks, broke, and said, Take ye and eat; this is My body which shall be delivered for you; this do for the commemoration of Me.}

\newcommand{\hymnlinetwo}{3.}
\newcommand{\hymntex}{hymn-PangeLingua}
\newcommand{\hymninitial}{P}
\newcommand{\hymntranslation}{
\item Of the glorious Body telling,
O my tongue, its mystery sing,
and the Blood, all price excelling,
which for this world's ransoming
in a noble womb once dwelling
He shed forth, the Gentiles' king.

\item Given for us, for us descending
of a Virgin to proceed,
man with man in converse blending
scattered He the Gospel seed;
till His sojourn drew to ending
which He closed in wondrous deed.

\item At the last great Supper seated,
circled by His brethren's band,
all the Law required completed
in the feast its statutes planned,
to the Twelve Himself He meted
for their food, with His own hand.

\item Word made flesh, by word He maketh
very bread His Flesh to be;
man for wine Christ's Blood partaketh;
and if senses fail to see,
faith alone the true heart waketh
to behold the mystery.

\item Therefore we, before it bending,
this great sacrament adore;
types and shadows have their ending
in the new rite evermore;
faith, our outward sense amending,
maketh good defects before.

\item Honour, laud, and praise addressing
to the Father and the Son,
might ascribe we, virtue, blessing;
and eternal benison;
Holy Ghost, from both progressing,
equal laud to thee be done.
Amen.
}


\newcommand{\vrtex}{vrPanemDeCaelo}
\newcommand{\vtranslation}{Thou didst give them bread from heaven, alleluia.}
\newcommand{\rtranslation}{Containing in itself all sweetness, alleluia.}

\newcommand{\collect}{Deus, qui nobis sub Sacraménto mirábili passiónis tuæ memóriam reliquísti~:~† tríbue, quǽsumus, ita nos córporis et sánguinis tui sacra mystéria venerári;~* ut redemptiónis tuæ fructum in nobis júgiter sentiámus.  Qui vivis et regnas.}
\newcommand{\collecttranslation}{O God, who in this wonderful sacrament hast left us a memorial of Thy passion~: grant us, we beseech Thee, so to reverence the sacred mysteries of Thy Body and Blood, that we may ever feel within us the fruit of Thy redemption.}
