% The title:
\vspace*{-50pt plus 20pt}
\begin{center}{\addfontfeature{Numbers=Lining}%
\huge \textsc{Holy Saturday}

\bigskip
\normalsize\textsc{At Matins}
}\end{center}
%\vspace{-2ex}
%\bigskip

%\emph{The altar should be completely bare, and without crucifix or candles.}

%!TEX root = Saturday
\def\officehour{Matins}
\def\matinsnocturn{1st Nocturn}
\writeheading{In the 1st Nocturn}
%
\large
%\printgabc{1. Ant.}{8. c.}{Z}{an--zelus_domus_tuae--solesmes}
\def\preant{\setgrefactor{17}\large}
\def\prepsalm{\normalsize\greblockcustos}
\def\anttranslation{In peace in the selfsame, I will both sleep and rest.}
\def\psalmtranslationsmall{T}
\printpsalm{1}{4}{8G}{an--in_pace_in_idipsum--solesmes}{I}
\let\prepsalm=\undefined
%
\def\preant{\setgrefactor{17}\large}
\def\prepsalm{\normalsize\greblockcustos}
\def\psalmtranslationsmall{T}
\def\anttranslation{He shall abide in thy tabernacle: he shall dwell on thy holy hill.}
\printpsalm{2}{14}{4E}{an--habitabit--solesmes}{H}
\let\prepsalm=\undefined
\bigskip
%
\def\preant{\setgrefactor{17}\large}
\def\psalmtranslationsmall{T}
\def\anttranslation{My flesh shall rest in hope.}
\def\prepsalm{\normalsize}
\printpsalm{3}{15}{7c}{an--caro_mea--solesmes}{C}
\let\prepsalm=\undefined

\bigskip
\printvr{vr-inPaceInIdipsum}
{I will lay me down in peace.}
{And rest.}

\bigskip
Pater noster. \emph{in silence.}

\setgrefactor{14}
\medskip
\hspace{10ex}\textsc{lesson i}\hfill\emph{Chap. 3, 22-30}\hspace{10ex}

{\normalsize
\printgabc{}{}{D}{lesson1-saturday-DeLamentationeJeremiae}

\translation[]{\emph{Heth}. It is by the mercies of the Lord that we are not consumed: because his commiserations have not failed.
\emph{Heth}. They are new every morning, great is thy faithfulness.
\emph{Heth}. The Lord is my portion, said my soul: therefore will I wait for him.
\emph{Teth}. The Lord is good to them that hope in him, to the soul that seeketh him.
\emph{Teth}. It is good to wait with silence for the salvation of God.
\emph{Teth}. It is good for a man, when he hath borne the yoke from his youth.
\emph{Jod}. He shall sit solitary, and hold his peace: because he hath taken it up upon himself.
\emph{Jod}. He shall put his mouth in the dust, if so be there may be hope.
\emph{Jod}. He shall give his cheek to him that striketh him, he shall be filled with reproaches.
Jerusalem! Jerusalem! Return unto the Lord thy God.}

\bigskip\bigskip

\printgabc{Resp. 1}{4.}{S}{re--sicut_ovis--solesmes}

\translation[]{\Rbar{}. He hath been brought as a sheep to the slaughter, and while he was evilly treated, he opened not his mouth: he was delivered up to death
* That he might give life his people.
\Vbar{}. He hath poured out his soul unto death, and he was numbered with the transgressors.
\Rbar{}. That he might give life his people.
}

%\begin{center}{\textsc{lesson ii}}\end{center}
\bigskip\bigskip
\hspace{10ex}\textsc{lesson ii}\hfill\emph{Chap. 4, 1-6}\hspace{10ex}

{\normalsize
\printgabc{}{}{A}{lesson2-saturday-Aleph}

\translation[]{\emph{Aleph}. How is the gold become dim, the finest colour is changed, the stones of the sanctuary are scattered in the top of every street?
\emph{Beth}. The noble sons of Sion, and they that were clothed with the best gold: how are they esteemed as earthen vessels, the work of the potter's hands?
\emph{Ghimel}. Even the sea monsters have drawn out the breast, they have given suck to their young: the daughter of my people is cruel, like the ostrich in the desert.
\emph{Daleth}. The tongue of the sucking child hath stuck to the roof of his mouth for thirst: the little ones have asked for bread, and there was none to break it unto them.
\emph{He}. They that were fed delicately have died in the streets; they that were brought up in scarlet have embraced the dung.
\emph{Vau}. And the iniquity of the daughter of my people is made greater than the sin of Sodom, which was overthrown in a moment, and hands took nothing in her.
Jerusalem! Jerusalem! Return unto the Lord thy God.}

\bigskip\bigskip
\bigskip\bigskip

\printgabc{Resp. 2}{5.}{J}{re--jerusalem--solesmes}

\translation[]{\Rbar{}. Arise, O Jerusalem, and put off thy garments of rejoicing: cover thee with sack-cloth and ashes:
* For the Saviour of Israel hath been slain in the midst of thee.
\Vbar{}. Let thy tears run down like a river day and night, and let not the apple of thine eye cease.
\Rbar{}. For the Saviour of Israel\dots}
}

\needspace{2\baselineskip}
\hspace{10ex}\textsc{lesson iii}\hfill\emph{Chap. 5, 1-11}\hspace{10ex}

{\normalsize
\printgabc{}{}{A}{lesson3-saturday-IncipitOratioJermiaeProphetae}

\translation[]{Remember, O Lord, what is come upon us: consider and behold our reproach.
Our inheritance is turned to aliens: our houses to strangers.
We are become orphans without a father: our mothers are as widows.
We have drunk our water for money: we have bought our wood.
We were dragged by the necks, we were weary and no rest was given us.
We have given our hand to Egypt, and to the Assyrians, that we might be satisfied with bread.
Our fathers have sinned, and are not: and we have borne their iniquities.
Servants have ruled over us: there was none to redeem us out of their hand.
We fetched our bread at the peril of our lives, because of the sword in the desert.
Our skin was burnt as an oven, by reason of the violence of the famine.
They oppressed the women in Sion, and the virgins in the cities of Juda.
Jerusalem! Jerusalem! Return unto the Lord thy God.}

\bigskip\bigskip

\needspace{6\baselineskip}
\printgabc{Resp. 3}{5.}{P}{re--plange--solesmes}
\translation[]{\Rbar{}. O my people! lament, like a virgin, howl, ye shepherds, in sack-cloth and ashes
* For the day of the Lord cometh, a mighty day and exceeding bitter.
\Vbar{}. Gird yourselves, ye Priests, and howl, ye ministers of the altar: cast up ashes upon you.
\Rbar{}. For the day\dots
\Rbar{}. O my people! lament\dots}
}