\item The mercies of the Lord I will sing for ever.
\item I will shew forth thy truth with my mouth to generation and generation.
\item For thou hast said: Mercy shall be built up for ever in the heavens: thy truth shall be prepared in them.
\item I have made a covenant with my elect: I have sworn to David my servant: Thy seed will I settle for ever.
\item And I will build up thy throne unto generation and generation.
\item The heavens shall confess thy wonders, O Lord: and thy truth in the church of the saints.
\item For who in the clouds can be compared to the Lord: or who among the sons of God shall be like to God?
\item God, who is glorified in the assembly of the saints: great and terrible above all them that are about him.
\item O Lord God of hosts, who is like to thee? thou art mighty, O Lord, and thy truth is round about thee.
\item Thou rulest the power of the sea: and appeasest the motion of the waves thereof.
\item Thou hast humbled the proud one, as one that is slain: with the arm of thy strength thou hast scattered thy enemies.
\item Thine are the heavens, and thine is the earth: the world and the fulness thereof thou hast founded: the north and the sea thou hast created.
\item Thabor and Hermon shall rejoice in thy name: thy arm is with might.
\item Let thy hand be strengthened, and thy right hand exalted: justice and judgment are the preparation of thy throne.
\item Mercy and truth shall go before thy face: blessed is the people that knoweth jubilation.
\item They shall walk, O Lord, in the light of thy countenance: and in thy name they shall rejoice all the day, and in thy justice they shall be exalted.
\item For thou art the glory of their strength: and in thy good pleasure shall our horn be exalted.
\item For our protection is of the Lord, and of our king the holy one of Israel.
\item Then thou spokest in a vision to thy saints, and saidst: I have laid help upon one that is mighty, and have exalted one chosen out of my people. 
\item I have found David my servant: with my holy oil I have anointed him.
\item For my hand shall help him: and my arm shall strengthen him.
\item The enemy shall have no advantage over him: nor the son of iniquity have power to hurt him.
\item And I will cut down his enemies before his face; and them that hate him I will put to flight.
\item And my truth and my mercy shall be with him: and in my name shall his horn be exalted.
\item And I will set his hand in the sea; and his right hand in the rivers.
\item He shall cry out to me: Thou art my father: my God, and the support of my salvation.
\item And I will make him my firstborn, high above the kings of the earth.
\item I will keep my mercy for him for ever: and my covenant faithful to him.
\item And I will make his seed to endure for evermore: and his throne as the days of heaven.
\item And if his children forsake my law, and walk not in my judgments: 
\item If they profane my justices: and keep not my commandments:
\item I will visit their iniquities with a rod: *and their sins with stripes. 
\item But my mercy I will not take away from him: nor will I suffer my truth to fail.
\item Neither will I profane my covenant: and the words that proceed from my mouth I will not make void.
\item Once have I sworn by my holiness: I will not lie unto David: his seed shall endure for ever.
\item And his throne as the sun before me: and as the moon perfect for ever, and a faithful witness in heaven.