\item Lord, thou hast proved me, and known me: thou hast known my sitting down, and my rising up.
\item Thou hast understood my thoughts afar off: my path and my life thou hast searched out.
\item And thou hast foreseen all my ways: for there is no speech on my tongue.
\item Behold, O Lord, thou hast known all things, the last and those of old: thou hast formed me, and hast laid thy hand upon me.
\item Thy knowledge is become wonderful to me: it is high, and I cannot reach to it.
\item Whither shall I go from thy spirit? or whither shall I flee from thy face?
\item If I ascend into heaven, thou art there: if I descend into hell, thou art present.
\item If I take my wings early in the morning, and dwell in the uttermost parts of the sea:
\item Even there also shall thy hand lead me: and thy right hand shall hold me.
\item And I said: Perhaps darkness shall cover me: and night shall be my light in my pleasures.
\item But darkness shall not be dark to thee, and night shall be light as the day: the darkness thereof, and the light thereof are alike to thee.
\item For thou hast possessed my reins: thou hast protected me from my mother’s womb.
\item I will praise thee, for thou art fearfully magnified: wonderful are thy works, and my soul knoweth right well.
\item My bone is not hidden from thee, which thou hast made in secret: and my substance in the lower parts of the earth.
\item Thy eyes did see my imperfect being, and in thy book all shall be written: days shall be formed, and no one in them
\item But to me thy friends, O God, are made exceedingly honourable: their principality is exceedingly strengthened.
\item I will number them, and they shall be multiplied above the sand: I rose up and am still with thee.
\item If thou wilt kill the wicked, O God: ye men of blood, depart from me:
\item Because you say in thought: They shall receive thy cities in vain.
\item Have I not hated them, O Lord, that hated thee: and pined away because of thy enemies?
\item I have hated them with a perfect hatred: and they are become enemies to me.
\item Prove me, O God, and know my heart: examine me, and know my paths.
\item And see if there be in me the way of iniquity: and lead me in the eternal way.