\item When Israel went out of Egypt, the house of Jacob from a barbarous people:
\item Judea made his sanctuary, Israel his dominion.
\item The sea saw and fled: Jordan was turned back.
\item The mountains skipped like rams, and the hills like the lambs of the flock.
\item What ailed thee, O thou sea, that thou didst flee: and thou, O Jordan, that thou wast turned back?
\item Ye mountains, that ye skipped like rams, and ye hills, like lambs of the flock?
\item At the presence of the Lord the earth was moved, at the presence of the God of Jacob:
\item Who turned the rock into pools of water, and the stony hill into fountains of waters.
\item Not to us, O Lord, not to us; but to thy name give glory.
\item For thy mercy, and for thy truth's sake: lest the gentiles should say: Where is their God?
\item But our God is in heaven: he hath done all things whatsoever he would.
\item The idols of the gentiles are silver and gold, the works of the hands of men.
\item They have mouths and speak not: they have eyes and see not.
\item They have ears and hear not: they have noses and smell not.
\item They have hands and feel not: they have feet and walk not: neither shall they cry out through their throat.
\item Let them that make them become like unto them: and all such as trust in them.
\item The house of Israel hath hoped in the Lord: he is their helper and their protector.
\item The house of Aaron hath hoped in the Lord: he is their helper and their protector.
\item They that fear the Lord hath hoped in the Lord: he is their helper and their protector.
\item The Lord hath been mindful of us, and hath blessed us.
\item He hath blessed the house of Israel: he hath blessed the house of Aaron.
\item He hath blessed all that fear the Lord, both little and great.
\item May the Lord add blessings upon you: upon you, and upon your children.
\item Blessed be you of the Lord, who made heaven and earth.
\item The heaven of heaven is the Lord's: but the earth he has given to the children of men.
\item The dead shall not praise thee, O Lord: nor any of them that go down to hell.
\item But we that live bless the Lord: from this time now and for ever.