\item Lord, remember David, and all his meekness.
\item How he swore to the Lord, he vowed a vow to the God of Jacob:
\item If I shall enter into the tabernacle of my house: if I shall go up into the bed wherein I lie:
\item If I shall give sleep to my eyes, or slumber to my eyelids,
\item Or rest to my temples: until I find out a place for the Lord, a tabernacle for the God of Jacob.
\item Behold we have heard of it in Ephrata: we have found it in the fields of the wood.
\item We will go into his tabernacle: we will adore in the place where his feet stood.
\item Arise, O Lord, into thy resting place: thou and the ark, which thou hast sanctified.
\item Let thy priests be clothed with justice: and let thy saints rejoice. 
\item For thy servant David's sake, turn not away the face of thy anointed.
\item The Lord hath sworn truth to David, and he will not make it void: of the fruit of thy womb I will set upon thy throne.
\item If thy children will keep my covenant, and these my testimonies which I shall teach them:
\item Their children also for evermore shall sit upon thy throne. 
\item For the Lord hath chosen Sion: he hath chosen it for his dwelling.
\item This is my rest forever: here will I dwell, for I have chosen it.
\item Blessing I will bless her widow: I will satisfy her poor with bread.
\item I will clothe her priests with salvation: and her saints shall rejoice with exceeding great joy.
\item There will I bring forth a horn to David: I have prepared a lamp for my anointed.
\item His enemies I will clothe with confusion: but upon him shall my sanctification flourish.