\item My heart hath uttered a good word; I speak my works to the King.
\item My tongue is the pen of a scrivener that writeth swiftly.
\item Thou art beautiful above the sons of men: grace is poured abroad in thy lips; therefore hath God blessed thee for ever.
\item Gird thy sword upon thy thigh, O thou most mighty.
\item With thy comeliness and thy beauty set out, proceed prosperously, and reign.
\item Because of truth and meekness and justice: and thy right hand shall conduct thee wonderfully.
\item Thy arrows are sharp: under thee shall people fall, into the hearts of the king's enemies.
\item Thy throne, O God, is for ever and ever: the sceptre of thy kingdom is a sceptre of uprightness.
\item Thou hast loved justice, and hated iniquity: therefore God, thy God, hath anointed thee with the oil of gladness above thy fellows.
\item Myrrh and stacte and cassia perfume thy garments, from the ivory houses: out of which the daughters of kings have delighted thee in thy glory.
\item The queen stood on thy right hand, in gilded clothing; surrounded with variety.
\item Hearken, O daughter, and see, and incline thy ear: and forget thy people and thy father's house.
\item And the king shall greatly desire thy beauty; for he is the Lord thy God, and him they shall adore.
\item And the daughters of Tyre with gifts, yea, all the rich among the people, shall entreat thy countenance.
\item All the glory of the king's daughter is within, in golden borders, clothed round about with varieties.
\item After her shall virgins be brought to the king: her neighbours shall be brought to thee.
\item They shall be brought with gladness and rejoicing: they shall be brought into the temple of the king.
\item Instead of thy fathers, sons are born to thee: thou shalt make them princes over all the earth.
\item They shall remember thy name throughout all generations.
\item Therefore shall people praise thee for ever; yea, for ever and ever.