\item The heavens shew forth the glory of God, * and the firmament declareth the work of his hands.
\item Day to day uttereth speech, * and night to night sheweth knowledge.
\item There are no speeches nor languages, * where their voices are not heard.
\item Their sound hath gone forth into all the earth: * and their words unto the ends of the world.
\item He hath set his tabernacle in the sun: * and he, as a bridegroom coming out of his bride chamber,
\item Hath rejoiced as a giant to run the way: * his going out is from the end of heaven,
\item And his circuit even to the end thereof: * and there is no one that can hide himself from his heat.
\item The law of the Lord is unspotted, converting souls: * the testimony of the Lord is faithful, giving wisdom to little ones.
\item The justices of the Lord are right, rejoicing hearts: * the commandment of the Lord is lightsome, enlightening the eyes.
\item The fear of the Lord is holy, enduring for ever and ever: * the judgments of the Lord are true, justified in themselves.
\item More to be desired than gold and many precious stones: * and sweeter than honey and the honeycomb.
\item For thy servant keepeth them, * and in keeping them there is a great reward.
\item Who can understand sins? from my secret ones cleanse me, O Lord: * and from those of others spare thy servant.
\item If they shall have no dominion over me, then shall I be without spot: * and I shall be cleansed from the greatest sin.
\item And the words of my mouth shall be such as may please: * and the meditation of my heart always in thy sight.
\item O Lord, my helper, * and my redeemer.