\newcommand{\antonetex}{Ant1-BeataEs}
\newcommand{\antoneinitial}{B}
\newcommand{\antonetranslation}{Blessed art thou, O Virgin Mary, who didst bear the Creator of all things.}
\definepsalm{1}{109}{8}{c}

\newcommand{\anttwotex}{Ant2-Genuisti}
\newcommand{\anttwoinitial}{G}
\newcommand{\anttwotranslation}{Thou didst give birth to Him who made thee, and yet remain a Virgin forever.}
\definepsalm{2}{112}{6}{F}

\newcommand{\antthreetex}{Ant3-CumEssemParvula}
\newcommand{\antthreeinitial}{C}
\newcommand{\antthreetranslation}{When I was little, I pleased the Most High, and from my womb, I have brought forth God and man.}
\definepsalm{3}{121}{1}{f}

\newcommand{\antfourtex}{Ant4-Benedicta}
\newcommand{\antfourinitial}{B}
\newcommand{\antfourtranslation}{Daughter, thou art blessed of the Lord: for by thee, we have partaken of the fruit of life.}
\definepsalm{4}{126}{7}{c2}

\newcommand{\antfivetex}{Ant5-VideruntEam}
\newcommand{\antfiveinitial}{V}
\newcommand{\antfivetranslation}{The daughters of Sion saw her and called her blessed, and the queens praised her.}
\definepsalm{5}{147}{7}{a}

\newcommand{\chaptertext}{\dropcap{latin}{Qui creávit me, requiévit in tabernáculo} \textbf{me}\-o~:~\dag{} et dixit mihi~: In Jac\emph{ob} \emph{in}\-\textbf{há}\-bi\-ta,~* et in eléctis meis mitte ra\-\textbf{dí}\-ces.}
\newcommand{\chaptertranslation}{He that made me rested in my tabernacle and said to me: Let thy dwelling be in Jacob, and take root among mine elect.}

\newcommand{\hymnlinetwo}{1.}
\newcommand{\hymntex}{Hymn-AveMarisStella}
\newcommand{\hymninitial}{A}
\newcommand{\hymntranslation}{
\item Hail, thou star of ocean,
Portal of the sky,
Ever-Virgin Mother,
Of the Lord most High.

\item Oh! by Gabriel's Ave
Uttered long ago
Eva's name reversing
Peace confirm below.

\item Break the captive's fetters,
Light on blindness pour
Chase all evils from us,
Every bliss implore.

\item Show thyself a Mother,
Offer Him our sighs,
Who for us incarnate
Did not thee despise.

\item Virgin all excelling,
Passing meek and lowly,
Freed from guilt, preserve us
Blameless chaste and holy.

\item Still as on we journey
Help our weak endeavour
Till we gaze on Jesus
And rejoice for ever.

\item Father, Son, and Spirit,
Three in One confessing.
Give we equal glory,
Equal praise and blessing.
Amen.

%Child divine who barest,
%Mother, ever-virgin,
%Heaven's portal fairest.
%
%\item Taking that sweet Ave
%Erst by Gabriel spoken,
%Eva's name reversed,
%Be of peace the token.
%
%\item Break the sinners' fetters,
%Light to blind restoring,
%All our ills dispelling,
%Every boon imploring.
%
%\item Show thyself a mother
%In thy supplication;
%He will hear who chose thee
%At his incarnation.
%
%\item Maid all maids excelling,
%Passing meek and lowly,
%Win for sinners pardon,
%Make us chaste and holy.
%
%\item As we onward journey
%Aid our weak endeavour,
%Till we gaze on Jesus
%And rejoice forever.
%
%\item Father, Son, and Spirit,
%Three in One confessing,
%Give we equal glory
%Equal praise and blessing.
%Amen.%\grechangestaffsize{15}
}

\newcommand{\vrtex}{vrBenedictaTuInMulieribus}
\newcommand{\vtranslation}{Blessed art thou amongst women.}
\newcommand{\rtranslation}{And blessed is the fruit of thy womb.}

\newcommand{\collect}{Deus, qui de beátæ Maríæ Vírginis útero Verbum tuum, Angelo nuntiánte, carnem suscípere voluísti~:~\dag{} præsta supplícibus tuis; ut, qui vere eam Genitrícem Dei crédimus,~* ejus apud te intercessiónibus adjuvémur. Per eúmdem.}
\newcommand{\collecttranslation}{O God, who didst will that Thy Word should take flesh, at the message of an Angel, in the womb of the Blessed Virgin Mary, grant to Thy suppliant people, that we who believe her to be truly the Mother of God, may be helped by her intercession with Thee.  Through the same.}

\def\magsolemn{T}
