\item Let us sing to the Lord: for he is gloriously magnified, the horse and the rider he hath thrown into the sea.
\item The Lord is my strength and my praise, and he is become salvation to me:
\item He is my God and I will glorify him: the God of my father, and I will exalt him.
\item The Lord is as a man of war, Almighty is his name. Pharao’s chariots and his army he hath cast into the sea:
\item His chosen captains are drowned in the Red Sea. The depths have covered them, they are sunk to the bottom like a stone.
\item Thy right hand, O Lord, is magnified in strength: thy right hand, O Lord, hath slain the enemy. And in the multitude of thy glory thou hast put down thy adversaries:
\item Thou hast sent thy wrath, which hath devoured them like stubble. And with the blast of thy anger the waters were gathered together:
\item The flowing water stood, the depths were gathered together in the midst of the sea.
\item The enemy said: I will pursue and overtake, I will divide the spoils, my soul shall have its fill:
\item I will draw my sword, my hand shall slay them.
\item Thy wind blew and the sea covered them: they sunk as lead in the mighty waters.
\item Who is like to thee, among the strong, O Lord? who is like to thee, glorious in holiness, terrible and praiseworthy, doing wonders?
\item Thou stretchedst forth thy hand, and the earth swallowed them. In thy mercy thou hast been a leader to the people which thou hast redeemed:
\item And in thy strength thou hast carried them to thy holy habitation.
\item Nations rose up, and were angry: sorrows took hold on the inhabitants of Philisthiim.
\item Then were the princes of Edom troubled, trembling seized on the stout men of Moab: all the inhabitants of Chanaan became stiff.
\item Let fear and dread fall upon them, in the greatness of thy arm:
\item Let them become unmovable as a stone, until thy people, O Lord, pass by: until this thy people pass by, which thou hast possessed.
\item Thou shalt bring them in, and plant them in the mountain of thy inheritance, in thy most firm habitation which thou hast made, O Lord;
\item Thy sanctuary, O Lord, which thy hands have established. The Lord shall reign for ever and ever.
\item For Pharao went in on horseback with his chariots and horsemen into the sea: and the Lord brought back upon them the waters of the sea:
\item But the children of Israel walked on dry ground in the midst thereof.