\item I said: In the midst of my days I shall go to the gates of hell:
\item I sought for the residue of my years. I said: I shall not see the Lord God in the land of the living.
\item I shall behold man no more, nor the inhabitant of rest.
\item My generation is at an end, and it is rolled away from me, as a shepherd’s tent.
\item My life is cut off, as by a weaver: whilst I was yet but beginning, he cut me off: from morning even to night thou wilt make an end of me.
\item I hoped till morning, as a lion so hath he broken all my bones:
\item From morning even to night thou wilt make an end of me. I will cry like a young swallow, I will meditate like a dove:
\item My eyes are weakened looking upward:
\item Lord, I suffer violence, answer thou for me. What shall I say, or what shall he answer for me, whereas he himself hath done it?
\item I will recount to thee all my years in the bitterness of my soul.
\item O Lord, if man’s life be such, and the life of my spirit be in such things as these, thou shalt correct me, and make me to live. Behold in peace is my bitterness most bitter:
\item But thou hast delivered my soul that it should not perish, thou hast cast all my sins behind thy back.
\item For hell shall not confess to thee, neither shall death praise thee: nor shall they that go down into the pit, look for thy truth.
\item The living, the living, he shall give praise to thee, as I do this day: the father shall make thy truth known to the children.
\item O Lord, save me, and we will sing our psalms all the days of our life in the house of the Lord.
