\item O God my God, look upon me: why hast thou forsaken me? Far from my salvation are the words of my sins.
\item O my God, I shall cry by day, and thou wilt not hear: and by night, and it shall not be reputed as folly in me.
\item But thou dwellest in the holy place, the praise of Israel. 
\item In thee have our fathers hoped: they have hoped, and thou hast delivered them.
\item They cried to thee, and they were saved: they trusted in thee, and were not confounded.
\item But I am a worm, and no man: the reproach of men, and the outcast of the people.
\item All they that saw me have laughed me to scorn: they have spoken with the lips, and wagged the head.
\item He hoped in the Lord, let him deliver him: let him save him, seeing he delighteth in him.
\item For thou art he that hast drawn me out of the womb: my hope from the breasts of my mother. I was cast upon thee from the womb.
\item From my mother’s womb thou art my God, depart not from me.
\item For tribulation is very near: for there is none to help me.
\item Many calves have surrounded me: fat bulls have besieged me.
\item They have opened their mouths against me, as a lion ravening and roaring.
\item I am poured out like water; and all my bones are scattered.
\item My heart is become like wax melting in the midst of my bowels.
\item My strength is dried up like a potsherd, and my tongue hath cleaved to my jaws: and thou hast brought me down into the dust of death.
\item For many dogs have encompassed me: the council of the malignant hath besieged me.
\item They have dug my hands and feet. They have numbered all my bones.
\item And they have looked and stared upon me. They parted my garments amongst them; and upon my vesture they cast lots.
\item But thou, O Lord, remove not thy help to a distance from me; look towards my defence.
\item Deliver, O God, my soul from the sword: my only one from the hand of the dog.
\item Save me from the lion’s mouth; and my lowness from the horns of the unicorns.
\item I will declare thy name to my brethren: in the midst of the church will I praise thee.
\item Ye that fear the Lord, praise him: all ye the seed of Jacob, glorify him.
\item Let all the seed of Israel fear him: because he hath not slighted nor despised the supplication of the poor man.
\item Neither hath he turned away his face from me: and when I cried to him he heard me.
\item With thee is my praise in a great church: I will pay my vows in the sight of them that fear him.
\item The poor shall eat and shall be filled: and they shall praise the Lord that seek him: their hearts shall live for ever and ever.
\item All the ends of the earth shall remember, and shall be converted to the Lord:
\item And all the kindreds of the Gentiles shall adore in his sight.
\item For the kingdom is the Lord’s; and he shall have dominion over the nations.
\item All the fat ones of the earth have eaten and have adored: all they that go down to the earth shall fall before him.
\item And to him my soul shall live: and my seed shall serve him.
\item There shall be declared to the Lord a generation to come: and the heavens shall shew forth his justice to a people that shall be born, which the Lord hath made.
