\item The Lord is my light and my salvation, whom shall I fear?
\item The Lord is the protector of my life: of whom shall I be afraid?
\item Whilst the wicked draw near against me, to eat my flesh.
\item My enemies that trouble me, have themselves been weakened, and have fallen.
\item If armies in camp should stand together against me, my heart shall not fear.
\item If a battle should rise up against me, in this will I be confident.
\item One thing I have asked of the Lord, this will I seek after; that I may dwell in the house of the Lord all the days of my life.
\item That I may see the delight of the Lord, and may visit his temple.
\item For he hath hidden me in his tabernacle; in the day of evils, he hath protected me in the secret place of his tabernacle.
\item He hath exalted me upon a rock: and now he hath lifted up my head above my enemies.
\item I have gone round, and have offered up in his tabernacle a sacrifice of jubilation: I will sing, and recite a psalm to the Lord.
\item Hear, O Lord, my voice, with which I have cried to thee: have mercy on me and hear me.
\item My heart hath said to thee: My face hath sought thee: thy face, O Lord, will I still seek.
\item Turn not away thy face from me; decline not in thy wrath from thy servant.
\item Be thou my helper, forsake me not; do not thou despise me, O God my Saviour.
\item For my father and my mother have left me: but the Lord hath taken me up.
\item Set me, O Lord, a law in thy way, and guide me in the right path, because of my enemies.
\item Deliver me not over to the will of them that trouble me; for unjust witnesses have risen up against me; and iniquity hath lied to itself.
\item I believe to see the good things of the Lord in the land of the living.
\item Expect the Lord, do manfully, and let thy heart take courage, and await thou the Lord.
