\item I cried to the Lord with my voice; to God with my voice, and he gave ear to me.
\item In the day of my trouble I sought God, with my hands lifted up to him in the night, and I was not deceived.
\item My soul refused to be comforted: I remembered God, and was delighted, and was exercised, and my spirit swooned away.
\item My eyes prevented the watches: I was troubled, and I spoke not.
\item I thought upon the days of old: and I had in my mind the eternal years.
\item And I meditated in the night with my own heart: and I was exercised and I swept my spirit.
\item Will God then cast off for ever? or will he never be more favourable again?
\item Or will he cut off his mercy for ever, from generation to generation?
\item Or will God forget to shew mercy? or will he in his anger shut up his mercies?
\item And I said, Now have I begun: this is the change of the right hand of the most High.
\item I remembered the works of the Lord: for I will be mindful of thy wonders from the beginning.
\item And I will meditate on all thy works: and will be employed in thy inventions.
\item Thy way, O God, is in the holy place: who is the great God like our God? Thou art the God that dost wonders.
\item Thou hast made thy power known among the nations: with thy arm thou hast redeemed thy people the children of Jacob and of Joseph.
\item The waters saw thee, O God, the waters saw thee: and they were afraid, and the depths were troubled.
\item Great was the noise of the waters: the clouds sent out a sound.
\item For thy arrows pass: the voice of thy thunder in a wheel.
\item Thy lightnings enlightened the world: the earth shook and trembled.
\item Thy way is in the sea, and thy paths in many waters: and thy footsteps shall not be known.
\item Thou hast conducted thy people like sheep, by the hand of Moses and Aaron.