\item How good is God to Israel, to them that are of a right heart!
\item But my feet were almost moved; my steps had well-nigh slipped.
\item Because I had a zeal on occasion of the wicked, seeing the prosperity of sinners.
\item For there is no regard to their death, nor is there strength in their stripes.
\item They are not in the labour of men: neither shall they be scourged like other men.
\item Therefore pride hath held them fast: they are covered with their iniquity and their wickedness.
\item Their iniquity hath come forth, as it were from fatness: they have passed into the affection of the heart.
\item They have thought and spoken wickedness: they have spoken iniquity on high.
\item They have set their mouth against heaven: and their tongue hath passed through the earth.
\item Therefore will my people return here and full days shall be found in them.
\item And they said: How doth God know? and is there knowledge in the most High?
\item Behold these are sinners; and yet abounding in the world they have obtained riches.
\item And I said: Then have I in vain justified my heart, and washed my hands among the innocent.
\item And I have been scourged all the day; and my chastisement hath been in the mornings.
\item If I said: I will speak thus; behold I should condemn the generation of thy children.
\item I studied that I might know this thing, it is a labour in my sight:
\item Until I go into the sanctuary of God, and understand concerning their last ends.
\item But indeed for deceits thou hast put it to them: when they were lifted up, thou hast cast them down.
\item How are they brought to desolation? they have suddenly ceased to be: they have perished by reason of their iniquity.
\item As the dream of them that awake, O Lord; so in thy city thou shalt bring their image to nothing.
\item For my heart hath been inflamed, and my reins have been changed: and I am brought to nothing, and I knew not.
\item I am become as a beast before thee: and I am always with thee.
\item Thou hast held me by my right hand; and by thy will thou hast conducted me, and with thy glory thou hast received me.
\item For what have I in heaven? and besides thee what do I desire upon earth?
\item For thee my flesh and my heart hath fainted away: thou art the God of my heart, and the God that is my portion for ever.
\item For behold they that go far from thee shall perish: thou hast destroyed all them that are disloyal to thee.
\item But it is good for me to adhere to my God, to put my hope in the Lord God:
\item That I may declare all thy praises, in the gates of the daughter of Sion.