\item With expectation I have waited for the Lord, and he was attentive to me.
\item And he heard my prayers, and brought me out of the pit of misery and the mire of dregs.
\item And he set my feet upon a rock, and directed my steps.
\item And he put a new canticle into my mouth, a song to our God.
\item Many shall see, and shall fear: and they shall hope in the Lord.
\item Blessed is the man whose trust is in the name of the Lord; and who hath not had regard to vanities, and lying follies.
\item Thou hast multiplied thy wonderful works, O Lord my God: and in thy thoughts there is no one like to thee.
\item I have declared and I have spoken they are multiplied above number.
\item Sacrifice and oblation thou didst not desire; but thou hast pierced ears for me.\ifx\enlinebreakafternine\undefined\else\\\fi
\item Burnt offering and sin offering thou didst not require: then said I, Behold I come.
\item In the head of the book it is written of me that I should do thy will: O my God, I have desired it, and thy law in the midst of my heart.
\item I have declared thy justice in a great church, lo, I will not restrain my lips: O Lord, thou knowest it.
\item I have not hid thy justice within my heart: I have declared thy truth and thy salvation.
\item I have not concealed thy mercy and thy truth from a great council.
\item Withhold not thou, O Lord, thy tender mercies from me: thy mercy and thy truth have always upheld me.
\item For evils without number have surrounded me; my iniquities have overtaken me, and I was not able to see.
\item They are multiplied above the hairs of my head: and my heart hath forsaken me.
\item Be pleased, O Lord to deliver me: look down, O Lord, to help me.
\item Let them be confounded and ashamed together, that seek after my soul to take it away.
\item Let them be turned backward and be ashamed that desire evils to me.
\item Let them immediately bear their confusion, that say to me: 'Tis well, 'tis well.
\item Let all that seek thee rejoice and be glad in thee: and let such as love thy salvation say always: The Lord be magnified.
\item But I am a beggar and poor: the Lord is careful for me.
\item Thou art my helper and my protector: O my God, be not slack.
