\item The Lord is the God to whom revenge belongeth: the God of revenge hath acted freely.
\item Lift up thyself, thou that judgest the earth: render a reward to the proud.
\item How long shall sinners, O Lord: how long shall sinners glory?
\item Shall they utter, and speak iniquity: shall all speak who work injustice?
\item Thy people, O Lord, they have brought low: and they have afflicted thy inheritance.
\item They have slain the widow and the stranger: and they have murdered the fatherless.
\item And they have said: The Lord shall not see: neither shall the God of Jacob understand.
\item Understand, ye senseless among the people: and, you fools, be wise at last.
\item He that planted the ear, shall he not hear? or he that formed the eye, doth he not consider?
\item He that chastiseth nations, shall he not rebuke: he that teacheth man knowledge?
\item The Lord knoweth the thoughts of men, that they are vain.
\item Blessed is the man whom thou shalt instruct, O Lord: and shalt teach him out of thy law.
\item That thou mayst give him rest from the evil days: till a pit be dug for the wicked.
\item For the Lord will not cast off his people: neither will he forsake his own inheritance.
\item Until justice be turned into judgment: and they that are near it are all the upright in heart.
\item Who shall rise up for me against the evildoers? or who shall stand with me against the workers of iniquity?
\item Unless the Lord had been my helper, my soul had almost dwelt in hell.
\item If I said: My foot is moved: thy mercy, O Lord, assisted me.
\item According to the multitude of my sorrows in my heart, thy comforts have given joy to my soul.
\item Doth the seat of iniquity stick to thee, who framest labour in commandment?
\item They will hunt after the soul of the just, and will condemn innocent blood.
\item But the Lord is my refuge: and my God the help of my hope.
\item And he will render them their iniquity: and in their malice he will destroy them: the Lord our God will destroy them.
