\item O God, why hast thou cast us off unto the end: why is thy wrath enkindled against the sheep of thy pasture?
\item Remember thy congregation, which thou hast possessed from the beginning.
\item The sceptre of thy inheritance which thou hast redeemed: mount Sion in which thou hast dwelt.
\item Lift up thy hands against their pride unto the end; see what things the enemy hath done wickedly in the sanctuary.
\item And they that hate thee have made their boasts, in the midst of thy solemnity.
\item They have set up their ensigns for signs, and they knew not both in the going out and on the highest top.
\item As with axes in a wood of trees, they have cut down at once the gates thereof, with axe and hatchet they have brought it down.
\item They have set fire to thy sanctuary: they have defiled the dwelling place of thy name on the earth.
\item They said in their heart, the whole kindred of them together: Let us abolish all the festival days of God from the land.
\item Our signs we have not seen, there is now no prophet: and he will know us no more.
\item How long, O God, shall the enemy reproach: is the adversary to provoke thy name for ever?
\item Why dost thou turn away thy hand: and thy right hand out of the midst of thy bosom for ever?
\item But God is our king before ages: he hath wrought salvation in the midst of the earth.
\item Thou by thy strength didst make the sea firm: thou didst crush the heads of the dragons in the waters.
\item Thou hast broken the heads of the dragon: thou hast given him to be meat for the people of the Ethiopians.
\item Thou hast broken up the fountains and the torrents: thou hast dried up the Ethan rivers.
\item Thine is the day, and thine is the night: thou hast made the morning light and the sun.
\item Thou hast made all the borders of the earth: the summer and the spring were formed by thee.
\item Remember this, the enemy hath reproached the Lord: and a foolish people hath provoked thy name.
\item Deliver not up to beasts the souls that confess to thee: and forget not to the end the souls of thy poor.
\item Have regard to thy covenant: for they that are the obscure of the earth have been filled with dwellings of iniquity.
\item Let not the humble be turned away with confusion: the poor and needy shall praise thy name.
\item Arise, O God, judge thy own cause: remember thy reproaches with which the foolish man hath reproached thee all the day.
\item Forget not the voices of thy enemies: the pride of them that hate thee ascendeth continually.