\item Rebuke me not, O Lord, in thy indignation; nor chastise me in thy wrath.
\item For thy arrows are fastened in me: and thy hand hath been strong upon me.
\item There is no health in my flesh, because of thy wrath: there is no peace for my bones, because of my sins.
\item For my iniquities are gone over my head: and as a heavy burden are become heavy upon me.
\item My sores are putrified and corrupted, because of my foolishness.
\item I am become miserable, and am bowed down even to the end: I walked sorrowful all the day long.
\item For my loins are filled with illusions; and there is no health in my flesh.
\item I am afflicted and humbled exceedingly: I roared with the groaning of my heart.
\item Lord, all my desire is before thee, and my groaning is not hidden from thee.
\item My heart is troubled, my strength hath left me, and the light of my eyes itself is not with me.
\item My friends and my neighbours have drawn near, and stood against me.
\item And they that were near me stood afar off: and they that sought my soul used violence.
\item And they that sought evils to me spoke vain things, and studied deceits all the day long.
\item But I, as a deaf man, heard not: and as a dumb man not opening his mouth.
\item And I became as a man that heareth not: and that hath no reproofs in his mouth.
\item For in thee, O Lord, have I hoped: thou wilt hear me, O Lord my God.\ifx\enlinebreakaftersixteen\undefined\else\\\fi
\item For I said: Lest at any time my enemies rejoice over me: and whilst my feet are moved, they speak great things against me.
\item For I am ready for scourges: and my sorrow is continually before me.
\item For I will declare my iniquity: and I will think for my sin.
\item But my enemies live, and are stronger than I: and they that hate me wrongfully are multiplied.
\item They that render evil for good, have detracted me, because I followed goodness.
\item Forsake me not, O Lord my God: do not thou depart from me. 
\item Attend unto my help, O Lord, the God of my salvation.
