\enminipageitem{Save me, O God: for the waters are come in even unto my soul.}
\enminipageitem{I stick fast in the mire of the deep: and there is no sure standing.}
\enminipageitem{I am come into the depth of the sea: and a tempest hath overwhelmed me.}
\enminipageitem{I have laboured with crying; my jaws are become hoarse: my eyes have failed, whilst I hope in my God.}
\enminipageitem{They are multiplied above the hairs of my head, who hate me without cause.}
\enminipageitem{My enemies are grown strong who have wrongfully persecuted me: then did I pay that which I took not away.}
\enminipageitem{O God, thou knowest my foolishness; and my offences are not hidden from thee.}
\enminipageitem{Let not them be ashamed for me, who look for thee, O Lord, the Lord of hosts.}
\enminipageitem{Let them not be confounded on my account, who seek thee, O God of Israel.}
\enminipageitem{Because for thy sake I have borne reproach; shame hath covered my face.}
\enminipageitem{I am become a stranger to my brethren, and an alien to the sons of my mother.}
\enminipageitem{For the zeal of thy house hath eaten me up: and the reproaches of them that reproached thee are fallen upon me.}
\enminipageitem{And I covered my soul in fasting: and it was made a reproach to me.}
\enminipageitem{And I made haircloth my garment: and I became a byword to them.}
\enminipageitem{They that sat in the gate spoke against me: and they that drank wine made me their song.}
\enminipageitem{But as for me, my prayer is to thee, O Lord; for the time of thy good pleasure, O God.}
\enminipageitem{In the multitude of thy mercy hear me, in the truth of thy salvation.}
\enminipageitem{Draw me out of the mire, that I may not stick fast: deliver me from them that hate me, and out of the deep waters.}
\enminipageitem{Let not the tempest of water drown me, nor the deep swallow me up: and let not the pit shut her mouth upon me.}
\enminipageitem{Hear me, O Lord, for thy mercy is kind; look upon me according to the multitude of thy tender mercies.}
\enminipageitem{And turn not away thy face from thy servant: for I am in trouble, hear me speedily.}
\enminipageitem{Attend to my soul, and deliver it: save me because of my enemies.}
\enminipageitem{Thou knowest my reproach, and my confusion, and my shame.}
\enminipageitem{In thy sight are all they that afflict me; my heart hath expected reproach and misery.}
\enminipageitem{And I looked for one that would grieve together with me, but there was none: and for one that would comfort me, and I found none.}
\enminipageitem{And they gave me gall for my food, and in my thirst they gave me vinegar to drink.}
\enminipageitem{Let their table become as a snare before them, and a recompense, and a stumblingblock.}
\enminipageitem{Let their eyes be darkened that they see not; and their back bend thou down always.}
\enminipageitem{Pour out thy indignation upon them: and let thy wrathful anger take hold of them.}
\enminipageitem{Let their habitation be made desolate: and let there be none to dwell in their tabernacles.}
\enminipageitem{Because they have persecuted him whom thou hast smitten; and they have added to the grief of my wounds.}
\enminipageitem{Add thou iniquity upon their iniquity: and let them not come into thy justice.}
\enminipageitem{Let them be blotted out of the book of the living; and with the just let them not be written.}
\enminipageitem{I am poor and sorrowful: thy salvation, O God, hath set me up.}
\enminipageitem{I will praise the name of God with a canticle: and I will magnify him with praise.}
\enminipageitem{And it shall please God better than a young calf, that bringeth forth horns and hoofs.}
\enminipageitem{Let the poor see and rejoice: seek ye God, and your soul shall live.}
\enminipageitem{For the Lord hath heard the poor: and hath not despised his prisoners.}
\enminipageitem{Let the heavens and the earth praise him; the sea, and every thing that creepeth therein.}
\enminipageitem{For God will save Sion, and the cities of Juda shall be built up.}
\enminipageitem{And they shall dwell there, and acquire it by inheritance.}
\enminipageitem{And the seed of his servants shall possess it; and they that love his name shall dwell therein.}