\item Deliver me from my enemies, O my God; and defend me from them that rise up against me.
\item Deliver me from them that work iniquity, and save me from bloody men.
\item For behold they have caught my soul: the mighty have rushed in upon me:
\item Neither is it my iniquity, nor my sin, O Lord: without iniquity have I run, and directed my steps.
\item Rise up thou to meet me, and behold: even thou, O Lord, the God of hosts, the God of Israel.
\item Attend to visit all the nations: have no mercy on all them that work iniquity.
\item They shall return at evening, and shall suffer hunger like dogs: and shall go round about the city.
\item Behold they shall speak with their mouth, and a sword is in their lips: for who, say they, hath heard us?
\item But thou, O Lord, shalt laugh at them: thou shalt bring all the nations to nothing.
\item I will keep my strength to thee: for thou art my protector: my God, his mercy shall prevent me.
\item God shall let me see over my enemies: slay them not, lest at any time my people forget. 
\item And scatter them by thy power; and bring them down, O Lord, my protector:
\item For the sin of their mouth, and the word of their lips: and let them be taken in their pride.
\item And for their cursing and lying they shall be talked of, when they are consumed: when they are consumed by thy wrath, and they shall be no more.
\item And they shall know that God will rule Jacob, and all the ends of the earth.
\item They shall return at evening and shall suffer hunger like dogs: and shall go round about the city.
\item They shall be scattered abroad to eat, and shall murmur if they be not filled.
\item But I will sing thy strength: and will extol thy mercy in the morning.\ifx\enlinebreakaftereighteen\undefined\else\\\fi
\item For thou art become my support, and my refuge, in the day of my trouble.
\item Unto thee, O my helper, will I sing, for thou art God my defence: my God, my mercy.
