\item In thee, O Lord, I have hoped, let me never be put to confusion: deliver me in thy justice, and rescue me.
\item Incline thy ear unto me, and save me.
\item Be thou unto me a God, a protector, and a place of strength: that thou mayst make me safe.
\item For thou art my firmament and my refuge.
\item Deliver me, O my God, out of the hand of the sinner, and out of the hand of the transgressor of the law and of the unjust.
\item For thou art my patience, O Lord: my hope, O Lord, from my youth.
\item By thee have I been confirmed from the womb: from my mother’s womb thou art my protector.
\item Of thee shall I continually sing: I am become unto many as a wonder, but thou art a strong helper.
\item Let my mouth be filled with praise, that I may sing thy glory; thy greatness all the day long.
\item Cast me not off in the time of old age: when my strength shall fail, do not thou forsake me.
\item For my enemies have spoken against me; and they that watched my soul have consulted together,
\item Saying: God hath forsaken him: pursue and take him, for there is none to deliver him.
\item O God, be not thou far from me: O my God, make haste to my help.
\item Let them be confounded and come to nothing that detract my soul; let them be covered with confusion and shame that seek my hurt.
\item But I will always hope; and will add to all thy praise.
\item My mouth shall shew forth thy justice; thy salvation all the day long.
\item Because I have not known learning, I will enter into the powers of the Lord: O Lord, I will be mindful of thy justice alone.
\item Thou hast taught me, O God, from my youth: and till now I will declare thy wonderful works.
\item And unto old age and grey hairs: O God, forsake me not,
\item Until I shew forth thy arm to all the generation that is to come:
\item Thy power, and thy justice, O God, even to the highest great things thou hast done: O God, who is like to thee?
\item How great troubles hast thou shewn me, many and grievous: and turning thou hast brought me to life, and hast brought me back again from the depths of the earth:
\item Thou hast multiplied thy magnificence; and turning to me thou hast comforted me.
\item For I will also confess to thee thy truth with the instruments of psaltery: O God, I will sing to thee with the harp,
\item My lips shall greatly rejoice, when I shall sing to thee; and my soul which thou hast redeemed. 
\item Yea and my tongue shall meditate on thy justice all the day; when they shall be confounded and put to shame that seek evils to me.