\item Have mercy on me, O God, according to thy great mercy.
\item And according to the multitude of thy tender mercies blot out my iniquity.
\item Wash me yet more from my iniquity, and cleanse me from my sin.
\item For I know my iniquity, and my sin is always before me.
\item Against thee only have I sinned, and done evil before thee: that thou mayst be justified in thy words, and mayst overcome when thou art judged.
\item For behold I was conceived in iniquities; and in sins did my mother conceive me.
\item For behold thou hast loved truth: the uncertain and hidden things of thy wisdom thou hast made manifest to me.
\item Thou shalt sprinkle me with hyssop, and I shall be cleansed: thou shalt wash me, and I shall be made whiter than snow.
\item To my hearing thou shalt give joy and gladness: and the bones that have been humbled shall rejoice.
\item Turn away thy face from my sins, and blot out all my iniquities.
\item Create a clean heart in me, O God: and renew a right spirit within my bowels.
\item Cast me not away from thy face; and take not thy holy spirit from me.
\item Restore unto me the joy of thy salvation, and strengthen me with a perfect spirit.
\item I will teach the unjust thy ways: and the wicked shall be converted to thee.
\item Deliver me from blood, O God, thou God of my salvation: and my tongue shall extol thy justice.
\item O Lord, thou wilt open my lips: and my mouth shall declare thy praise.
\item For if thou hadst desired sacrifice, I would indeed have given it: with burnt offerings thou wilt not be delighted.
\item A sacrifice to God is an afflicted spirit: a contrite and humbled heart, O God, thou wilt not despise.
\item Deal favourably, O Lord, in thy good will with Sion; that the walls of Jerusalem may be built up.
\item Then shalt thou accept the sacrifice of justice, oblations and whole burnt offerings: then shall they lay calves upon thy altar.