\item Lord, the God of my salvation: I have cried in the day, and in the night before thee.
\item Let my prayer come in before thee: incline thy ear to my petition.
\item For my soul is filled with evils: and my life hath drawn nigh to hell.
\item I am counted among them that go down to the pit: I am become as a man without help, free among the dead.
\item Like the slain sleeping in the sepulchres, whom thou rememberest no more: and they are cast off from thy hand.
\item They have laid me in the lower pit: in the dark places, and in the shadow of death.
\item Thy wrath is strong over me: and all thy waves thou hast brought in upon me.
\item Thou hast put away my acquaintance far from me: they have set me an abomination to themselves.
\item I was delivered up, and came not forth: my eyes languished through poverty.
\item All the day I cried to thee, O Lord: I stretched out my hands to thee.
\item Wilt thou shew wonders to the dead? or shall physicians raise to life, and give praise to thee?
\item Shall any one in the sepulchre declare thy mercy: and thy truth in destruction?\ifx\enlinebreakaftertwelve\undefined\else\\\fi
\item Shall thy wonders be known in the dark; and thy justice in the land of forgetfulness?
\item But I, O Lord, have cried to thee: and in the morning my prayer shall prevent thee.
\item Lord, why castest thou off my prayer: why turnest thou away thy face from me?
\item I am poor, and in labours from my youth: and being exalted have been humbled and troubled.
\item Thy wrath hath come upon me: and thy terrors have troubled me.
\item They have come round about me like water all the day: they have compassed me about together.
\item Friend and neighbour thou hast put far from me: and my acquaintance, because of misery.
