\item Lord, thou hast been our refuge from generation to generation.
\item Before the mountains were made, or the earth and the world was formed; from eternity and to eternity thou art God.
\item Turn not man away to be brought low: and thou hast said: Be converted, O ye sons of men.
\item For a thousand years in thy sight are as yesterday, which is past.
\item And as a watch in the night, things that are counted nothing, shall their years be.
\item In the morning man shall grow up like grass; in the morning he shall flourish and pass away: in the evening he shall fall, grow dry, and wither.
\item For in thy wrath we have fainted away: and are troubled in thy indignation.
\item Thou hast set our iniquities before thy eyes: our life in the light of thy countenance.
\item For all our days are spent; and in thy wrath we have fainted away.
\item Our years shall be considered as a spider: the days of our years in them are threescore and ten years.
\item But if in the strong they be fourscore years: and what is more of them is labour and sorrow.
\item For mildness is come upon us: and we shall be corrected.
\item Who knoweth the power of thy anger, and for thy fear can number thy wrath?
\item So make thy right hand known: and men learned in heart, in wisdom.
\item Return, O Lord, how long? and be entreated in favour of thy servants.
\item We are filled in the morning with thy mercy: and we have rejoiced, and are delighted all our days.
\item We have rejoiced for the days in which thou hast humbled us: for the years in which we have seen evils.
\item Look upon thy servants and upon their works: and direct their children.
\item And let the brightness of the Lord our God be upon us: and direct thou the works of our hands over us; yea, the work of our hands do thou direct.