\input{inc-CommonOfApostles-2Vespers-psalms}

\newcommand{\chaptertext}{\dropcap{latin}{Fratres~: Jam non estis hóspites et} \textbf{ád}\-ve\-næ~:~\dag{} sed estis cives sanctórum et doméstici Dei~: superædificáti super fundaméntum Apostolórum et \emph{Pro\-phe}\-\textbf{tá}\-rum,~* ipso summo angulári lápide Christo \textbf{Je}su.}
\newcommand{\chaptertranslation}{Brethren: You are no more strangers and foreigners, but you are fellow-citizens with the saints, and the domestics of God: built upon the foundation of the apostles and prophets, Jesus Christ Himself being the chief cornerstone.}

\newcommand{\hymnlinetwo}{4.}
\newcommand{\hymntex}{Hymn-ExsultetOrbisGaudiis}
\newcommand{\hymninitial}{E}
\newcommand{\hymntranslation}{
\item Now let the earth with joy resound,
And heaven the chant re-echo round;
Nor heaven nor earth too high can raise
The great Apostles' glorious praise.

\item O ye who, throned in glory dread,
Shall judge the living and the dead,
Lights of the world forevermore!
To you the suppliant prayer we pour.

\item Ye close the sacred gates on high;
At your command apart they fly:
Oh! loose for us the guilty chain
We strive to break, and strive in vain.

\item Sickness and health your voice obey;
At your command they go or stay:
From sin's disease our souls restore;
In good confirm us more and more.

\item So when the world is at its end,
And Christ to judgement shall descend,
May we be called those joys to see
Prepared from all eternity.

\item Praise to the Father, with the Son,
And Holy Spirit, Three in One;
As ever was in ages past,
And so shall be while ages last.
Amen.\grechangestaffsize{15}}

\newcommand{\vrtex}{vrAnnuntiaveruntOperaDei}
\newcommand{\vtranslation}{They declared the works of God.}
\newcommand{\rtranslation}{And understood His doings.}

\newcommand{\maganttex}{MagnificatAntiphon}
\newcommand{\magantinitial}{E}
\newcommand{\maganttranslation}{Be ye valiant in warfare, and fight with the old serpent: and ye shall receive an everlasting kingdom.}
\def\magsolemn{T}
\definemag{1}{g2}
