\newcommand{\antonetex}{Ant1-EcceInNubibusCaeli}
\newcommand{\antoneinitial}{E}
\newcommand{\antonetranslation}{Behold, the Lord shall come in the clouds of heaven with great power, alleluia.}
\definepsalm{1}{109}{1}{g}

\newcommand{\anttwotex}{Ant2-Urbs}
\newcommand{\anttwoinitial}{U}
\newcommand{\anttwotranslation}{Sion, the city of our strength, a Saviour shall be set therein as a wall and bulwark: open ye the gates, for God is with us, alleluia.}
\def\psalmclef{2}
\definepsalm{2}{110}{7}{d}
\let\psalmclef=\undefined

\newcommand{\antthreetex}{Ant3-EcceApparebit}
\newcommand{\antthreeinitial}{E}
\newcommand{\antthreetranslation}{Behold the Lord shall appear, and shall not lie: if He delay wait for Him, for He shall come, and shall not tarry, alleluia.}
\definepsalm{3}{111}{7}{a}

\newcommand{\antfourtex}{Ant4-Montes}
\newcommand{\antfourinitial}{M}
\newcommand{\antfourtranslation}{The mountains and the hills shall sing praise before God, and all the trees of the woods shall clap their hands, for the sovereign Lord shall come into His everlasting kingdom, alleluia, alleluia.}
\definepsalm{4}{112}{1}{f}

\newcommand{\antfivetex}{Ant5-EcceDominusNoster}
\newcommand{\antfiveinitial}{E}
\newcommand{\antfivetranslation}{Behold our Lord shall come with strength to enlighten the eyes of His servants, alleluia.}
\definepsalm{5}{113}{3}{a}

\newcommand{\chaptertext}{\dropcap{latin}{Fratres~: Quæcúmque scripta sunt, ad nostram doctrínam} \textbf{scrí}\-pta sunt~:~\gredagger{} ut per patiéntiam, et consolatiónem \emph{Scri\-ptu}\-\textbf{rá}\-rum,~* spem ha\-be\-\textbf{á}\-mus.}
\newcommand{\chaptertranslation}{Brethren: What things soever were written, were written for our learning: that through patience and the comfort of the Scriptures, we might have hope.}

\newcommand{\magantinitial}{T}
\newcommand{\maganttex}{MagnificatAntiphon}
\newcommand{\maganttranslation}{Art Thou He that art to come, or look we for another? Relate to John what you have seen: The blind recover their sight, the dead rise again, the poor have the Gospel preached to them, alleluia.}
\def\magsolemn{F}
\definemag{8}{G*}

\newcommand{\collect}{Excita Dómine corda nostra ad præparándas Unigéniti tui vias~:~† ut per ejus advéntum,~* purificátis tibi méntibus servíre mereámur. Qui tecum vivit et regnat.}
\newcommand{\collecttranslation}{Stir up our hearts, O Lord, to prepare the ways of Thine only-begotten Son: that through His coming we may deserve to serve Thee with purified minds: Who with Thee liveth and reigneth.}
