% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% page 812 in liber (998 in pdf)

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\heading}{Vesper Hymn for Paschal Time.}
\def\hymninitialsize{32}
\def\hymnlinetwo{\oldstylenums{8.}}
\def\hymntex{hymn-AdRegiasAgniDapes}
\def\hymninitial{A}
\def\hymntranslation{\item At the Lamb's high feast we sing
praise to our victorious King,
Who hath washed us in the tide
flowing from His pierced side.
\item Praise we Him Whose love divine
gives the guests His Blood for wine,
gives His Body for the feast,
Love the victim, Love the priest.
\item Where the Paschal blood is poured,
Death's dark Angel sheathes his sword;
Israel's hosts triumphant go
through the wave that drowns the foe.
\item Christ, the Lamb Whose Blood was shed,
Paschal victim, Paschal bread;
with sincerity and love
eat we manna from above.
\item Mighty Victim from the sky,
powers of hell beneath Thee lie;
Death is conquered in the fight;
Thou hast brought us life and light.
\item Now Thy banner Thou dost wave;
vanquished Satan and the grave;
see the prince of darkness quelled;
heaven's bright gates are open held.
\item Paschal triumph, Paschal joy,
only sin can this destroy;
from sin's death do Thou set free
souls re-born, dear Lord, in Thee.
\item Hymns of glory, songs of praise,
Father, unto Thee we raise;
risen Lord, all praise to Thee,
ever with the Spirit be.
Amen.}
\def\prehymn{\normalsize\setgrefactor{14}\vspace*{-5ex plus 5ex}}
\def\posthymn{\vspace{-1ex}
}

\def\vrtex{hymn-AdRegiasAgniDapesvr}
\def\vrnospace{T}
\def\vtranslation{Stay with us O Lord, alleluia.}
\def\rtranslation{Because it is towards evening, alleluia.}

%\definebenedicamusdomino{lent}{2}
\input{../hymn-template}