\newcommand{\chaptertext}{\dropcap{latin}{Caríssimi~: Estóte prudéntes, et vigiláte in} o\-ra\-ti\-\textbf{ó}\-ni\-bus.~\dag{} Ante ómnia autem, mútuam in vobismetípsis caritátem con\-tí\-nu\-\emph{am} \emph{ha}\-\textbf{bén}\-tes~:~* quia cáritas óperit multitúdinem pec\-ca\-\textbf{tó}\-rum.}
\newcommand{\chaptertranslation}{Dearly beloved, be prudent, and watch in prayers.  But before all things, have a constant mutual charity among yourselves: for charity covereth a multitude of sins.}

\def\hymnlinetwo{\oldstylenums{4.}}
\def\hymntex{hymn-SalutisHumanaeSator}
\def\hymninitial{S}
\def\hymntranslation{\item O Thou pure Light of souls that love!
True joy of every human breast!
Sower of life's immortal seed!
Our Maker, and Redeemer blest!
\item What wond'rous pity Thee o'ercame
To make our guilty load Thine own,
And, sinless, suffer death and shame,
For our transgressions to atone!
\item Thou, bursting Hades open wide,
Didst all the captive souls unchain;
And thence to Thy dread Father's side
With glorious pomp ascend again.
\item O still may pity Thee compel
To heal the wounds of which we die;
And take us in Thy light to dwell,
Who for Thy blissful Presence sigh.
\item Be Thou our Guide: be Thou our Goal:
Be Thou our Pathway to the skies;
Our Joy when sorrow fills the soul;
In death our everlasting Prize.
Amen.}

\def\vrtex{hymn-DominusInCaelovr}
\def\vtranslation{The Lord in heaven, alleluia.}
\def\rtranslation{Has prepared His throne, alleluia.}

\newcommand{\latincollect}{Omnípotens sempitérne Deus~:~\dag{} fac nos tibi semper et devótam gérere voluntátem,~* et majestáti tuæ sincéro corde servíre. Per Dóminum nostrum.}
\newcommand{\englishcollect}{Almighty and everlasting God, make us always bear towards Thee a devoted will, and serve Thy Majesty with a sincere heart. Through our Lord.}

\newcommand{\maganttex}{MagnificatAntiphonSundayAfterAscension}
\newcommand{\englishmagantiphon}{These things have I spoken to you that, when the hour shall come, you may remember that I told you, alleluia.}
\def\magsolemn{F}
\newcommand{\magantinitial}{H}
\definemag{8}{G}

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 1 accent.}{Termination of 1 accent with 2 preparatory syllables.}}
