% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% page 829 in liber (1015 in pdf)

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Caríssimi~: Omne datum óptimum, et omne donum perféctum desúrsum est, descéndens a Patre} \textbf{lú}\-mi\-num,~\dag{} apud quem non est \emph{trans\-mu}\-\textbf{tá}\-ti\-o,~* nec vicissitúdinis obum\textbf{brá}\-ti\-o.}
\newcommand{\chaptertranslation}{Dearly beloved, every best gift and every perfect gift, is from above; coming down from the Father of lights, with whom there is no change, nor shadow of alteration.}

\newcommand{\hymn}{Ad régias Agni dápes}
\newcommand{\vr}{Máne nobíscum Dómine}

\newcommand{\headingtext}{4th Sunday after Easter.}
\newcommand{\maganttex}{MagnificatAntiphonEaster4}

\newcommand{\latincollect}{Deus, qui fidélium mentes uníus éfficis voluntátis~:~\dag{} da pópulis tuis id amáre quod praécipis, id desideráre quod promíttis~;~* ut inter mundánas varietátes, ibi nostra fixa sint corda, ubi vera sunt gáudia. Per Dóminum nostrum.}
\newcommand{\englishcollect}{O God, who makest the faithful to be of one mind and will: grant to Thy people the grace to love what Thou dost command and to desire what Thou dost promise, that amid the changes of the world our hearts may there be fixed where true joys are found. Through our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
%\vspace{-3ex}%
I go to him who sent me; but because I have spoken these things to you, sorrow hath filled your heart, alleluia.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{V}
\definemag{2}{D}

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 1 accent.}{Termination of 1 accent with 1 preparatory syllable.}}

\newcommand{\premagant}{%
%\normalsize
\large%\greblockcustos
}

\newcommand{\magantinitialsize}{38}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{14}}

\definebenedicamusdomino{easter}{}

\input{../vespersmagnificat}
