% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\def\usepagenumbers{T}

\newcommand{\chapter}{\dropcap{latin}{Caríssimi~: Estóte prudéntes, et vigiláte in} o\-ra\-ti\-\textbf{ó}\-ni\-bus.~\dag{} Ante ómnia autem, mútuam in vobismetípsis caritátem con\-tí\-nu\-\emph{am} \emph{ha}\-\textbf{bén}\-tes~:~* quia cáritas óperit multitúdinem pec\-ca\-\textbf{tó}\-rum.}
\newcommand{\chaptertranslation}{Dearly beloved, be prudent, and watch in prayers.  But before all things, have a constant mutual charity among yourselves: for charity covereth a multitude of sins.}

%todo full hymn and versicle
\def\hymninitialsize{35}
\def\hymnlinetwo{\oldstylenums{4.}}
\def\hymntex{hymn-SalutisHumanaeSator}
\def\hymninitial{S}
\def\hymntranslation{\item O Thou pure Light of souls that love!
True joy of every human breast!
Sower of life's immortal seed!
Our Maker, and Redeemer blest!
\item What wond'rous pity Thee o'ercame
To make our guilty load Thine own,
And, sinless, suffer death and shame,
For our transgressions to atone!
\item Thou, bursting Hades open wide,
Didst all the captive souls unchain;
And thence to Thy dread Father's side
With glorious pomp ascend again.
\item O still may pity Thee compel
To heal the wounds of which we die;
And take us in Thy light to dwell,
Who for Thy blissful Presence sigh.
\item Be Thou our Guide: be Thou our Goal:
Be Thou our Pathway to the skies;
Our Joy when sorrow fills the soul;
In death our everlasting Prize.
Amen.}
\def\prehymn{%\large\setgrefactor{14}\vspace*{-5ex plus 5ex}
}

\def\vrtex{hymn-DominusInCaelovr}
\def\vrnospace{F}
\def\vtranslation{The Lord in heaven, alleluia.}
\def\rtranslation{Has prepared His throne, alleluia.}

\newcommand{\headingtext}{Sunday after the Ascension.}
\newcommand{\maganttex}{MagnificatAntiphonSundayAfterAscension}

\newcommand{\latincollect}{Omnípotens sempitérne Deus~:~\dag{} fac nos tibi semper et devótam gérere voluntátem,~* et majestáti tuæ sincéro corde servíre. Per Dóminum nostrum.}
\newcommand{\englishcollect}{Almighty and everlasting God, make us always bear towards Thee a devoted will, and serve Thy Majesty with a sincere heart. Through our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
%\vspace{-3ex}%
These things have I spoken to you that, when the hour shall come, you may remember that I told you, alleluia.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{H}
\definemag{8}{G}

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 1 accent.}{Termination of 1 accent with 2 preperatory syllables.}}

\newcommand{\premagant}{%
%\normalsize
\large%\greblockcustos
}

\newcommand{\magantinitialsize}{38}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{15}}

\definebenedicamusdomino{easter}{}

\input{../vespersmagnificat}
