% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Caríssimi~: Obsecro vos tamquam ádvenas et} per\-e\-\textbf{grí}\-nos,~\dag{} abstinére vos a carnálibus \emph{de\-si}\-\textbf{dé}\-ri\-is.~* quæ mílitant advérsus \textbf{á}\-ni\-mam.}
\newcommand{\chaptertranslation}{Dearly beloved, I beseech you as strangers and pilgrims, to refrain yourselves from carnal desires which war against the soul.}

\newcommand{\hymn}{Ad régias Agni dápes}
\newcommand{\vr}{Máne nobíscum Dómine}

\newcommand{\headingtext}{3rd Sunday after Easter.}
\newcommand{\maganttex}{MagnificatAntiphonEaster3.tex}

\newcommand{\latincollect}{Deus, qui errántibus, ut in viam possint redíre justítiæ, veritátis tuæ lumen osténdis~:~\dag{} da cunctis qui christiána professióne censéntur, et illa respúere quæ huic inimíca sunt nómini~;~* et ea quæ sunt apta sectári. Per Dóminum nostrum.}
\newcommand{\englishcollect}{O God, who to those that go astray dost show the light of Thy truth, that they may return to the path of justice: grant that all who are enrolled in the Christian faith, may both spurn all that is hostile to that name, and follow after what is fitting to it. Through our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
%\vspace{-3ex}%
Amen, amen, I say to you, that you shall lament and weep, but the world shall rejoice; and you shall be made sorrowful, but your sorrow shall be turned into joy, alleluia.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{A}
\definemag{8}{G}

%\newcommand{\magmedianttermination}{\medianttermination{Mediant of 1 accent.}{Termination of 1 accent with 2 preperatory syllables.}}

\newcommand{\premagant}{%
\normalsize
\setgrefactor{17}
%\large
%\greblockcustos
}

\newcommand{\magantinitialsize}{38}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{15}}

\definebenedicamusdomino{easter}{}

\input{../vespersmagnificat}
