% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% page 820 in liber (1006 in pdf)

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Caríssimi~: Christus passus est pro} \textbf{no}\-bis~:~\dag{} vobis relínquens exémplum, ut sequámini ve\-stí\-\emph{gi\-a} \textbf{e}\-jus.~* Qui peccátum non fecit, nec invéntus est dolus in ore \textbf{e}\-jus.}
\newcommand{\chaptertranslation}{Dearly beloved, Christ suffered for us, leaving you an example that you should follow His steps.  He did no sin, neither was guile found in His mouth.}

\newcommand{\hymn}{Ad régias Agni dápes}
\newcommand{\vr}{Máne nobíscum Dómine}

\newcommand{\headingtext}{2nd Sunday after Easter.}
\newcommand{\maganttex}{MagnificatAntiphonEaster2}

\newcommand{\latincollect}{Deus, qui in Fílii tui humilitáte, jacéntem mundum erexísti~:~\dag{} fidélibus tuis perpétuam concéde lætítiam~;~* ut quos perpétuæ mortis eripuísti cásibus, gáudiis fácias pérfrui sempitérnis. Per eúmdem Dóminum nostrum.}
\newcommand{\englishcollect}{O God, who by the humility of Thy Son, didst lift up a fallen world, grant unending happiness to Thy faithful: that those whom Thou hast snatched from the perils of endless death, Thou mayest cause to rejoice in everlasting joys. Through the same our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
%\vspace{-3ex}%
I am the good shepherd, who feed My sheep; and for My sheep I lay down My life, alleluia.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{E}
\definemag{3}{a}

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 2 accents.}{Termination of 1 accent with 1 preparatory syllable.}}

\newcommand{\premagant}{%
%\normalsize
\large%\greblockcustos
}

\newcommand{\magantinitialsize}{38}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{15}}

\definebenedicamusdomino{easter}{}

\input{../vespersmagnificat}
