\newcommand{\antonetex}{an--unus_militum--solesmes}
\newcommand{\antoneinitial}{U}
\newcommand{\antonetranslation}{A soldier with a spear opened his side, and immediately there came forth blood and water.}
\definepsalm{1}{109}{1}{f}

\newcommand{\anttwotex}{an--stans_jesus--solesmes}
\newcommand{\anttwoinitial}{S}
\newcommand{\anttwotranslation}{Jesus stood and cried, saying~: If any man thirst, let him come to me and drink.}
\definepsalm{2}{110}{7}{c}

\newcommand{\antthreetex}{an--in_caritate--solesmes}
\newcommand{\antthreeinitial}{I}
\newcommand{\antthreetranslation}{With an everlasting love has God loved us; lifted up, therefore, from the earth, he has drawn us to his Heart, taking pity on us.}
\definepsalm{3}{115}{3}{a2}

\newcommand{\antfourtex}{an--venite_ad_me--solesmes}
\newcommand{\antfourinitial}{V}
\newcommand{\antfourtranslation}{Come to me, all you that labour and are burdened~: and I will refresh you.}
\definepsalm{4}{127}{4}{E}

\newcommand{\antfivetex}{an--fili_praebe--solesmes}
\newcommand{\antfiveinitial}{F}
\newcommand{\antfivetranslation}{My son, give me thy heart~: and let thine eyes keep my ways.}
\definepsalm{5}{147}{5}{a}

\newcommand{\chaptertext}{\dropcap{latin}{Fratres~: Mihi ómnium sanctórum mínimo, data est} grá\-ti\-\textbf{a} hæc,~\dag{} in géntibus evangelizáre investigábiles di\-vi\-\emph{ti\-as} \textbf{Chri}\-sti;~* et illumináre omnes, quæ sit dispensátio sacraménti abscónditi a sǽculis in \textbf{De}o.}
\newcommand{\chaptertranslation}{Brethren, to me, the least of all the saints, is given this grace, to preach among the gentiles the unsearchable riches of Christ~: and to enlighten all men, that they may see what is the dispensation of the mystery which hath been hidden from eternity in God.}

\newcommand{\hymnlinetwo}{3.}
\newcommand{\hymntex}{hy--en_ut_superba--solesmes}
\newcommand{\hymninitial}{E}
\newcommand{\hymntranslation}{
\item Look on this wounded heart, and know
for our offence 'twas cloven so;
for guilty man's perfidious deeds the pure and heavenly Victim bleeds.

\item What worse than heathen souls are here
whose sins direct the heathen spear
and wound that blessed Heart from whence
proceed our succour and defence.

\item Wherefrom, as Eve from Adam's side,
is born the new mysterious Bride;
wherethrough, like Noë's faithful band,
forth from the ark we pass to land.

\item Thence like a sevenfold river flows
grace that no bound or measure knows;
thither the sinful tribes repair
and wash their robes to whiteness there.

\item Oh may our hearts the semblance take
of his who suffered for our sake
and in our bosoms burn the same
divine and ever-during flame.

\item Christ, from whose Heart all grace is poured,
be everlastingly adored,
and equal praises still repeat
the Father and the Paraclete.
Amen.%\grechangestaffsize{15}
}


\newcommand{\vrtex}{vrHaurietis}
\newcommand{\vtranslation}{Ye shall draw waters with joy.}
\newcommand{\rtranslation}{Out of the Saviour's fountains.}

\newcommand{\collect}{Deus qui nobis, in Corde Fílii tui, nostris vulneráto peccátis, infinítos dilectiónis thesáuros misericórditer largíri dignáris;~† concéde, quǽsumus, ut illi devótum pietátis nostræ præstántes obséquium,~* dignæ quoque satisfactiónis exhibeámus offícium.  Per eúmdem.}
\newcommand{\collecttranslation}{O God, who in the Heart of thy Son, wounded for our sins, dost deign mercifully to lavish upon us the treasures of thy love~: grant, we beseech thee, that with the devout homage of our piety we may also offer him worthy service of reparation.  Through the same.}
