\newcommand{\antonetex}{Ant1-DeExcelso}
\newcommand{\antoneinitial}{D}
\newcommand{\antonetranslation}{From above hath he sent fire into my bones, and it prevaileth against them.}
\definepsalm{1}{109}{7}{c}

\newcommand{\anttwotex}{Ant2-Concaluit}
\newcommand{\anttwoinitial}{C}
\newcommand{\anttwotranslation}{My heart was hot within me: and while I was thus musing the fire kindled.}
\definepsalm{2}{110}{2}{D}

\newcommand{\antthreetex}{Ant3-CorMeum}
\newcommand{\antthreeinitial}{C}
\newcommand{\antthreetranslation}{My heart and my flesh rejoice in the living God.}
\definepsalm{3}{111}{1}{g3}

\newcommand{\antfourtex}{Ant4-FactusEst}
\newcommand{\antfourinitial}{F}
\newcommand{\antfourtranslation}{There came in my heart as a burning fire, shut up in my bones, and I was wearied, not being able to bear it.}
\definepsalm{4}{112}{5}{a}

\newcommand{\antfivetex}{Ant5-Defecit}
\newcommand{\antfiveinitial}{L}
\newcommand{\antfivetranslation}{My flesh and my heart faileth; but God is the strength of my heart, and my portion for ever.}
\definepsalm{5}{116}{3}{a}

\newcommand{\chaptertext}{\dropcap{latin}{Cáritas Déi diffúsa est in córdibus nóstris, per inhabitántem Spíritum ejus in nóbis.}}
\newcommand{\chaptertranslation}{The love of God is shed abroad in our hearts by the Holy Ghost which is given unto us.}

\newcommand{\hymnlinetwo}{3.}
\newcommand{\hymntex}{Hymn-PangamusNerio}
\newcommand{\hymninitial}{P}
\newcommand{\hymntranslation}{
\item Let us sing the songs that are Neri's due,
Whom Virtue and Merit famously exalted
Over the shining stars in the sky,
Where he might pluck the pious joys of heaven.

\item Seeing his dwelling place
Ravaged by sudden and calamitous fire,
He disdains weeping,
Though a few of his tears might easily overcome the flames.

\item Foregoing his uncle's magnanimous offer of gold coins,
He wendeth his way to Rome
Whom, more than any other city,
He illustriously makes to shine again.

\item Down in the catacombs,
Filled with the bodies of the martyrs,
He spends whole wakeful nights,
Busily learning from the very dead,
The rule whereby to live.

\item Constant Glory be to the nourishing Trinity,
Sustainer of the Sky, Abyss and Earth themselves;
And Who grant us through Neri's prayers
The perpetual joys of heaven, our true and native home.
The perpetual joys of the sweet native land.
Amen.%\grechangestaffsize{15}
}
\def\hymnnote{Translated by Dr Roberto Lionello}

\newcommand{\vrtex}{vrDeusVirtutum}
\newcommand{\vrpttex}{vrDeusVirtutumPT}
\newcommand{\vtranslation}{God of hosts, look down from heaven, and visit this vineyard.}
\newcommand{\rtranslation}{And perfect the same which thy right hand hath planted.}

\def\magsolemn{T}

\newcommand{\collect}{Deus, qui beátum Philíppum, confessórem túum, sanctórum tuórum glória sublimásti~:~\dag{} concéde propítius, ut cújus solemnitáte lætámur,~* ejus virtútum proficiámus exémplo. Per Dóminum nostrum.}
\newcommand{\collecttranslation}{O God, who hast exalted blessed Philip, Thy Confessor, in the glory of Thy saints, grant that, as we rejoice in his solemnity, so we may profit by the example of his virtues. Through our Lord.}
