\newcommand{\chapter}{\dropcap{latin}{Misit Heródes rex manus, ut afflígeret quosdam de } ec\-\textbf{clé}\-sia.~\dag{} Occídit autem Jacóbum fratrem Jo\-\emph{án\-nis} \textbf{glá}\-dio.~* Videns autem quia placéret Judǽis, appósuit ut apprehénderet et \textbf{Pe}trum.}
\newcommand{\chaptertranslation}{Herod the King stretched forth his hands to afflict some of the Church: and he killed James, the brother of John, with the sword; and seeing that it pleased the Jews, he proceeded to take up Peter also.}

\newcommand{\collect}{Deus, qui hodiérnam diem Apostolórum tuórum Petri et Pauli martýrio consecrásti~:~\dag{} da Ecclésiæ tuæ, eórum in ómnibus sequi præcéptum;~* per quos religiónis sumpsit exórdium. Per Dóminum nostrum.}
\newcommand{\collecttranslation}{O God, who didst hallow this day by the martyrdom of Thine Apostles Peter and Paul: grant that Thy Church may in all things follow the precepts of those through whom she received the beginnings of the Faith. Through our Lord.}

\newcommand{\hymnlinetwo}{4.}
\newcommand{\hymntex}{Hymn-DecoraLuxAeternitatis}
\newcommand{\hymninitial}{D}
\newcommand{\hymntranslation}{
\item The beauteous light of God's eternal majesty
Streams down in golden rays to grace this holy day
Which crowned the princes of the Apostles' glorious choir,
And unto guilty mortals showed the heavenward way.

\item The teacher of the world and keeper of heaven's gate,
Rome's founders twain and rulers too of every land,
Triumphant over death by sword and shameful cross,
With laurel crowned are gathered to the eternal band.

\item O happy Rome! who in thy martyr princes' blood,
A twofold stream, art washed and doubly sanctified.
All earthly beauty thou alone outshinest far,
Empurpled by their outpoured life-blood's glorious tide.

\item All honour, power, and everlasting jubilee
To him who all things made and governs here below,
To God in essence One, and yet in persons Three,
Both now and ever, while unending ages flow.
Amen.%\grechangestaffsize{15}
}
