\newcommand{\antonetex}{an--qui_me_confessus_fuerit--solesmes}
\newcommand{\antoneinitial}{Q}
\newcommand{\antonetranslation}{Every one therefore that shall confess me before men, I will also confess me before my father.}
\definepsalm{1}{109}{1}{f}

\newcommand{\anttwotex}{an--qui_sequitur_me--solesmes}
\newcommand{\anttwoinitial}{Q}
\newcommand{\anttwotranslation}{He that followeth me walketh not in darkness, but shall have the light of life, saith the Lord.}
\definepsalm{2}{110}{3}{a}

\newcommand{\antthreetex}{an--qui_mihi_ministrat--solesmes}
\newcommand{\antthreeinitial}{Q}
\newcommand{\antthreetranslation}{If any man minister to me, let him follow me~: and where I am, there also shall my minister be.}
\definepsalm{3}{111}{1}{f}

\newcommand{\antfourtex}{an--si_quis_mihi_ministraverit--solesmes}
\newcommand{\antfourinitial}{S}
\newcommand{\antfourtranslation}{If any man minister to me, him will my Father who is in heaven honour, saith the Lord.}
\definepsalm{4}{112}{1}{f}

\newcommand{\antfivetex}{an--volo_pater--solesmes}
\newcommand{\antfiveinitial}{V}
\newcommand{\antfivetranslation}{Father, I will that where I am, there also may my minister be.}
\definepsalm{5}{115}{1}{a2}

\newcommand{\chaptertext}{\dropcap{latin}{Beátus vir qui suffert} ten\-ta\-ti\-\textbf{ó}\-nem~:~\dag{} quóniam cum probátus fúerit, accípiet cor\-\emph{ó\-nam} \textbf{vi}\-tæ,~* quam repromísit Deus di\-li\-\textbf{gén}\-ti\-bus se.}
\newcommand{\chaptertranslation}{Blessed is the man that endureth temptation~: for when he hath been proved, he shall receive the crown of life, which God hath promised to them that love Him.}

\def\hymnlinetwo{\oldstylenums{3.}}
\def\hymntex{hy--deus_tuorum_militum_another_chant--solesmes}
\def\hymninitial{D}
\def\hymntranslation{\item O God, the lot, reward, and prize
that crowns thy Martyr's victories,
grant, while we sing this Martyr's praise,
we may renounce our sinful ways.

\item The world with specious cheats disguised
he soon discovered and despised,
and laboured for a nobler gain
than palling pleasures mixed with pain.

\item No force could make his mind relent,
no racks his resolution bent,
fearless of death, he sheds his blood
and wades to heaven through the flood.

\item O vocal blood, now pierce the skies
and deal with heaven to hear our cries;
that on his glorious triumph we
may find indulgence, Lord, with thee.

\item Immortal glory, endless fame
the glorious works of God proclaim,
and sing with the celestial host
the Father, Son, and Holy Ghost.
}

%\def\magsolemn{T}

\newcommand{\vrtex}{vrJustusUtPalmaFlorebit}
\newcommand{\vtranslation}{The just shall flourish like the palm-tree.}
\newcommand{\rtranslation}{And shall be multiplied as the cedar of Libanus.}

\newcommand{\maganttex}{an--qui_vult_venire--solesmes}
\newcommand{\magantinitial}{Q}
\newcommand{\maganttranslation}{If any man will come after me, let him deny himself and take up his cross and follow me.}
\def\magsolemn{T}
\definemag{1}{f}

