\newcommand{\antonetex}{an--deus_mundi_opifex--solesmes}
\newcommand{\antoneinitial}{D}
\newcommand{\antonetranslation}{God, the maker of the world, has stationed man to dress and keep the earth, alleluia.}
\definepsalm{1}{109}{1}{f}

\newcommand{\anttwotex}{an--christus_dei_filius--solesmes}
\newcommand{\anttwoinitial}{C}
\newcommand{\anttwotranslation}{Christ, the Son of God, deigned to work with his hands, alleluia.}
\definepsalm{2}{110}{1}{f}

\newcommand{\antthreetex}{an--artem_fabri--solesmes}
\newcommand{\antthreeinitial}{A}
\newcommand{\antthreetranslation}{The carpenter, St Joseph, faithfully exercising his trade, shines forth as a marvellous example of work, alleluia.}
\definepsalm{3}{111}{7}{a}

\newcommand{\antfourtex}{an--fidelis_servus--solesmes}
\newcommand{\antfourinitial}{F}
\newcommand{\antfourtranslation}{Faithful and prudent servant, whom the Lord hath appointed over his family, alleluia.}
\definepsalm{4}{112}{3}{a}

\newcommand{\antfivetex}{an--joseph_opifex_sancte--solesmes}
\newcommand{\antfiveinitial}{J}
\newcommand{\antfivetranslation}{O Joseph, holy workman, defend our work, alleluia.}
\definepsalm{5}{116}{4}{c}

\newcommand{\chaptertext}{\dropcap{latin}{Fratres~: Caritátem habéte, quod est vínculum} per\-fec\-ti\textbf{ó}\-nis,~\dag{} et pax Christi exsúltet in cór\-\emph{di\-bus}, \textbf{vé}\-stris,~* et grati es\-\textbf{tó}\-te.}
\newcommand{\chaptertranslation}{Brethren, have charity, which is the bond of perfection, and let the peace of Christ rejoice in your hearts, and be ye thankful.}

% hymn Ave Maris Stella
\newcommand{\hymnlinetwo}{1.}
\newcommand{\hymntex}{hy--te_joseph_celebrent--solesmes}
\newcommand{\hymninitial}{T}
\newcommand{\hymntranslation}{
\item Let angels chant thy praise, pure spouse of purest bride,
While Christendom's sweet choirs the gladsome strains repeat,
To tell thy wondrous fame, to raise the pealing hymn,
Wherewith we all thy glory greet.

\item When doubts and bitter fears thy heavy heart oppressed,
And filled thy righteous soul with sorrow and dismay,
An angel quickly came, the wondrous secret told,
And drove thy anxious griefs away.

\item Thy arms thy new-born Lord, with tender joy embrace;
Him then to Egypt's land thy watchful care doth bring;
Him in the temple's courts once lost thou dost regain,
And 'mid thy tears dost greet thy King.

\item Not till death's pangs are o'er do others gain their crown,
But, Joseph, unto thee the blessed lot was given
While life did yet endure, thy God to see and know,
As do the saints above in heaven.

\item Grant us, great Trinity, for Joseph's holy sake,
In highest bliss and love, above the stars to reign,
That we in joy with him may praise our loving God,
And sing our glad eternal strain.
Amen.
}

\def\magsolemn{T}

\newcommand{\collect}{Rerum cónditor Deus, qui legem labóris humáno géneri statuísti~:\dag{} cancéde propítius; ut, sancti Joseph exémplo et patrocínio, ópera perficiámus quæ prǽcipis,~* et prǽmia consequámur quæ promíttis. Per Dóminum.}
\newcommand{\collecttranslation}{God, Creator of all things, who didst lay on the human race the law of labour: graciously grant; that by following the example of St Joseph and under his patronage, we may carry out the work Thou dost command, and obtain the reward Thou dost promise. Through.}
