% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% page 1176 in liber (1370 in pdf)

\newcommand{\heading}{Common of a Confessor Bishop. II Vespers.}
\sloppy

\newcommand{\predeusinadjutorium}{%
%\smallskip
\large
\grechangestaffsize{15}
}
\def\deusinadjutoriumsolemn{F}
\def\includelaustibi{T}

\newcommand{\preantone}{\grechangestaffsize{17}
\large
%\greseteolcustos{manual}
}

\newcommand{\antoneinitialsize}{33}
\newcommand{\antonetex}{Ant1-EcceSacerdosMagnus}
\newcommand{\antoneinitial}{E}
\newcommand{\antonetranslation}{Behold a great priest, who in his days pleased God, and was found just.}
\definepsalm{1}{109}{7}{c}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\grechangestaffsize{17}
\greseteolcustos{manual}
\large
}
\newcommand{\anttwoinitialsize}{33}
\newcommand{\anttwotex}{Ant2-NonEstInventus}
\newcommand{\anttwoinitial}{N}
\newcommand{\anttwotranslation}{There was not any found like to him, who kept the law of the Most High.}
\definepsalm{2}{110}{7}{c}
\newcommand{\prepsalmtwo}{%
\normalsize
\greseteolcustos{manual}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\grechangestaffsize{17}
\large
%\greseteolcustos{manual}
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{Ant3-Ideo}
\newcommand{\antthreeinitial}{I}
\newcommand{\antthreetranslation}{Therefore by an oath the Lord made him increase among his people.}
%\def\psalmclef{2}
\definepsalm{3}{111}{8}{G*}
%\let\psalmclef=\undefined
\newcommand{\prepsalmthree}{%
\normalsize
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\grechangestaffsize{17}
%\greseteolcustos{manual}
\large
%\normalsize
}
\newcommand{\antfourinitialsize}{34}
\newcommand{\antfourtex}{Ant4-SacerdotesDei}
\newcommand{\antfourinitial}{S}
\newcommand{\antfourtranslation}{\vspace{0ex minus 3.5ex}Priests of God, bless the Lord: servants of the Lord, sing a hymn to God, alleluia.\vspace{0ex minus 3.5ex}}
\definepsalm{4}{112}{7}{c}
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\grechangestaffsize{15}
\normalsize
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\nopagebreakbeforepsalmfive{T}
\def\pagebreakafterpsalmfive{T}
\newcommand{\preantfive}{\grechangestaffsize{15}
%\greseteolcustos{manual}
\normalsize
}
\newcommand{\preantfivetwo}{\preantfive}
\newcommand{\antfivefontsizetwo}{34}

\newcommand{\antfiveinitialsize}{34}
\newcommand{\antfivetex}{Ant5-ServeBone}
\newcommand{\antfiveinitial}{S}
\newcommand{\antfivetranslation}{Good and faithful servant, enter thou into the joy of thy Lord.\pagebreak}
\definepsalm{5}{131}{3}{g}
\newcommand{\prepsalmfive}{%
%\vspace{-1ex}
%\grechangestaffsize{15}%
\normalsize%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\chapter}{\dropcap{latin}{Ecce sacérdos} \textbf{má}\-gnus,~\dag{} qui in diébus suis plácuit Deo, et in\-vén\-\emph{tus est} \textbf{jú}\-stus~:~* et in témpore iracúndiæ factus est reconcili\textbf{á}tio.}
\newcommand{\chaptertranslation}{Behold a great priest, who in his days pleased God, and was found just; and in the time of wrath was made a reconciliation.}

\newcommand{\prehymn}{\normalsize
\grechangestaffsize{15}
}
\newcommand{\hymnlinetwo}{2.}
\newcommand{\hymntex}{Hymn-IsteConfessorDominiColentes.tex}
\newcommand{\hymninitial}{I}
\newcommand{\hymninitialsize}{33}
\newcommand{\hymntranslation}{
\item The faithful servant who confessed his Lord,
whose feast the Church's annual joys record,
this day in recompense is called to be
before thy Father, Lord, confessed by thee.
\item His humble prudence and his thoughts on high,
his pure and unpretending piety, by
blameless steps a sober life conveyed
till last it centred where it first was made.
\item Within his tomb lies all that heaven can spare;
hither the deaf, the blind, and lame repair;
his kind protection each disease restrains,
restores their losses, and relieves their pains.
\item Justly may then his praise bespeak our voice,
to join in consort, and with heaven rejoice.
So may we hope to have an equal share,
of his protection here, and merit there.
\item To God, in nature one, in persons three,
eternal glory, power and jubilee,
whose sovereign and universal throne
disposes all things with his word alone.
Amen.\grechangestaffsize{15}}

%\newcommand{\hymn}{O lux beata caelitum}
%mode 2
%\newcommand{\vr}{Notum fecit Dóminus}
\newcommand{\vrtex}{vrJustumDeduxit}
\newcommand{\vtranslation}{The Lord led the just by right ways. (\emph{T. P.} Alleluia.)}
\newcommand{\rtranslation}{And showed him the kingdom of God. (\emph{T. P.} Alleluia.)}
%\def\vrnospace{T}
