\newcommand{\antonetex}{an--quae_est_ista_speciosa--solesmes}
\newcommand{\antoneinitial}{Q}
\newcommand{\antonetranslation}{Who is this, fair as a dove, as the rose planted by the brooks of waters?}
\definepsalm{1}{109}{8}{G}

\newcommand{\anttwotex}{an--virgo_potens--solesmes}
\newcommand{\anttwoinitial}{V}
\newcommand{\anttwotranslation}{The Virgin, strong as the tower of David; a thousand bucklers hang upon it, all the armour of valiant men.}
\definepsalm{2}{112}{6}{F}

\newcommand{\antthreetex}{an--ave_maria--solesmes}
\newcommand{\antthreeinitial}{A}
\newcommand{\antthreetranslation}{Hail, Mary, full of grace, the Lord is with thee~: blessed art thou among women.}
\definepsalm{3}{121}{1}{g}

\newcommand{\antfourtex}{an--benedixit_te_dominus--solesmes}
\newcommand{\antfourinitial}{B}
\newcommand{\antfourtranslation}{The Lord hath blessed thee by his power, because by thee he hath brought our enemies to nought.}
\definepsalm{4}{126}{7}{a}

\newcommand{\antfivetex}{an--viderunt_eam_vernantem--solesmes}
\newcommand{\antfiveinitial}{V}
\newcommand{\antfivetranslation}{The daughters of Sion saw her, like the Spring with its roses, and declared her most blessed.}
\definepsalm{5}{147}{3}{a}

\newcommand{\chaptertext}{\dropcap{latin}{In me grátia omnis viæ et} ve\-ri\-\textbf{tá}\-tis,~\dag{} in me omnis spes vitæ \emph{et vir}\-\textbf{tú}\-tis~:~* ego quasi rosa plantáta super rivos aquárum fructifi\textbf{cá}vi.}
\newcommand{\chaptertranslation}{In me is all grace of the way and of the truth~: in me is all hope of life and of virtue~: I have budded forth as the rose planted by the brooks of waters.}

\newcommand{\hymnlinetwo}{2.}
\newcommand{\hymntex}{hy--te_gestientem_gaudiis--solesmes}
\newcommand{\hymninitial}{T}
\newcommand{\hymntranslation}{
\item Mother and Maid, the praise of thee
the burden of our song shall be;
thy joys, thy sorrows, and the crown
of thin eternal bright renown.

\item The heavenly tidings brought to earth,
the visitation and the birth,
Christ offered, Christ restored to thee,
hail, in each joyful mystery.

\item The bloody sweat, the soldiers' scorn,
the scourging and the crown of thorn,
the burdened way, the bitter tree,
hail, in each woeful mystery.

\item The risen and heaven ascending Lord,
the Pentecostal unction poured,
thy crown and endless jubilee,
hail, in each glorious mystery.

\item From these thy mysteries shall all
the faithful weave a coronal,
whose roseal honours shall proclaim
thy chaste and ever-lasting name.

\item May age to age for ever sing
the Virgin's Son and Angels' King,
and praise with the celestial host
the Father, Son, and Holy Ghost.
Amen.
}

\newcommand{\vrtex}{vrReginaSacratissimiRosarii}
\newcommand{\vtranslation}{Queen of the most holy Rosary, pray for us.}
\newcommand{\rtranslation}{That we may be made worthy of the promises of Christ.}

\newcommand{\collect}{Deus, cujus Unigénitus per vitam, mortem et resurrectiónem suam nobis salútis ætérnæ prǽmia comparávit~:~\dag{} concéde quǽsumus; ut hæc mystéria sacratíssimo beátæ Maríæ Vírginis Rosário recoléntes,~* et imitémur quod cóntinent, et quod promíttunt assequámur. Per eúmdem.}
\newcommand{\collecttranslation}{O God, whose only-begotten Son, by his life, death and resurrection, has purchased for us the rewards of eternal life~: grant, we beseech thee, that, meditating on these mysteries in the most holy Rosary of the blessed Virgin Mary, we may imitate what they contain, and obtain what they promise.  Through the same.}

\def\magsolemn{T}
