\newcommand{\antonetex}{Ant1-DumComplerentur}
\newcommand{\antoneinitial}{D}
\newcommand{\antonetranslation}{When the days of Pentecost were accomplished, they were all together, saying: Alleluia.}
\definepsalm{1}{109}{3}{a2}

\newcommand{\anttwotex}{Ant2-SpiritusDomini}
\newcommand{\anttwoinitial}{S}
\newcommand{\anttwotranslation}{The Spirit of the Lord hath filled the whole earth: alleluia.}
\definepsalm{2}{110}{8}{G}

\newcommand{\antthreetex}{Ant3-RepletiSuntOmnes}
\newcommand{\antthreeinitial}{R}
\newcommand{\antthreetranslation}{They were all filled with the Holy Ghost, and they began to speak, alleluia.}
\definepsalm{3}{111}{8}{G}

\newcommand{\antfourtex}{Ant4-Fontes}
\newcommand{\antfourinitial}{F}
\newcommand{\antfourtranslation}{O ye fountains, and all that move in the waters, sing a hymn to God, alleluia.}
\definepsalm{4}{112}{1}{a3}

\newcommand{\antfivetex}{Ant5-Loquebantur}
\newcommand{\antfiveinitial}{L}
\newcommand{\antfivetranslation}{The Apostles spoke in divers tongues the wonderful works of God, alleluia, alleluia, alleluia.}
%psalm 5 is different at 1st and 2nd vespers

\newcommand{\chaptertext}{\dropcap{latin}{Cum compleréntur dies Pentecóstes, erant omnes discípuli páriter in eódem} \textbf{lo}\-co~:~\gredagger{} et factus est repénte de cælo sonus, tamquam adveniéntis spíritus \emph{ve\-he}\-\textbf{mén}\-tis,~* et replévit totam domum ubi erant se\-\textbf{dén}\-tes.}
\newcommand{\chaptertranslation}{When the days of Pentecost were accomplished, they were all together in one place; and suddenly there came a sound from heaven as of a mighty wind coming, and it filled the whole house where they were sitting.}

\newcommand{\hymnlinetwo}{8.}
\newcommand{\hymntex}{Hymn-VeniCreatorSpiritus}
\newcommand{\hymninitial}{V}
\newcommand{\hymntranslation}{
\item Thou, Holy Ghost, Creater, come,
and make Thy people's souls Thy home:
with grace celestial animate
the hearts Thou didst Thyself create.

\item The Paraclete from God above,
Thou art His gift, Thou art His love:
the fount of life and burning zeal
and of our souls th'anointing seal.

\item As sevenfold Thy gifts expand,
the finger Thou of God's right hand:
the Father's promise well fulfilled,
Thy truths in us Thou hast instilled.

\item Our minds enkindle with Thy light,
within our hearts Thy love excite:
do Thou endue our members frail
with strength of Thine that ne'er can fail.

\item Far keep from us our ancient foe,
without delay Thy peace bestow:
be Thou our guide: do Thou forestall
the many ills our path entrall.

\item Through Thee may we the Father know,
the Son's effulgence deign to show:
in blessing Thee from either sent,
may our eternal years be spent!

\item To God the Father, to God the Son,
Who over death the vistory won,
to both and to the Paraclete,
we raise our hearts with thanks replete.
Amen.%\grechangestaffsize{15}
}

\def\magsolemn{T}
\definemag{1}{D}

\newcommand{\collect}{Deus, qui hodiérna die corda fidélium Sancti Spíritus illustratióne docuísti~:~\dag{} da nobis in eódem Spíritu recta sápere,~* et de ejus semper consolatióne gaudére. Per Dóminum nostrum\ldots in unitáte ejúsdem.}
\newcommand{\collecttranslation}{O God, who hast this day taught the hearts of the faithful by the light of the Holy Ghost: grant that, in the same Spirit, we may be truly wise and ever rejoice in His consolations. Through our Lord\ldots in the unity of the same.}
