%psalms, antiphons, chapter and hymn are all common

\newcommand{\preantone}{\setgrefactor{17}
\large
%\greblockcustos
\medskip
}
\newcommand{\antoneinitialsize}{40}
\newcommand{\antonetex}{Ant1-DomumTuamDomine}
\newcommand{\antoneinitial}{D}
\newcommand{\antonetranslation}{Holiness becometh thine house, O Lord, forever.}
\definepsalm{1}{109}{7}{a}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\setgrefactor{17}
%\greblockcustos
\large
}
\newcommand{\anttwoinitialsize}{40}
\newcommand{\anttwotex}{Ant2-DomusMea}
\newcommand{\anttwoinitial}{D}
\newcommand{\anttwotranslation}{My house shall be called the house of prayer.}
\definepsalm{2}{110}{1}{D2}
\newcommand{\prepsalmtwo}{%
\normalsize
\greblockcustos
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\setgrefactor{17}
\large
%\greblockcustos
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{Ant3-HaecEstDomusDomini}
\newcommand{\antthreeinitial}{H}
\newcommand{\antthreetranslation}{This is the Lord's house, stoutly builded, well founded upon a sure rock.}
\definepsalm{3}{111}{1}{f}
\newcommand{\prepsalmthree}{%
%\gdef\psalmclef{2}
%\greblockcustos
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\setgrefactor{17}
\greblockcustos
\large
%\normalsize
}
\newcommand{\antfourinitialsize}{40}
\newcommand{\antfourtex}{Ant4-BeneFundataEst}
\newcommand{\antfourinitial}{B}
\newcommand{\antfourtranslation}{The Lord's house is well founded upon a sure rock.}
\definepsalm{4}{112}{8}{c}
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\setgrefactor{15}
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\def\nopagebreakbeforepsalmfive{T}
%\def\pagebreakafterpsalmfive{T}
\newcommand{\preantfive}{\setgrefactor{17}
%\greblockcustos
\large
}
%\newcommand{\preantfivetwo}{\preantfive}
%\newcommand{\antfivefontsizetwo}{40}

\newcommand{\antfiveinitialsize}{40}
\newcommand{\antfivetex}{Ant5-LapidesPretiosi}
\newcommand{\antfiveinitial}{L}
\newcommand{\antfivetranslation}{All thy walls are of stones most precious, and the towers of Jerusalem shall be built up with jewels.}
\definepsalm{5}{147}{1}{g}
\newcommand{\prepsalmfive}{%
%\vspace{-1ex}
%\setgrefactor{15}%
%\normalsize%
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\pagebreakbeforehymn{T}

\newcommand{\prehymn}{\large
\setgrefactor{16}
}


\newcommand{\chapter}{\dropcap{latin}{Vidi civitátem sanctam Jerúsalem } \textbf{no}\-vam,~\dag{} descendéntem de cæ\-\emph{lo a} \textbf{De}\-o,~* parátam sicut sponsam ornátam viro \textbf{su}o.}
\newcommand{\chaptertranslation}{I saw the holy city, New Jerusalem, coming down from God out of heaven, prepared as a Bride adorned for her husband.}

\newcommand{\collect}{Deus, qui nobis per síngulos annos hujus sancti templi tui consecratiónis réparas diem, et sacris semper mystériis repræséntas incólumes~:~\dag{} exáudi preces pópuli tui, et præsta; ut quisquis hoc templum benefícia petitúrus ingréditur,~* cuncta se impetrásse lætétur. Per Dóminum nostrum.}
\newcommand{\collecttranslation}{O God, who every year dost bring round unto us the day whereon this thy holy temple was hallowed, and bringest us again uninjured to thy holy worship, graciously hear the prayers of thy people, and grant that whosoever shall come into this temple to ask favors, may be rejoiced in the obtaining of all his requests. Through our Lord.}

\newcommand{\hymnlinetwo}{1.}
\newcommand{\hymntex}{Hymn-CaelestisUrbsJerusalem}
\newcommand{\hymninitial}{C}
\newcommand{\hymntranslation}{
\item Thou heavenly, new Jerusalem,
Vision of peace in prophet's dream!
With living stones built up on high,
And rising to yon starry sky;
In bridal pomp thy form is crowned,
With thousand thousand angels round!

\item O bride, betrothed in happy hour,
The Father's glory is thy dower;
The bridegroom's grace is shed on thee
Thou queen all fair eternally;
To Christ allied, thy Prince adored,
Bright shining city of the Lord!

\item Behold with pearls they glittering stand
thy peaceful gates to all expand;
By grace and strength divinely shed
Each mortal thither may be led;
Who, kindled by Christ's love, will dare
All earthly sufferings now to bear.

\item By many a salutary stroke,
By many a weary blow that broke,
Or polished with a workman's skill,
The stones that form that glorious pile,
They all are fitly framed to lie
In their appointed place on high.

\item Fair and well pleasing in thy sight,
Parent most high, enthroned in light,
And for thine only Son most meet,
And thee, all-glorious Paraclete,
To whom praise, power, and glory rise
Forever through the eternal skies.
Amen.%\setgrefactor{15}
}
