\newcommand{\antonetex}{Ant1-DixitDominus}
\newcommand{\antoneinitial}{D}
\def\psalmonebeforeant{T} % this just means the title Psalm 109.
\def\psalmbeginversetwo{T}
\definepsalm{1}{109}{7}{c2}
\let\psalmonebeforeant=\undefined
\let\psalmbeginversetwo=\undefined

\newcommand{\anttwotex}{Ant2-MagnaOperaDomini}
\newcommand{\anttwoinitial}{M}
\newcommand{\anttwotranslation}{Great are the works of the Lord, sought out according to all His wills.}
\definepsalm{2}{110}{3}{b}

\newcommand{\antthreetex}{Ant3-QuiTimetDominum.tex}
\newcommand{\antthreeinitial}{Q}
\newcommand{\antthreetranslation}{He that feareth the Lord delighteth exceedingly in His commandments.}
\definepsalm{3}{111}{4}{g}

\newcommand{\antfourtex}{Ant4-SitNomenDomini.tex}
\newcommand{\antfourinitial}{S}
\newcommand{\antfourtranslation}{Blessed be the name of the Lord forever.\vspace{-2ex}}
\definepsalm{4}{112}{7}{c}

\newcommand{\antfivetex}{Ant5-DeusAutemNoster.tex}
\newcommand{\antfiveinitial}{D}
\newcommand{\antfivetranslation}{But our God is in heaven; He hath done all things, whatsoever He would.}
\definepsalm{5}{113}{p}{}

\newcommand{\chaptertext}{\dropcap{latin}{Benedíctus Déus, et Páter Dómini nóstri Jésu} \textbf{Chrí}\-sti.~\gredagger{} Páter misericordiárum, et Déus totíus con\-so\-\emph{la}\-\emph{ti}\-\textbf{ó}\-nis,~* qui consolátur nos in ómni tribulatióne \textbf{nó}\-stra.}
\newcommand{\chaptertranslation}{Blessed be the God and Father of our Lord Jesus Christ, the Father of mercies and the God of all comfort, who comforteth us in all our tribulation.}

\newcommand{\hymnlinetwo}{8.}
\newcommand{\hymntex}{hymn-LucisCreatorOptime.tex}
\newcommand{\hymninitial}{L}
\newcommand{\hymntranslation}{
\item O blest Creator of the Light!
Who dost the dawn from darkness bring:
And, framing Nature's depth and height,
Didst with the light thy work begin;
\item Who gently blending eve with morn,
And morn with eve, didst call them day;
Thick flows the flood of darkness down;
O hear us as we weep and pray.
\item Keep thou our souls from schemes of crime;
Nor guilt remorseful let them know;
Nor, thinking but on things of time,
Into eternal darkness go.
\item Teach us to knock at heaven's high door;
Teach us the prize of life to win;
Teach us all evil to abhor,
And purify ourselves within.
\item Father of mercies, hear our cry;
Hear us, O sole-begotten Son,
Who, with the Holy Ghost most high,
Reignest while endless ages run.
Amen.
}

\newcommand{\vrtex}{Dirigaturvr}
\newcommand{\vtranslation}{Let my prayer be directed, O Lord.}
\newcommand{\rtranslation}{As incense in Thy sight.}
