% page 591,597 in pdf
% page 445,451 in liber

% only mag antiphon is different

% 2nd class

\newcommand{\predeusinadjutorium}{%
%\smallskip
\large
\setgrefactor{15}
}
\def\deusinadjutoriumsolemn{F}
\def\includelaustibi{F}

\newcommand{\preantone}{\setgrefactor{17}
\large
\greblockcustos
\medskip
}


\newcommand{\antoneinitialsize}{40}
\newcommand{\antonetex}{an--omnis_qui_invocaverit--solesmes}
\newcommand{\antoneinitial}{O}
\newcommand{\antonetranslation}{All who shall call on the name of the Lord shall be saved.}
\definepsalm{1}{109}{8}{G}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\setgrefactor{17}
\greblockcustos
\large
}
\newcommand{\anttwoinitialsize}{40}
\newcommand{\anttwotex}{an--sanctum_et_terribile--solesmes}
\newcommand{\anttwoinitial}{S}
\newcommand{\anttwotranslation}{Holy and terrible is His name; the fear of the Lord is the beginning of wisdom.}
\definepsalm{2}{110}{5}{a}
\newcommand{\prepsalmtwo}{%
\normalsize
\greblockcustos
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\setgrefactor{17}
\large
\greblockcustos
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{an--ego_autem_in_domino--solesmes}
\newcommand{\antthreeinitial}{E}
\newcommand{\antthreetranslation}{Yet I will rejoice in the Lord and exult in the God of my salvation.}
\definepsalm{3}{111}{3}{a2}
\newcommand{\prepsalmthree}{%
%\greblockcustos
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\setgrefactor{17}
%\greblockcustos
\large
%\normalsize
}
\newcommand{\antfourinitialsize}{40}
\newcommand{\antfourtex}{an--a_solis_ortu--solesmes}
\newcommand{\antfourinitial}{A}
\newcommand{\antfourtranslation}{From the rising of the sun unto the going down of the same the Lord's Name is to be praised.}
\definepsalm{4}{112}{4}{E}
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\setgrefactor{15}
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\def\nopagebreakbeforepsalmfive{T}
%\def\pagebreakafterpsalmfive{T}
\newcommand{\preantfive}{\setgrefactor{17}
\greblockcustos
\large
}
%\newcommand{\preantfivetwo}{\preantfive}
%\newcommand{\antfivefontsizetwo}{40}

\newcommand{\antfiveinitialsize}{40}
\newcommand{\antfivetex}{an--sacrificabo_hostiam--solesmes}
\newcommand{\antfiveinitial}{S}
\newcommand{\antfivetranslation}{I will offer the sacrifice of thanksgiving, and will call upon the Name of the Lord.}
\newcommand{\psalmcleffive}{2}
\definepsalm{5}{115}{8}{c}
\newcommand{\prepsalmfive}{%
%\vspace{-1ex}
%\setgrefactor{15}%
%\normalsize%
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\pagebreakbeforehymn{T}

\newcommand{\prehymn}{\large
\setgrefactor{16}
}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Christus humiliávit semetípsum, factus obédiens usque ad mortem, mortem autem} \textbf{crú}\-cis.~\dag{} Propter quod et Deus exaltávit illum, et donávit illi nomen quod est super \emph{om\-ne} \textbf{nó}\-men~:~* ut in nómine Jesu omne genu flec\textbf{tá}tur.}
\newcommand{\chaptertranslation}{Christ humbled Himself, becoming obedient unto death, even to the death of the cross. For which cause God also hath exalted Him, and hath given Him a name which is above all names: That in the name of Jesus every knee should bow.}

\newcommand{\hymnlinetwo}{1.}
\newcommand{\hymntex}{hy--jesu_dulcis_memoria--solesmes}
\newcommand{\hymninitial}{J}
\newcommand{\hymntranslation}{
\item Jesu, the very thought of thee
With sweetness fills my breast;
But sweeter far thy face to see,
And in thy presence rest.

\item Nor voice can sing, nor heart can frame,
Nor can the memory find,
A sweeter sound than thy blest Name,
O Saviour of mankind!

\item O Hope of every contrite heart,
O Joy of all the meek,
To those who fall, how kind Thou art!
How good to those who seek!

\item But what to those who find? Ah! this
Nor tongue nor pen can show:
The love of Jesus, what it is
None but his loved ones know.

\item Jesu, our only joy be Thou,
As Thou our prize wilt be;
Jesu, be Thou our glory now,
And through eternity.
Amen.%\setgrefactor{15}
}

\newcommand{\vrtex}{vrSitNomenDominiBenedictum}
\newcommand{\vtranslation}{Blessed be the Name of the Lord, alleluia.}
\newcommand{\rtranslation}{From this time forth, and for evermore, alleluia.}
\newcommand{\vrnospace}{F}


\newcommand{\collect}{Deus, qui unigénitum Fílium tuum constituísti humáni géneris Salvatórem, et Jesum vocári jussísti~:~\dag{} concéde propítius~; ut, cujus sanctum nomen venerámur in terris,~* ejus quoque aspéctu perfruámur in cælis. Per eúmdem Dóminum.}
\newcommand{\collecttranslation}{O God, who hast appointed thine Only-begotten Son to be the Savior of mankind, and commanded that His Name should be called Jesus, mercifully grant that we who here on earth do worship that most Holy Name may be made glad in heaven by His Presence. Through the same our Lord.}

\def\benedicamusdominogrefactor{17}
