\newcommand{\preantone}{\grechangestaffsize{17}
\large
%\greseteolcustos{manual}
\medskip
}


\newcommand{\antoneinitialsize}{40}
\newcommand{\antonetex}{Ant1-OMagnum}
\newcommand{\antoneinitial}{O}
\newcommand{\antonetranslation}{O what a work of love was that when Life and death died together upon the Tree.}
\definepsalm{1}{109}{7}{c}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\grechangestaffsize{17}
%\greseteolcustos{manual}
\large
}
\newcommand{\anttwoinitialsize}{40}
\newcommand{\anttwotex}{Ant2-SalvaNos}
\newcommand{\anttwoinitial}{S}
\newcommand{\anttwotranslation}{Save us, O Christ the Saviour, save us through the might of Thy Cross Thou Who didst save Peter when he was ready to sink in the sea, have mercy upon us.}
\definepsalm{2}{110}{3}{a}
\newcommand{\prepsalmtwo}{%
\normalsize
\greseteolcustos{manual}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\grechangestaffsize{17}
\large
%\greseteolcustos{manual}
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{Ant3-EcceCrucemDomini}
\newcommand{\antthreeinitial}{E}
\newcommand{\antthreetranslation}{Behold the Cross of the Lord, fly, ye ranks of the adversary, the Lion of the tribe of Judah, the Root of David, hath prevailed. Alleluia.}
\definepsalm{3}{111}{1}{f}
\newcommand{\prepsalmthree}{%
%\gdef\psalmclef{2}
%\greseteolcustos{manual}
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\grechangestaffsize{17}
\greseteolcustos{manual}
\large
%\normalsize
}
\newcommand{\antfourinitialsize}{40}
\newcommand{\antfourtex}{Ant4-NosAutem}
\newcommand{\antfourinitial}{N}
\newcommand{\antfourtranslation}{But us it behoveth to glory in the Cross of our Lord Jesus Christ.}
\definepsalm{4}{112}{7}{c}
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\grechangestaffsize{15}
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\def\nopagebreakbeforepsalmfive{T}
%\def\pagebreakafterpsalmfive{T}
\newcommand{\preantfive}{\grechangestaffsize{17}
\greseteolcustos{manual}
\large
}
%\newcommand{\preantfivetwo}{\preantfive}
%\newcommand{\antfivefontsizetwo}{40}

\newcommand{\antfiveinitialsize}{40}
\newcommand{\antfivetex}{Ant5-PerSignumCrucis}
\newcommand{\antfiveinitial}{P}
\newcommand{\antfivetranslation}{By the Cross' sign, O our God, free us from our enemies.}
\definepsalm{5}{116}{8}{c}
\newcommand{\prepsalmfive}{%
%\vspace{-1ex}
%\grechangestaffsize{15}%
%\normalsize%
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\chapter}{\dropcap{latin}{Fratres : Hoc enim sentíte in vobis, quod et in Christo Jesu~: qui cum in forma Dei esset, non rapínam arbitrátus est esse se æquálem } \textbf{De}\-o~:~\dag{} sed semetípsum exinanívit, formam servi accípiens, in similitúdinem hó\-\emph{mi\-num} \textbf{fa}\-ctus,~* et hábitu invéntus ut \textbf{ho}mo.}
\newcommand{\chaptertranslation}{For let this mind be in you, which was also in Christ Jesus: Who being in the form of God, thought it not robbery to be equal with God: But emptied himself, taking the form of a servant, being made in the likeness of men, and in habit found as a man.}

\newcommand{\collect}{Deus, qui nos hodiérna die Exaltatiónis sanctæ Crucis ánnua solemnitáte lætíficas~:~\dag{} præsta quæsumus; ut cujus mystérium in terra cognóvimus,~* ejus redemptiónis præmia in cælo mereámur. Per eúmdem Dóminum.}
\newcommand{\collecttranslation}{O God, Who dost this day gladden us by the yearly Feast of the Exaltation of the Holy Cross, grant, we beseech thee, that as we have understood the mystery thereof upon earth, so we may worthily enjoy in heaven the fruits of the redemption which was paid thereon. Through the same Lord.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\pagebreakbeforehymn{F}

\newcommand{\prehymn}{\large
\grechangestaffsize{16}
}

\newcommand{\vrtex}{vrHocSignumCrucis}
\newcommand{\vtranslation}{This sign of the Cross shall be in heaven.}
\newcommand{\rtranslation}{When the Lord cometh to judgement.}
\newcommand{\vrnospace}{F}

\newcommand{\hymnlinetwo}{1.}
\newcommand{\hymntex}{Hymn-VexillaRegis}
\newcommand{\hymninitial}{V}
\newcommand{\hymntranslation}{\item Forth comes the Standard of the King:
All hail, thou Mystery ador'd!
Hail, Cross! on which the Life Himself
Died, and by death our life restor'd!
\item On which our Saviour's holy side
Rent open with a cruel spear
Of blood and water poured a stream,
To wash us from defilement clear.
\item O sacred wood! in Thee fulfill'd
Was holy David's truthful lay!
Which told the world, that from a tree
The Lord should all the nations sway.
\item Most royally empurpled o'er,
How beauteously thy stem doth shine!
How glorious was its lot to touch
Those limbs so holy and divine!
\item Thrice blest, upon whose arms outstretched
The Saviour of the world reclined;
Balance sublime! upon whose beam
Was weighed the ransom of mankind.
\item Hail, Cross! thou only hope of man,
In this glory of triumph
To saints increase the grace they have;
From sinners purge their guilt away.
\item Salvation's spring, blest Trinity,
Be praise to Thee through earth and skies:
Thou through the Cross the victory
Dost give; oh, also give the prize!
Amen.%\grechangestaffsize{15}
}
