% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.
\usepackage{../definepsalms}

\sloppy

\newcommand{\predeusinadjutorium}{%
%\smallskip
\large
\setgrefactor{15}
}
\def\deusinadjutoriumsolemn{T}

\newcommand{\preantone}{\setgrefactor{17}
\large
%\greblockcustos
}

\newcommand{\antoneinitialsize}{40}
\newcommand{\antonetex}{Ant1-StetitAngelus}
\newcommand{\antoneinitial}{S}
\newcommand{\antonetranslation}{An Angel stood near the altar of the temple, holding a golden censer in his hand.}
\definepsalm{1}{109}{4}{A*}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\setgrefactor{17}
%\greblockcustos
\large
}
\newcommand{\anttwoinitialsize}{40}
\newcommand{\anttwotex}{Ant2-DumPraeliaretur}
\newcommand{\anttwoinitial}{D}
\newcommand{\anttwotranslation}{As the Archangel Michael was fighting with the dragon, the voice of a multitude was heard crying: Salvation unto our God.  Alleluia.\vspace{-1ex}}
\definepsalm{2}{110}{7}{a}
\newcommand{\prepsalmtwo}{%
\normalsize
\greblockcustos
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\setgrefactor{17}
\large
%\greblockcustos
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{Ant3-ArchangeleMichael}
\newcommand{\antthreeinitial}{A}
\newcommand{\antthreetranslation}{O Archangel Michael, I have made thee a prince, that thou mayest receive the souls of all.}
\definepsalm{3}{111}{8}{G}
\newcommand{\prepsalmthree}{%
\normalsize
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\setgrefactor{17}
\greblockcustos
\large
%\normalsize
}
\newcommand{\antfourinitialsize}{40}
\newcommand{\antfourtex}{Ant4-AngeliDomini}
\newcommand{\antfourinitial}{A}
\newcommand{\antfourtranslation}{\vspace{0ex minus 3.5ex}O ye Angels of the Lord, bless ye the Lord for ever.\vspace{0ex minus 3.5ex}}
\definepsalm{4}{112}{p}{}
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\setgrefactor{15}
\normalsize
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\def\nopagebreakbeforepsalmfive{T}
%\def\pagebreakafterpsalmfive{T}
\newcommand{\preantfive}{\setgrefactor{17}
%\greblockcustos
\large
}
%\newcommand{\preantfivetwo}{\preantfive}
\newcommand{\antfivefontsizetwo}{40}

\newcommand{\antfiveinitialsize}{40}
\newcommand{\antfivetex}{Ant5-AngeliArchangeli}
\newcommand{\antfiveinitial}{A}
\newcommand{\antfivetranslation}{\vspace{-2ex}Angels and Archangels, Thrones and Dominations, Principalities and Powers, all ye hosts of heaven, praise ye the Lord of heaven.  Alleluia.\vspace{-1ex}}
%\definepsalm{5}{137}{7}{c}
\newcommand{\prepsalmfive}{%
\greblockcustos
\vspace{-12pt}
%\setgrefactor{15}%
%\normalsize%
}
\def\pagebreakafterpsalmfive{T}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\chapter}{\dropcap{latin}{Significávit Deus quæ opórtet fíeri} \textbf{ci}\-to,~\dag{} loquens per Angelum suum servo suo Joánni, qui testimónium per\-hí\-bu\-it \emph{ver\-bo} \textbf{De}\-i,~* et testimónium Jesu Chrísti, quæcúmque \textbf{vi}\-dit.}
\newcommand{\chaptertranslation}{God signified the things which must shortly come to pass, speaking through His Angel to His servant John, who hath given testimony to the word of God and the testimony of Jesus Christ, what things soever he hath seen.}

\newcommand{\prehymn}{\normalsize
\setgrefactor{15}
}
\def\hymninitialsize{30}
\newcommand{\hymnlinetwo}{8.}
\newcommand{\hymntex}{Hymn-TeSplendorEtVirtusPatris}
\newcommand{\hymninitial}{T}
\newcommand{\hymntranslation}{
\item O Thou, the Father's glorious Might,
Jesus, true life of ev'ry heart,
Thee do we praise 'mid Angels bright
Whose hope and light alone Thou art.

\item A thousand thousand hosts, for Thee,
Of glorious warriors, battle wage;
But Michael waves Thy standard free,
Salvation's cross and vict'ry's gage.

\item The dragon fierce with stubborn crown
He hurls to lowest depths of hell;
The rebel crew, their prince o'erthrown,
He thrusts from Heav'ns high citadel.

\item The prince of pride may we, too, fight,
And follow this, our captain true,
That so the crown with glory dight
By Jesus given, may be our due.

\item Glory be to God the Father,
Who protects by His Angels,
Those whom the Son redeemeth
And the Holy Ghost anointeth. Amen.%\setgrefactor{15}
}

%\def\vrnospace{T}

\newcommand{\premag}{
\normalsize
\setgrefactor{16}
%\greblockcustos
}
%\newcommand{\premagtwo}{
%\setgrefactor{16}
%}
%\newcommand{\maganttex}{MagnificatAntiphon2}
\newcommand{\magfontsize}{34}
\def\pagebreakbeforemagnificat{T}
\def\magsolemn{T}
\def\magoneline{T}
\newcommand{\premagverses}{%
%\greblockcustos
\normalsize
\setgrefactor{14}
%\pagebreak
}
%\input{../psalms/definemag}

\newcommand{\collect}{Deus, qui miro órdine Angelórum ministéria hominúmque dispénsas~:~\dag{} concéde propítius; ut a quibus tibi ministrántibus in cælo semper assístitur,~* ab his in terra vita nostra muniátur. Per Dóminum nostrum.}
\newcommand{\collecttranslation}{O God, who hast constituted the services of Angels and of men in a wonderful order, mercifully grant, that they who ever stand before Thy face to do Thee service in heaven, may also defend our life upon earth. Through our Lord.}

%\definebenedicamusdomino{1}{2}

\def\includefideliumanimae{T}

%\input{../FullVespers}
