% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

\newcommand{\predocument}{\setgrefactor{17}}

\newcommand{\heading}{Alma Redemptoris Mater}
\newcommand{\firstinitial}{A}
\newcommand{\timenote}{From Vespers of Saturday before the 1st Sunday of Advent to 2nd Vespers of the Purification.}
\newcommand{\anttranslation}{Mother of Christ! hear thou thy people's cry
Star of the deep, and portal of the sky!
Mother of Him who thee from nothing made,
Sinking we strive and call to thee for aid;
Oh, by that joy which Gabriel brought to thee,
Thou Virgin first and last, let us thy mercy see.}

\newcommand{\presolemn}{%
%\setspaceafterinitial{0mm plus 0em minus 0em}
%\setspacebeforeinitial{0mm plus 0em minus 0em}

%\redlines
}
\newcommand{\solemninitialsize}{40}
\newcommand{\secondlinesolemn}{5.}

\newcommand{\antfilename}{Alma}

\newcommand{\presimple}{}
\newcommand{\simpleinitialsize}{40}
\newcommand{\annotationsimple}{5.}

\newcommand{\note}{During Advent:}
\newcommand{\vlatin}{Angelus Dómini nuntiávit Maríæ.}
\newcommand{\venglish}{The Angel of the Lord declared unto Mary.}
\newcommand{\rlatin}{Et concépit de Spíritu Sancto.}
\newcommand{\renglish}{And she conceived by the Holy Ghost.}
\newcommand{\prayerlatin}{Grátiam tuam, quaésumus Dómine, méntibus nostris infúnde~:~\dag{} ut qui, Angelo nuntiánte, Christi Fílii tui incarnatiónem cognóvimus,~* per passiónem ejus et crucem ad resurrectiónis glóriam perducámur.  Per eúmdem Christum Dóminum nostrum. \Rbar~Amen.}
\newcommand{\prayerenglish}{Pour forth, we beseech Thee, O Lord, Thy grace into our hearts; that we, to whom the Incarnation of Christ Thy Son was made known by the message of an Angel, may, by His Passion and Cross, be brought to the glory of His Resurrection. Through the same Christ our Lord. \Rbar~Amen.}

\newcommand{\notetwo}{From 1st Vespers of Christmas to 2nd Vespers of the Purification:}
\newcommand{\vlatintwo}{Post pártum Vírgo invioláta permansísti.}
\newcommand{\venglishtwo}{After childbirth thou didst remain a pure Virgin.}
\newcommand{\rlatintwo}{Déi Génitrix intercéde pro nóbis.}
\newcommand{\renglishtwo}{Intercede for us, O Mother of God.}
\newcommand{\prayerlatintwo}{Deus, qui salútis ætérnæ, beátæ Maríæ virginitáte f\oe cúnda, humáno géneri praémia præstitísti~:~\dag{} tríbue, quaésumus; ut ipsam pro nobis intercédere sentiámus,~* per quam merúimus auctórem vitæ suscípere, Dóminum nostrum Jesum Christum Fílium tuum. \Rbar~Amen.}
\newcommand{\prayerenglishtwo}{O God, who, by the fruitful virginity of blessed Mary, hast given to mankind the rewards of eternal salvation; grant, we beseech Thee, that we may experience her intercession for us, through whom we have deserved to receive the Author of life, our Lord Jesus Christ, Thy Son. \Rbar~Amen.}

\def\usetwopages{T}

\input{MarianAntiphon}
