% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

\newcommand{\predocument}{\setgrefactor{17}}

\newcommand{\heading}{Salve Regina}
\newcommand{\firstinitial}{S}
\newcommand{\timenote}{From 1st Vespers of the Feast of the Blessed Trinity to None on Saturday before the 1st Sunday of Advent.}
\newcommand{\anttranslation}{Hail, holy Queen, Mother of mercy; hail, our life, our sweetness, and our hope! To thee do we cry, poor banished children of Eve; to thee do we send up our sighs, mourning and weeping in this vale of tears.  Turn then, most gracious advocate, thine eyes of mercy towards us; and after this our exile, show unto us the blessed fruit of thy womb, Jesus.  O clement, O loving, O sweet Virgin Mary.}

\newcommand{\presolemn}{%
%\setspaceafterinitial{1.5mm plus 0em minus 0em}
%\setspacebeforeinitial{1.5mm plus 0em minus 0em}

%\redlines
}
\newcommand{\solemninitialsize}{40}
\newcommand{\secondlinesolemn}{1.}

\newcommand{\antfilename}{SalveRegina}

\newcommand{\presimple}{}
\newcommand{\simpleinitialsize}{40}
\newcommand{\annotationsimple}{5.}

\newcommand{\vlatin}{Ora pro nóbis sáncta Déi Génitrix.}
\newcommand{\venglish}{ Pray for us, O holy Mother of God.}
\newcommand{\rlatin}{Ut dígni efficiámur promissiónibus Chrísti.}
\newcommand{\renglish}{That we may be made worthy of the promises of Christ.}
\newcommand{\prayerlatin}{Omnípotens sempitérne Deus, qui gloriósæ Vírginis Matris Maríæ corpus et ánimam, ut dignum Fílii tui habitáculum éffici mererétur, Spíritu Sancto cooperánte præparásti~:~\gredagger{} da, ut cujus commemoratióne lætámur,~* ejus pia intercessióne ab instántibus malis et a morte perpétua liberémur. Per eúmdem Christum Dóminum nostrum. \Rbar~Amen.}
\newcommand{\prayerenglish}{Almighty, everlasting God, who with the cooperation of the Holy Ghost didst prepare the body and soul of the glorious Virgin Mary, to make it fit to be the worthy dwelling of Thy Son; grant that by the loving intercession of her in whose commemoration we rejoice, we may be delivered from present ills, and from everlasting death.  Through the same Christ our Lord. \Rbar~Amen.}

\def\usetwopages{T}

\input{MarianAntiphon}
