% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt

\newcommand{\heading}{The Circumcision of Our Lord at 2nd Vespers.}
\sloppy

\newcommand{\predeusinadjutorium}{%
%\smallskip
\large
\setgrefactor{15}
}
\def\deusinadjutoriumsolemn{F}

\newcommand{\preantone}{\setgrefactor{15}
\normalsize
%\greblockcustos
}
\newcommand{\antoneinitialsize}{33}
\newcommand{\antonetex}{Ant1-OAdmirabileCommercium}
\newcommand{\antoneinitial}{O}
\newcommand{\antonetranslation}{\vspace{-18pt}O wondrous interchange: the Creator of the human race, taking unto Himself a living body, deigns to be born of a Virgin: and becoming man from no human seed, hath bestowed upon us His Divinity.\vspace{0ex plus 0ex minus 3ex}}
\newcommand{\psalmonenum}{109}
\newcommand{\psalmonetone}{6}
\newcommand{\psalmoneend}{F}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}
\newenvironment{psalmonecols}{\begin{parcolumns}[rulebetween]{2}}{\end{parcolumns}}
\input{../psalms/definepsalmone}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\setgrefactor{15}
%\greblockcustos
\normalsize
}
\newcommand{\anttwoinitialsize}{33}
\newcommand{\anttwotex}{Ant2-QuandoNatusEs}
\newcommand{\anttwoinitial}{Q}
\newcommand{\anttwotranslation}{When Thou wast born in an ineffable manner of a Virgin, then were the Scriptures fulfilled: Thou camest down like rain upon the fleece to save the human race: we praise Thee, O our God.}
\newcommand{\psalmtwonum}{110}
\newcommand{\psalmtwotone}{3}
\newcommand{\psalmtwoend}{a2}
\newcommand{\prepsalmtwo}{%
\normalsize
\greblockcustos
}
\newenvironment{psalmtwocols}{\begin{parcolumns}[rulebetween]{2}}{\end{parcolumns}}
\input{../psalms/definepsalmtwo}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\setgrefactor{17}
\large
%\greblockcustos
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{Ant3-RubumQuemViderat}
\newcommand{\antthreeinitial}{R}
\newcommand{\antthreetranslation}{In the bush which Moses saw was not burnt, we acknowledge the figure of thy glorious virginity: Mother of God, intercede for us.}
\newcommand{\psalmthreenum}{121}
\newcommand{\psalmthreetone}{4}
\newcommand{\psalmthreeend}{E}
\newcommand{\prepsalmthree}{%
\normalsize
}
\newenvironment{psalmthreecols}{\begin{parcolumns}[rulebetween,colwidths={1=252pt}]{2}}{\end{parcolumns}}
\input{../psalms/definepsalmthree}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\setgrefactor{15}
%\greblockcustos
%\large
\normalsize
}
\newcommand{\antfourinitialsize}{34}
\newcommand{\antfourtex}{Ant4-Germinavit}
\newcommand{\antfourinitial}{G}
\newcommand{\antfourtranslation}{\vspace{0ex minus 3.5ex}The root of Jesse hath budded: the Star is risen out of Jacob: the Virgin hath brought forth the Saviour: We praise Thee, O our God.\vspace{0ex minus 3.5ex}}
\newcommand{\psalmfournum}{126}
\newcommand{\psalmfourtone}{1}
\newcommand{\psalmfourend}{f}
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\setgrefactor{15}
\normalsize
}
\newenvironment{psalmfourcols}{\begin{parcolumns}[rulebetween,colwidths={1=290pt}]{2}}{\end{parcolumns}}
\input{../psalms/definepsalmfour}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\def\nopagebreakbeforepsalmfive{T}
%\def\pagebreakafterpsalmfive{T}
\newcommand{\preantfive}{\setgrefactor{15}
%\greblockcustos
\normalsize
}
%\newcommand{\preantfivetwo}{\preantfive}
\newcommand{\antfivefontsizetwo}{34}

\newcommand{\antfiveinitialsize}{34}
\newcommand{\antfivetex}{Ant5-EcceMaria}
\newcommand{\antfiveinitial}{E}
\newcommand{\antfivetranslation}{\vspace{0pt minus 1ex}Behold Mary hath brought forth unto us the Saviour, whom when John saw, he cried out: Behold the Lamb of God, behold Him who takes away the sins of the world, alleluia.}
\newcommand{\psalmfivenum}{147}
\newcommand{\psalmfivetone}{2}
\newcommand{\psalmfiveend}{D}
\newcommand{\prepsalmfive}{%
%\vspace{-1ex}
%\setgrefactor{15}%
\normalsize%
}
\newenvironment{psalmfivecols}{\begin{parcolumns}[rulebetween%,colwidths={1=266pt}
]{2}}{\end{parcolumns}}
\input{../psalms/definepsalmfive}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\chapter}{\dropcap{latin}{Appáruit grátia Dei Salvatóris nóstri ómnibus}{ho\-\textbf{mí}\-ni\-bus,~\dag{} erúdiens nos, ut abnegántes impietátem et sæculária \emph{de\-si}\-\textbf{dé}\-ri\-a,~* sóbrie, et juste, et pie vivámus in hoc \textbf{saé}\-cu\-lo.}}
\newcommand{\chaptertranslation}{The grace of God our Saviour hath appeared to all men, instructing us, that denying ungodliness and worldly desires, we should live soberly and justly and godly in this world.}

\newcommand{\hymn}{Jesu Redémptor ómnium}
%\newcommand{\vr}{Notum fecit Dóminus}
\newcommand{\vrtex}{vrNotumFecitDominus}
\newcommand{\vtranslation}{The Lord hath made known, alleluia.}
\newcommand{\rtranslation}{His salvation, alleluia.}
\def\vrnospace{T}

\newcommand{\premag}{
\large
\setgrefactor{15}
}
%\newcommand{\premagtwo}{
%\setgrefactor{16}
%}
\newcommand{\magfontsize}{33}
\newcommand{\magantinitial}{M}
\newcommand{\maganttranslation}{O mighty mystery of generation: the womb of her who knew not man is become the temple of God: He who takes flesh from her is not defiled: all nations shall come, and say: Glory be to Thee, O Lord.}
\newcommand{\magtone}{2}
\newcommand{\magend}{A}
\def\magsolemn{T}
\def\magoneline{F}
\newcommand{\premagverses}{\greblockcustos\setgrefactor{15}
\normalsize
%\pagebreak
}
\input{../psalms/definemag}

\newcommand{\collect}{Deus, qui salútis ætérnæ, beátæ Maríæ virginitáte fecúnda, humáno géneri praémia præstitísti~:~\dag{} tríbue quaésumus; ut ipsam pro nobis intercédere sentiámus,~* per quam merúimus auctórem vitæ suscípere, Dóminum nostrum Jesum Christum Fílium tuum.  Qui tecum vivit.}
\newcommand{\collecttranslation}{O God, who by the fruitful virginity of blessed Mary hast bestowed upon mankind the rewards of eternal salvation: grant, we beseech Thee, that we may experience her intercession for us, through whom we have been made worthy to receive the Author of Life, Jesus Christ Thy Son, our Lord.}

\newcommand{\benedicamusdominotone}{8.}
\newcommand{\benedicamusdominotex}{../BenedicamusDomino/BenedicamusDomino_2class2ndVespers}
%\newcommand{\benedicamusdominotonealt}{5.}
%\newcommand{\benedicamusdominotexalt}{../BenedicamusDomino/BenedicamusDomino_1class2ndvespersAlt}

\input{../FullVespers}
