\newcommand{\chaptertext}{\dropcap{latin}{Appáruit grátia Dei Salvatóris nóstri ómnibus} ho\-\textbf{mí}\-ni\-bus,~\dag{} erúdiens nos, ut abnegántes impietátem et sæculária \emph{de\-si}\-\textbf{dé}\-ri\-a,~* sóbrie, et juste, et pie vivámus in hoc \textbf{sǽ}\-cu\-lo.}
\newcommand{\chaptertranslation}{The grace of God our Saviour hath appeared to all men, instructing us, that denying ungodliness and worldly desires, we should live soberly and justly and godly in this world.}

\newcommand{\vrtex}{vrNotumFecitDominus}
\newcommand{\vtranslation}{The Lord hath made known, alleluia.}
\newcommand{\rtranslation}{His salvation, alleluia.}

\newcommand{\maganttex}{MagnificatAntiphon}
\newcommand{\magantinitial}{M}
\newcommand{\maganttranslation}{Great the mystery of our inheritance: the womb that knew not man is become the temple of God: taking flesh from her, he is not defiled: all nations shall come, and say: Glory to Thee, O Lord.}
\def\magsolemn{T}
\definemag{2}{A}

\newcommand{\collect}{Deus, qui salútis ætérnæ, beátæ Maríæ virginitáte fecúnda, humáno géneri prǽmia præstitísti~:~\dag{} tríbue quǽsumus; ut ipsam pro nobis intercédere sentiámus,~* per quam merúimus auctórem vitæ suscípere, Dóminum nostrum Jesum Christum Fílium tuum.  Qui tecum vivit.}
\newcommand{\collecttranslation}{O God, who by the fruitful virginity of blessed Mary hast bestowed upon mankind the rewards of eternal salvation: grant, we beseech Thee, that we may experience her intercession for us, through whom we have been made worthy to receive the Author of Life, Jesus Christ Thy Son, our Lord.}
