\newcommand{\antonetex}{an--placebo_domino--solesmes}
\newcommand{\antoneinitial}{P}
\newcommand{\antonetranslation}{I will please the Lord in the land of the living.}
\definepsalm{1}{114}{3}{b}

\newcommand{\anttwotex}{an--heu_me_domine--solesmes}
\newcommand{\anttwoinitial}{H}
\newcommand{\anttwotranslation}{Woe is me, that my sojourning is prolonged.}
\definepsalm{2}{119}{2}{D}

\newcommand{\antthreetex}{an--dominus_custodit_te--solesmes}
\newcommand{\antthreeinitial}{D}
\newcommand{\antthreetranslation}{The Lord keepeth thee from all evil~: may the Lord keep thy soul.}
\definepsalm{3}{120}{8}{G}

\newcommand{\antfourtex}{an--si_iniquitates--solesmes}
\newcommand{\antfourinitial}{S}
\newcommand{\antfourtranslation}{If thou, O Lord, wilt mark iniquities~: Lord, who shall stand it?}
\definepsalm{4}{129}{8}{G}

\newcommand{\antfivetex}{an--opera_manuum_tuarum--solesmes}
\newcommand{\antfiveinitial}{O}
\newcommand{\antfivetranslation}{O Lord, despise not the works of thy hands.}
\definepsalm{5}{137}{2}{D}

\def\chapterreplacement{}

\newcommand{\vrtex}{vrAudiviVocem}
\newcommand{\vtranslation}{I heard a voice from heaven, saying to me.}
\newcommand{\rtranslation}{Blessed are the dead who die in the Lord.}

\def\magsolemn{F}

\newcommand{\maganttex}{an--omne_quod_dat_mihi--solesmes}
\newcommand{\magantinitial}{O}
\newcommand{\maganttranslation}{All that the Father giveth to me shall come to me~: and him that cometh to me, I will not cast out.}
\definemag{7}{c}

\newcommand{\collect}{Deus véniæ largítor et humánæ salútis amátor~:~\dag{} quǽsumus cleméntiam tuam; ut nostræ congregatiónis fratres, propínquos et benefactóres, qui ex hoc sǽculo transiérunt,~* beáta María semper Vírgine intercedénte cum ómnibus Sanctis tuis, ad perpétuæ beatitúdinis consórtium perveníre concédas.  Per Dóminum.}
\newcommand{\collecttranslation}{O God, who art ever ready to forgive sins and who ever seekest the salvation of men~: we most humbly entreat, of thy mercy, that through the intercession of blessed Mary ever Virgin and of all thy Saints, the brethren, friends and benefactors of our congregation, who have passed out of this world, may together enjoy that happiness which has no end.  Through.}

