{
\ifthenelse{\boolean{includepolyphony}}{
  \newcommand{\printprayernote}{
    \textit{Prayer on page \pageref{\prayerlabel}}.
  }
  \newcommand{\afterant}[1][F]{
    \ifthenelse{\boolean{lettersize}}{
      \bigskip
    }{
      \vfil
    }

    \ifx\note\undefined\else%
    \noindent\textit{\note}

    \smallskip
    \fi
    \sloppy
    \selectlanguage{latin}\Vbar{}~\vlatin

    \selectlanguage{latin}\Rbar{}~\rlatin\if#1T
      \hfill
      \printprayernote{}
    \fi

    \ifx\notetwo\undefined\else%
    \medskip

    \needspace{2\baselineskip}
    \noindent\textit{\notetwo}

    \smallskip
    \selectlanguage{latin}\Vbar{}~\vlatintwo

    \selectlanguage{latin}\Rbar{}~\rlatintwo
    \fi

    \ifx\postvr\undefined
      \smallskip
    \else
      \postvr
    \fi

    \if#1T\else
      \noindent{}\printprayernote{}
    \fi
  }

  \def\gabcfolder{../MarianAntiphons}
  \newcommand{\includelilypond}[1]{
    \ifthenelse{\boolean{includepolyphony}}{
      \noindent
      \ifthenelse{\boolean{lettersize}}{
        \import{../MarianAntiphons/}{#1_letter-systems}%
      }{
        \import{../MarianAntiphons/}{#1-systems}%
      }
    }{}
  }
  \def\betweenLilyPondSystem#1{
    \ifnum#1>1
      \vfil\noindent
      \ifthenelse{\boolean{lettersize}}{
        \linebreak
      }{}
      %\bigskip
    \else
      \linebreak
    \fi
    %\vspace{0.5\baselineskip}
  }

  \section{Salve Regina}
  \label{salveregina_poly}
  \includelilypond{SalveRegina}%

  {
  \newcommand{\vlatin}{Ora pro nóbis sáncta Déi Génitrix.}
  \newcommand{\venglish}{ Pray for us, O holy Mother of God.}
  \newcommand{\rlatin}{Ut dígni efficiámur promissiónibus Chrísti.}
  \newcommand{\renglish}{That we may be made worthy of the promises of Christ.}
  \newcommand{\prayerlatin}{Omnípotens sempitérne Deus, qui gloriósæ Vírginis Matris Maríæ corpus et ánimam, ut dignum Fílii tui habitáculum éffici mererétur, Spíritu Sancto cooperánte præparásti~:~\gredagger{} da, ut cujus commemoratióne lætámur,~* ejus pia intercessióne ab instántibus malis et a morte perpétua liberémur. Per eúmdem Christum Dóminum nostrum. \Rbar~Amen.}
  \newcommand{\prayerenglish}{Almighty, everlasting God, who with the cooperation of the Holy Ghost didst prepare the body and soul of the glorious Virgin Mary, to make it fit to be the worthy dwelling of Thy Son; grant that by the loving intercession of her in whose commemoration we rejoice, we may be delivered from present ills, and from everlasting death.  Through the same Christ our Lord. \Rbar~Amen.}
  \def\prayerlabel{salveprayer}

  \afterant[T]
  }


  \section{Alma Redemptoris Mater}
  \label{alma_poly}
  \includelilypond{AlmaRedemptorisMater}%

  {
    \newcommand{\note}{During Advent:}
    \newcommand{\vlatin}{Angelus Dómini nuntiávit Maríæ.}
    \newcommand{\rlatin}{Et concépit de Spíritu Sancto.}
    
    \newcommand{\notetwo}{From \nth{1} Vespers of Christmas to \nth{2} Vespers of the Purification:}
    \newcommand{\vlatintwo}{Post pártum Vírgo invioláta permansísti.}
    \newcommand{\rlatintwo}{Déi Génitrix intercéde pro nóbis.}
    \def\prayerlabel{almaprayer}

    \afterant{}
  }


  \section{Ave Regina Cælorum}
  \label{averegina_poly}
  \includelilypond{AveReginaCaelorum}%

  {
  \newcommand{\vlatin}{Dignáre me laudáre te Vírgo sacráta.}
  \newcommand{\rlatin}{Da míhi virtútem cóntra hóstes túos.}
  \def\prayerlabel{avereginacaelorumprayer}

  \afterant{}
  }

  \section{Regina Cœli}
  \label{reginacaeli_poly}
  \includelilypond{ReginaCoeli}%

  {
  \newcommand{\vlatin}{Gáude et lætáre Virgo María, allelúia.}
  \newcommand{\venglish}{Rejoice and be glad, O Virgin Mary, alleluia.}
  \newcommand{\rlatin}{Quia surréxit Dóminus vere, allelúia.}
  \newcommand{\renglish}{For the Lord is risen indeed, alleluia.}
  \newcommand{\prayerlatin}{Deus, qui per resurrectiónem Fílii tui Dómini nostri Jesu Christi mundum lætificáre dignátus es~:~\gredagger{} præsta, quǽsumus; ut per ejus Genitrícem Vírginem Maríam~* perpétuæ capiámus gáudia vitæ. Per eúmdem Christum Dóminum nostrum. \Rbar~Amen.}
  \newcommand{\prayerenglish}{O God, who didst vouchsafe to give joy to the world through the resurrection of Thy Son our Lord Jesus Christ; grant, we beseech Thee, that through His Mother, the Virgin Mary, we may obtain the joys of everlasing life. Through the same Christ our Lord. \Rbar~Amen.}
 \def\prayerlabel{reginacaeliprayer}

  \afterant{}
  }

}{}

}