{
\section{Chants at Benediction}
\def\gabcfolder{../BenedictionChants}
\printgabc{8.}{}{O}{OSalutaris}

%\def\translationmargin{68pt}
\translation[]{
\begin{multicols}{2}
\textbf{1.}~O saving Victim of the world,
Who openest wide the gates on high,
The foe his bands on us hath hurled,
O, give us strength; for aid we cry.\\
%\hspace{65ex}
\textbf{2.}~To thee, one Lord, yet Three in One,
Let everlasting glory be~:
O grant us life that end hath none,
In Fatherland to spend with thee. Amen.
\end{multicols}
}
\let\translationmargin=\undefined
\bigskip

\ifthenelse{\boolean{onlysundaycommon}}{
	\vfil
	\pagebreak
}{% false
	\printgabc{7.}{}{O}{OSalutaris_v2}
}


\oldneedspace{4\baselineskip}
\printgabc{3.}{}{T}{TantumErgo}

\ifthenelse{\boolean{onlysundaycommon}}{}{% false
	\needspace{4\baselineskip}
	\bigskip
	{\centering
	2.~\emph{Another Chant.}
	%\vspace{-1ex}
	\par
	}
	\medskip
	\printgabc{1.}{}{T}{TantumErgo_v2}

	\needspace{4\baselineskip}

	\oldneedspace{4\baselineskip}
	\bigskip
	{\centering
	3.~\emph{Modern Chant.}
	\par
	}
	\medskip

	\needspace{4\baselineskip}
	\printgabc{5.}{}{T}{TantumErgo_v3}

	\needspace{4\baselineskip}
	\bigskip
	{\centering
	4.~\emph{Spanish Chant.}
	\par
	}
	\medskip

	\needspace{4\baselineskip}
	\printgabc{5.}{}{T}{TantumErgo-Spanish}
}

\begin{multicols}{2}
\selectlanguage{american}
\noindent
\textbf{1.}~Therefore we, before it bending,
this great sacrament adore;
type and shadows have their ending
in the new rite evermore;
faith, our outward sense amending,
maketh good defects before.\\
\textbf{2.}~Honour, laud, and praise addressing
to the Father and the Son,
might ascribe we, virtue, blessing,
and eternal benison;
Holy Ghost, from both progressing,
equal laud to thee be done. Amen.
\end{multicols}
\medskip

\needspace{4\baselineskip}
\begin{columns}
\versicle{Pánem de cǽlo præstitísti éis. (P.~T.~allelúia.)}{You have given them bread from heaven.}
\response{Omne delectaméntum in se habéntem. (P.~T.~allelúia.)}{Containing all sweetness within it.}
\colchunk{}
\colplacechunks{}
\colchunk{\hspace*{3em}Orémus.}\colchunk{\hspace*{3em}Let us pray,}
\colplacechunks{}
\prayer{Deus, qui nobis sub Sacraménto mirábili passiónis tuæ memóriam reliquísti~:~\dag{} tríbue, quǽsumus, ita nos córporis et sánguinis tui sacra mystéria venerári;~* ut redemptiónis tuæ fructum in nobis júgiter sentiámus.  Qui vivis et regnas in sǽcula sæculórum.  Amen.}
{O God, who hast left us a memorial of Thy passion under a wonderful Sacrament: Grant, we bessech Thee, that we may so venerate the sacred mysteries of Thy body and blood that we may continually sense in ourselves the fruit of Thy redemption. Who livest\dots{}}
\end{columns}

%TODO: we could add the Divine Praises might be nice...

\needspace{4\baselineskip}
{
\bigskip
\printgabc{5.}{}{A}{AdoremusInAeternum}}%

\begin{psalmverses}[1]
\item \emph{Quóniam} confirmáta est super nos misericórdia \textbf{é}jus~:~* et véritas Dómini mánet \textbf{in} æ\textbf{tér}num.
\Rbar{}~\emph{Adorémus}.
\item \emph{Glória} Pátri, et \textbf{Fí}lio,~* et Spi\textbf{rí}tui \textbf{Sán}cto.
\item \emph{Sicut é}\-rat in princípio, et núnc, et \textbf{sém}per,~* et in sǽcula sæcu\textbf{ló}rum. \textbf{A}men.
\Rbar{}~\emph{Adorémus}.
\end{psalmverses}

\translation[]{\emph{Ant.}~Let us adore for ever the Most Holy Sacrament.\\
{\emph Ps.}~All ye nations, praise the Lord~: all ye peoples, sing his glory.\\
Because his merciful kindness is great towards us, and the truth of the Lord endureth for ever. Let us adore\ldots Glory.}
\vfil
}