\chapter{Proper of the Time -- Advent Season}
\section{First Sunday of Advent}
\subtitle{1st Class}
\newcommand{\deusinadjutorium}{\noindent\printnote{\Vbar~\emph{Deus in adjutórium}, page \pageref{deusinadjutorium}.}}
\newcommand{\benedicamusdomino}[1][advent]{
	\noindent\printnote{\Vbar~\emph{Benedicámus Dómino}, page \pageref{benedicamusdomino-#1}.}
	\bigskip
	\hrule
}
\newcommand{\adventhymn}{
	\noindent\printnote{Hymn. \emph{Créator alme síderum}, page \pageref{hymn-creatoralmesiderum}.
	\Vbar~\emph{Roráte}, page \pageref{vr-rorate}.}
}
\newcommand{\collect}[2]{
\needspace{3\baselineskip}
\begin{center}{\large Collect.}\end{center}
\vspace{-0.5\baselineskip plus 0.25\baselineskip}
\begin{parcolumns}[rulebetween]{2}
\sloppy
\prayer{#1}{#2}
\end{parcolumns}
}
\newcommand{\printoant}[2]{
%	#1 number
%	#2 translation
{
\needspace{5\baselineskip}
\subtitle{December #1}
\printgabc{\small At Magn.}{\small \oldstylenums{Ant. 2. D}}{O}{December#1-MagAntiphon}
\translation[]{#2}
}
}

\normalsize
%\def\nogloriapatri{T}
%\def\breakbeforeEuouae{T}
\def\psalmcolsoverride{\begin{parcolumns}[rulebetween,colwidths={1=0.45\linewidth}]{2}}

%1st sunday of advent
{
\deusinadjutorium{}
\def\gabcfolder{../Advent1}
\bigskip
{\def\anttranslation{In that day the mountains shall drop down sweetness, and the hills shall flow with milk and honey, alleluia.}
\def\dontrepeatantiphon{T}
\printpsalm{1}{109}{8G}{Ant1-InIllaDie}{I}
}
\bigskip
{\def\anttranslation{Shout for joy, O daughter of Sion, rejoice greatly, O daughter of Jerusalem, alleluia.}
%\def\dontrepeatantiphon{T}
\printpsalm{2}{110}{8G*}{Ant2-Jucundare}{J}
}
\bigskip
\needspace{6\baselineskip}
{\def\anttranslation{Behold, the Lord shall come, and all His Saints with Him: and there shall be in this day a great light, alleluia.}
%\def\dontrepeatantiphon{T}
\printpsalm{3}{111}{5a}{Ant3-EcceDominusVeniet}{E}
}
%\vfil
\bigskip
{
\def\anttranslation{All ye that thirst come to the waters: seek the Lord while He can be found, alleluia.}
\def\dontrepeatantiphon{T}
\printpsalm{4}{112}{7c}{Ant4-Omnes}{O}
}
\bigskip
%\def\breakbeforeEuouae{T}
{
\def\anttranslation{Behold there shall come the great Prophet, and He shall build Jerusalem anew, alleluia.\needspace{8\baselineskip}}
\printpsalm{5}{113}{4A*}{Ant5-EcceVeniet}{E}
}
%\bigskip
\needspace{3\baselineskip}
\printchapter
{\dropcap{latin}{Fratres~: Hora est jam nos de somno} \textbf{súr}\-ge\-re~:~\gredagger{} nunc enim própior est \emph{no\-stra} \textbf{sá}\-lus,~* quam cum cre\-\textbf{dí}\-dimus.}
{Brethren: it is now the hour for us to rise from sleep.  For now our salvation is nearer than when we believed.}
\bigskip
\label{hymn-creatoralmesiderum}
{
\def\gabcfolder{../Advent}
\printhymn{\oldstylenums{4.}}{C}{hymn-CreatorAlmeSiderum}
{\item Creator of the stars of night
Thy people's everlasting light,
Jesu, Redeemer, save us all,
And hear Thy servants when they call.

\item Thou, lest the demon's ancient curse
Should doom to death a universe,
In love wast made, Thyself alone,
The means to save a world undone.

\item Towards the Cross Thou wentest forth,
That Thou might'st heal the crimes of earth;
Proceeding from a virgin shrine,
The spotless Victim all divine.

\item At whose dread Name, majestic now,
All knees must bend, all hearts must bow;
And things celestial Thee shall own,
And things terrestrial, Lord alone.

\item O Thou, whose coming is with dread,
To judge and doom the quick and dead.
Thy heavenly grace on us bestow,
To shield us from our ghostly foe.

\item To God the Father, God the Son,
And God the Spirit, Three in One,
Laud, honour, might, and glory be
From age to age eternally.
Amen.}

{
\def\vrlinebreak{T}
\label{vr-rorate}
\printvr[\greblockcustos]{vr}
{Ye heavens, drop down dew from above, and let the clouds rain down the Just One.}
{Let the earth open and bud forth the Saviour.}
}
}

\bigskip
{
\def\anttranslation{Fear not, Mary, for thou hast found grace with the Lord: behold thou shalt conceive and bring forth a son, alleluia.}
%\def\preant{\def\noeuouae{T}}
%\def\preanttwo{}
\def\noeuouae{T}
\def\preverses{\greblockcustos}
\printmag{8G}{N}{MagnificatAntiphon}
}

\collect{Excita, quaésumus Dómine, poténtiam tuam, et veni~:~† ut ab imminéntibus peccatórum nostrórum perículis, te mereámur protegénte éripi,~* te liberánte salvári.  Qui vivis et regnas cum Deo Patre in unitáte Spíritus Sancti Deus~:~* per ómnia saécula sæculórum.}
{Stir up Thy power, we beseech Thee, O Lord, and come: that from the threatening dangers of our sins we may deserve to be rescued by Thy protection, and to be saved by Thy deliverance: Who livest and reignest with God the Father in the unity of the Holy Ghost, world without end.}

\bigskip
\benedicamusdomino{}
}













% Advent 2
{
\section{Second Sunday of Advent}
\subtitle{1st Class}
\printnote{If today is December 7, Vespers are of the Sunday with a Commemoration of the First Vespers of the Immaculate Conception.  If today is December 8, the Feast of the Immaculate Conception is celebrated with a Commemoration of this Sunday (see page \pageref{immaculateconception}).}

\deusinadjutorium{}
\def\gabcfolder{../Advent2}

\bigskip
{
\def\anttranslation{Behold, the Lord shall come in the clouds of heaven with great power, alleluia.}
%\def\dontrepeatantiphon{T}
\printpsalm{1}{109}{1g}{Ant1-EcceInNubibusCaeli}{E}
}
\bigskip
%\bigskip
%\bigskip
{\def\anttranslation{Sion, the city of our strength; a Saviour, a wall and a bulwark shall be set therein: open ye the gates, for God is with us, alleluia.}
%\def\dontrepeatantiphon{T}
\printpsalm{2}{110}{7d}{Ant2-Urbs}{U}
}
\bigskip
\needspace{6\baselineskip}
{\def\anttranslation{Behold the Lord shall appear, and shall not lie: if He make delay wait for Him, for He shall come, and shall not tarry, alleluia.}
\def\dontrepeatantiphon{T}
\printpsalm{3}{111}{7a}{Ant3-EcceApparebit}{E}
}
%\vfil
\bigskip
\needspace{3\baselineskip}
{
\def\anttranslation{The mountains and the hills shall sing praise before God, and all the trees of the woods shall clap their hands, for the Lord of all that hath dominion shall come into His everlasting kingdom, alleluia, alleluia.}
\def\dontrepeatantiphon{T}
\printpsalm{4}{112}{1f}{Ant4-Montes}{M}
}
\bigskip
%\def\breakbeforeEuouae{T}
{\def\preant{\def\breakbeforeEuouae{T}}
\def\anttranslation{Behold our Lord shall come with strength, and shall enlighten the eyes of His servants, alleluia.}
\printpsalm{5}{113}{3a}{Ant5-EcceDominusNoster}{E}
}
%\bigskip
\needspace{3\baselineskip}
\printchapter
{\dropcap{latin}{Fratres~: Quæcúmque scripta sunt, ad nostram doctrínam} \textbf{scrí}\-pta sunt~:~\gredagger{} ut per patiéntiam, et consolatiónem \emph{Scri\-ptu}\-\textbf{rá}\-rum,~* spem ha\-be\-\textbf{á}\-mus.}
{Brethren: What things soever were written, were written for our learning: that through patience and the comfort of the Scriptures, we might have hope.}

\bigskip
\adventhymn

\bigskip
{
\def\dontrepeatantiphon{T}
\newcommand{\anttranslation}{Art Thou He that art to come, or look we for another? Relate to John what you have seen: The blind recover their sight, the dead rise again, the poor have the Gospel preached to them, alleluia.}
\def\preant{\def\noeuouae{T}}
%\def\preanttwo{}
\def\preverses{\greblockcustos}
\printmag{8G*}{T}{MagnificatAntiphon}
}

\collect{Excita Dómine corda nostra ad præparándas Unigéniti tui vias~:~† ut per ejus advéntum,~* purificátis tibi méntibus servíre mereámur. Qui tecum vivit et regnat.}
{Stir up our hearts, O Lord, to prepare the ways of Thine only-begotten Son: that through His coming we may deserve to serve Thee with purified minds: Who with Thee liveth and reigneth.}

\bigskip
\noindent
\printnote{If today is December 7, the First Vespers of the Immaculate Conception is commemorated as follows.  Otherwise \Vbar~\emph{Bendicámus Dómino}, page \pageref{benedicamusdomino-advent}.}
\bigskip
\hrule
}






% commemoration of First Vespers of Immaculate Conception
{
\def\gabcfolder{../December8-ImmaculateConception}
\subtitle{Commemoration of First Vespers of the Immaculate Conception}
\sectionmark{Commemoration of First Vespers of the Immaculate Conception}

{
\def\noeuouae{T}
\printgabc{\small At Magn.}{\small \oldstylenums{Ant. 8. G}}{B}{MagnificatAntiphon1}
}
\translation[]{All generations shall call me blessed, because he that is mighty, hath done great things for me, alleluia.}

\bigskip
\printvr[\greblockcustos]{vrImmaculataConceptio-commemoration}
{Today is the Immaculate Conception of the holy Virgin Mary.}
{Who with her virginal foot crushed the head of the serpent.}

\collect{Deus, qui per Immaculátam Vírginis Conceptiónem dignum Fílio tuo habitáculum præparásti~:~\dag{} quaésumus; ut qui ex morte ejúsdem Fílii tui prævísa, eam ab omni labe præservásti,~* nos quoque mundos ejus intercessióne ad te perveníre concédas.  Per eúmdem Dominum.}
{O God, who, by the Immaculate Conception of the Virgin, didst prepare for Thy Son a worthy habitation, we beseech Thee, that as Thou didst preserve her from every stain by the foreseen death of this Thy Son, so Thou wouldst grant that we also being cleansed from guilt by her intercession, may come to Thee.  Through the same Lord.}

\bigskip
\benedicamusdomino{}
}








% Second Vespers of Immaculate Conception
{
\label{immaculateconception}
\def\gabcfolder{../December8-ImmaculateConception}
\section{Immaculate Conception}
\subtitle{1st Class, December 8}

\deusinadjutorium{}

\bigskip
\needspace{6\baselineskip}
{\def\anttranslation{Thou art all fair, O Mary; and the original stain is not in thee.}
\def\dontrepeatantiphon{T}
\printpsalm{1}{109}{1g2}{Ant1-TotaPulchraEsMaria}{T}
}
\bigskip
\needspace{10\baselineskip}
{\def\anttranslation{Thy vesture is white as snow; and thy face is as the sun.}
%\def\dontrepeatantiphon{T}
\printpsalm{2}{112}{8G}{Ant2-VestimentumTuum}{J}
}
\bigskip
\needspace{12\baselineskip}
{\def\anttranslation{Thou art the glory of Jerusalem; thou art the joy of Israel; thou art the honour of our people.}
%\def\dontrepeatantiphon{T}
\printpsalm{3}{121}{8c}{Ant3-TuGloriaJerusalem}{T}
}
%\vfil
\bigskip
{
\def\anttranslation{Blessed art thou, O Virgin Mary, by the Lord, the Most High God, above all women upon the earth.}
\def\dontrepeatantiphon{T}
\def\noeuouae{T}
\printpsalm{4}{126}{7a}{Ant4-BenedictaEsTu}{B}
}
\bigskip
%\def\breakbeforeEuouae{T}
{
\def\anttranslation{Draw us, O immaculate Virgin: we will run after thee in the odour of thine ointments.}
\printpsalm{5}{147}{3a2}{Ant5-TraheNos}{T}
}
%\bigskip
\needspace{3\baselineskip}
\printchapter
{\dropcap{latin}{Dóminus possédit me in inítio viárum suárum, ántequam quidquam fáceret a} prin\-\textbf{cí}\-pi\-o.~\dag{} Ab ætérno ordináta sum, et ex antíquis ántequam \emph{ter\-ra} \textbf{fí}\-e\-ret.~* Nondum erant abýssi, et ego jam concépta \textbf{e}\-ram.}
{The Lord possessed me in the begininning of his ways, before He made anything, from the beginning.  I was set up from eternity, and of old, before the earth was made.  The depths were not as yet, and I was already conceived.}

\bigskip
\label{hymn-avemarisstella}
\printhymn{\oldstylenums{1.}}{A}{hymn-AvemarisStella}
{
\item Hail, thou star of ocean,
Portal of the sky,
Ever-Virgin Mother,
Of the Lord most High.

\item Oh! by Gabriel's Ave
Uttered long ago
Eva's name reversing
Peace confirm below.

\item Break the captive's fetters,
Light on blindness pour
Chase all evils from us,
Every bliss implore.

\item Show thyself a Mother,
Offer Him our sighs,
Who for us incarnate
Did not thee despise.

\item Virgin all excelling,
Passing meek and lowly,
Freed from guilt, preserve us
Blameless chaste and holy.

\item Still as on we journey
Help our weak endeavour
Till we gaze on Jesus
And rejoice for ever.

\item Father, Son, and Spirit,
Three in One confessing.
Give we equal glory,
Equal praise and blessing.
Amen.%\setgrefactor{15}
}

{
\def\vrlinebreak{T}
\printvr[\greblockcustos]{vrImmaculataConceptio}
{Today is the Immaculate Conception of the holy Virgin Mary.}
{Who with her virginal foot crushed the head of the serpent.}
}

\bigskip
{
\newcommand{\anttranslation}{This day a rod came forth from the root of Jesse: this day Mary was conceived without any stain of sin: this day the head of the old serpent was crushed by her.  Alleluia.}
%\def\preant{\def\noeuouae{T}}
%\def\preanttwo{}
\def\breakbeforeEuouae{T}
\def\noeuouae{T}
\def\preverses{\greblockcustos}
\def\dontrepeatantiphon{T}
\printmag{1f}{H}{MagnificatAntiphon2}}
\collect{Deus, qui per Immaculátam Vírginis Conceptiónem dignum Fílio tuo habitáculum præparásti~:~\dag{} quaésumus; ut qui ex morte ejúsdem Fílii tui prævísa, eam ab omni labe præservásti,~* nos quoque mundos ejus intercessióne ad te perveníre concédas.  Per eúmdem Dominum.}
{O God, who, by the Immaculate Conception of the Virgin, didst prepare for Thy Son a worthy habitation, we beseech Thee, that as Thou didst preserve her from every stain by the foreseen death of this Thy Son, so Thou wouldst grant that we also being cleansed from guilt by her intercession, may come to Thee.  Through the same Lord.}

\bigskip
\benedicamusdomino[mary]
}












% 3rd Sunday of Advent
{
\section{Third Sunday of Advent}
\subtitle{1st Class}

\deusinadjutorium{}
\def\gabcfolder{../Advent3}

\bigskip
{
\def\anttranslation{The Lord will come, and will not tarry, and will bring to light the hidden things of darkness, and will manifest Himself to all the nations, alleluia.}
\def\dontrepeatantiphon{T}
\printpsalm{1}{109}{1a}{Ant1-VenietDominus}{V}
}
\bigskip
%\bigskip
%\bigskip
{\def\anttranslation{Rejoice, O Jerusalem, with great joy, for there shall come unto thee a Saviour, alleluia.}
%\def\dontrepeatantiphon{T}
\printpsalm{2}{110}{7b}{Ant2-JerusalemGaude}{J}
}
\bigskip
\needspace{6\baselineskip}
{\def\anttranslation{I will give salvation in Sion, and my glory in Jerusalem, alleluia.}
\def\dontrepeatantiphon{T}
\printpsalm{3}{111}{8G}{Ant3-DaboInSion}{D}
}
%\vfil
\bigskip
\needspace{6\baselineskip}
{
\def\anttranslation{The mountains and all the hills shall be made low: and the crooked shall become straight and the rough ways plain: Come, O Lord, and tarry not, alleluia.}
\def\dontrepeatantiphon{T}
\printpsalm{4}{112}{5a}{Ant4-MontesEtOmnesColles}{M}
}
\bigskip
{%\def\preant{\def\breakbeforeEuouae{T}}
\def\anttranslation{Let us live justly and piously, looking for the blessed hope and the coming of the Lord.}
\printpsalm{5}{113}{2D}{Ant5-JusteEtPieVivamus}{J}
}
%\bigskip
\needspace{3\baselineskip}
\printchapter
{\dropcap{latin}{Fratres~: Gaudéte in Dómino semper~: íterum dico,} gau\-\textbf{dé}\-te.~\gredagger{} Modéstia vestra nota sit óm\-ni\-\emph{bus ho}\-\textbf{mí}\-ni\-bus~:~* Dóminus enim \textbf{pró}\-pe est.}
{Brethren, Rejoice in the Lord always: again, I say, rejoice.  Let your modesty be known to all men: for the Lord is nigh.}

\bigskip
\adventhymn

\bigskip
\printnote{When the third Sunday of Advent falls on December 17, the Antiphon \emph{O Sapiéntia} on page \pageref{osapientia} is sung in place of \emph{Beáta es}.}
{
\def\dontrepeatantiphon{T}
\newcommand{\anttranslation}{Blessed art thou, Mary, that hast believed: those things shall be accomplished in thee, which were spoken to thee by the Lord, alleluia.}
\def\preant{\def\breakbeforeEuouae{T}}
%\def\preanttwo{}
\def\preverses{\greblockcustos}
\label{magant-beataes}
\printmag{8G}{T}{MagnificatAntiphon}
}
\bigskip
{
\def\nomagtitle{T}
\def\magsolemn{T}
\definemag{2}{D}
\def\gabcfolder{../Advent}
\def\noeuouae{T}
	%print o sapientia
%\printoant{17}{O Wisdom, which camest out of the mouth of the Most High, reaching from end to end and ordering all things mightily and sweetly: come and teach us the way of prudence.}
\newcommand{\anttranslation}{O Wisdom, which camest out of the mouth of the Most High, reaching from end to end and ordering all things mightily and sweetly: come and teach us the way of prudence.}
\printmag{2D}{O}{December17-MagAntiphon}
}

\collect{Aurem tuam, quaésumus Dómine, précibus nostris accómmoda~:~† et mentis nostræ ténebras~* grátia tuæ visitatiónis illústra.  Qui vivis et regnas.}
{Incline Thine ear, we beseech Thee, O Lord, to our petitions: and, by the grace of Thy visitation, enlighten the darkness of our minds: Who livest and reignest.}

\bigskip
\benedicamusdomino{}
}











%Advent 4
{
\section{Fourth Sunday of Advent}
\subtitle{1st Class}
\printnote{If today is December 24, First Vespers of Christmas are used on page \pageref{christmas}.}

\deusinadjutorium{}
\def\gabcfolder{../Advent4}

\bigskip
{
\def\anttranslation{Blow ye the trumpet in Sion, for the day of the Lord is near: behold He shall come to save us, alleluia, alleluia.}
%\def\dontrepeatantiphon{T}
\printpsalm{1}{109}{1g}{Ant1-CaniteTuba}{C}
}
\bigskip
%\bigskip
%\bigskip
{\def\anttranslation{Behold the Desired of all nations shall come: and the house of the Lord shall be filled with glory, alleluia.}
%\def\dontrepeatantiphon{T}
\def\noeuouae{T}
\printpsalm{2}{110}{1F}{Ant2-EcceVeniet}{E}
}
\bigskip
\needspace{6\baselineskip}
{\def\anttranslation{The crooked shall become straight, and the rough ways plain: come, O Lord, and tarry not, alleluia.}
\def\dontrepeatantiphon{T}
\printpsalm{3}{111}{1g}{Ant3-EruntPrava}{E}
}
%\vfil
\bigskip
\needspace{6\baselineskip}
{
\def\anttranslation{The Lord shall come, go forth to meet Him, saying: Great is His sovereignty, and of His kingdom there shall be no end: God the mighty, the Lord, the Prince of peace, alleluia, alleluia.}
\def\dontrepeatantiphon{T}
\printpsalm{4}{112}{1f}{Ant4-DominusVeniet}{D}
}
\bigskip
%\def\breakbeforeEuouae{T}
{%\def\preant{\def\breakbeforeEuouae{T}}
\def\anttranslation{Thine almighty Word, O Lord, shall come forth from Thy royal throne, alleluia.}
\printpsalm{5}{113}{2D}{Ant5-Omnipotens}{O}
}
%\bigskip
\needspace{3\baselineskip}
\printchapter
{\dropcap{latin}{Fratres~: Sic nos exístimet homo ut minístros} \textbf{Chrí}\-sti,~\gredagger{} et dispensatóres mys\-te\-ri\-\emph{ó\-rum} \textbf{Dé}\-i.~* Hic jam quaéritur inter dispensatóres, ut fidélis quis in\-ve\-ni\-\textbf{á}\-tur.}
{Brethren, let a man so account of us as of the ministers of Christ and the dispensers of the mysteries of God.  Here now it is required among the dispensers that a man be found faithful.}

\bigskip
\adventhymn

\pagebreak
{
\def\magsolemn{T}
\definemag{2}{D}
\def\gabcfolder{../Advent}
\def\noeuouae{T}
\printoant{18}{O Adonai, and Leader of the house of Israël, who didst appear to Moses in the flame of the burning bush and didst give unto him the law on Sinai: come and with an outstretched arm redeem us.}
\printoant{19}{O Root of Jesse, which standest for an ensign of the people, before whom kings shall keep silence, whom the Gentiles shall beseech: come and deliver us, and tarry not.}
\printoant{20}{O Key of David, and Sceptre of the house of Israël, that openest and no man shutteth, and shuttest and no man openeth: come and bring the prisoner forth from the prison-house, and him that sitteth in darkness and in the shadow of death.}
\printoant{21}{O Day-spring, Brightness of light eternal, and Sun of Justice, come and enlighten them that sit in darkness and in the shadow of death.}
\printoant{22}{O King of the Gentiles and the desire thereof, Thou cornerstone that makest both one, come and deliver mankind, whom Thou didst form out of clay.}
\printoant{23}{O Emmanuel, our King and Lawgiver, the desire of the nations and the Saviour thereof, come to save us, O Lord our God.}

\bigskip
\vfil
{\greblockcustos
\begin{magnificat}{\magtex}
\magverses
\end{magnificat}
\noindent\emph{Repeat antiphon.}}
\vfil
}

\collect{Excita, quaésumus Dómine, poténtiam tuam, et veni, et magna nobis virtúte succúrre~:~† ut per auxílium grátiæ tuæ, quod nostra peccáta præpédiunt,~* indulgéntia tuæ propitiatiónis accéleret.  Qui vivis et regnas cum Deo Patre.}
{O Lord, we beseech Thee, stir up Thy power, and come, and with great might succour us: that by the help of Thy grace that which is hindered by our sins may be hastened by Thy merciful forgiveness: who livest and reignest.}

\bigskip
\benedicamusdomino{}
}