{
\makeatletter  
\newcounter{score}
\newcounter{tabstop}[score]
\newcommand{\grealign}{%
  \@bsphack%
  \ifgre@boxing\else%
    \kern\gre@dimen@begindifference%
    \stepcounter{tabstop}%
    \expandafter\zsavepos{stop-\thescore-\thetabstop}%
    \kern-\gre@dimen@begindifference%
  \fi%
  \@esphack%
}

\newcommand{\setstops}{%
  \gdef\nstabbing@stops{%
    \checkoddpage
    \hspace*{-\ifoddpage\oddsidemargin\else\evensidemargin\fi}\hspace{-1in}%
    \hspace*{\zposx{stop-\thescore-1} sp}\=%
  }%
  \count@=\@ne
  \loop\ifnum\count@<\value{tabstop}%
    \begingroup\edef\x{\endgroup
      \noexpand\g@addto@macro\noexpand\nstabbing@stops{%
        \noexpand\hspace{-\noexpand\zposx{stop-\thescore-\the\count@} sp}%
        \noexpand\hspace{\noexpand\zposx{stop-\thescore-\the\numexpr\count@+1} sp}\noexpand\=%
      }%
    }\x
    \advance\count@\@ne
  \repeat
  \nstabbing@stops\kill
}
\makeatother

\newenvironment{nstabbing}
  {\setlength{\topsep}{0pt}%
   \setlength{\partopsep}{0pt}%
   \tabbing%
   \setstops}
  {\endtabbing\stepcounter{score}}

\pagebreak{}
\section{Prayers for the Forty Hours}

\emph{At the Exposition of the Blessed Sacrament~:}

After Mass, the Celebrant, at the sedilia, having taken off the
chasuble and maniple and put on a cope, puts incense into two
thuribles, giving no blessing.

Kneeling on the lowest step of the altar, he incenses the Blessed
Sacrament. Then he receives the humeral veil.

The Procession follows, while \emph{Pange, lingua} is sung.

After the Procession, the Deacon places the Blessed Sacrament on
the throne, the Celebrant meanwhile putting off the humeral veil.
\emph{Tantum ergo Sacraméntum} is then sung; at \emph{Genitóri} the Blessed
Sacrament is incensed in the usual way.

When \emph{Tantum ergo} is ended, \emph{Panem de cælo} etc. is not said, but
the Cantors at once begin the Litany of the Saints, \emph{p. \pageref{litanyofsaints}}.

\smallskip{}

\emph{On the day of Deposition~:}

After Mass, the Celebrant, at the sedilia, takes off chasuble and
maniple, and puts on a cope. The Ministers lay aside their
maniples; and all return to the altar.

The Litany of the Saints, \emph{p. \pageref{litanyofsaints}}, is sung, and the following prayer as far
as the \Vbar{}~\emph{Dómine exáudi oratiónem meam} inclusive.

The Celebrant stands and puts incense into two thuribles, giving
no blessing. He incenses the Blessed Sacrament, and receives the
humeral veil.

The Procession follows while \emph{Pange, lingua} is sung.

After the Procession the Blessed Sacrament is placed on the altar,
and \emph{Tantum ergo} is sung. At \emph{Genitóri} the Celebrant puts incense
into a thurible, and incenses the Blessed Sacrament.

At the end of \emph{Tantum ergo} there follows \emph{Panem de cælo} etc. The
Celebrant stands, and (omitting \emph{Dóminus vobíscum}) sings all the
prescribed prayers. Afterwards he again kneels down and sings the
\Vbar{}~\emph{Dómine exáudi} etc.  The Cantors sing \emph{Exáudiat nos} etc., and the
Celebrant adds \emph{Fidélium ánimæ} etc. on a lower note.

Finally the Celebrant receives the humeral veil and gives
Benediction in the usual way.

%\def\gabcfolder{../litany}
\oldneedspace{8\baselineskip}

{
\def\gabcfolder{../CorpusChristi}
\printgabc{Hymn.}{3.}{P}{hymn-PangeLingua}
}

%\def\translationmargin{68pt}
\translation[]{
\begin{multicols}{2}
\begin{psalmverses}
{\item Sing, my tongue, the Saviour's glory
Of His Flesh the mystery sing;
Of His Blood all price exceeding,
Shed by our immortal King,
Destined for the world's redemption
From a noble womb to spring.
\item Of a pure and spotless Virgin,
Born for us on earth below,
He, as Man with man conversing,
Stayed the seeds of truth to sow.
Then He closed in solemn order
Wondrously His life of woe.
\item On the night of that last supper,
Seated with His chosen band,
He, the paschal victim eating,
First fulfils the Law's command;
Then as food to all His brethren
Gives Himself with His own Hand.
\item Word made Flesh the bread of nature
By His word to Flesh He turns;
Wine into His Blood He changes:
What though sense no change discerns,
Only be the heart in earnest,
Faith her lesson quickly learns.
\item Down in adoration falling,
Lo, the sacred Host we hail,
Lo, o'er ancient forms departing
Newer rites of grace prevail:
Faith for all defects supplying,
Where the feeble senses fail.
\item To the everlasting Father
And the Son who reigns on high
With the Holy Ghost proceeding
Forth from each eternally,
Be salvation, honour, blessing,
Might and endless majesty.
Amen.}
\end{psalmverses}
\end{multicols}
}

\begin{centering}

Litany of the Saints.\label{litanyofsaints}

\end{centering}

{
\gresetinitiallines{1}
%\printgabc{}{}{K}{../litany/litany-kyrie}
\gregorioscore{../litany/litany-kyrie}
}
%\pagebreak

\gresetinitiallines{0}
\gregorioscore{../litany/Litany-I}%
\begin{nstabbing}
\>Fili Redémptor mundi, \>\>\>\>\>\textbf{De}-\>us, \>mi\>se\>\textit{ré}\>\textit{re} \>no\>bis.\\
\>Spí-\>ri-\>tus \>Sancte, \>\>\textbf{De}-\>us, \>mi\>se\>\textit{ré}\>\textit{re} \>no\>bis.\\
\>Sancta \>\>Trínitas, unus \>\>\>\textbf{De}-\>us, \>mi\>se\>\textit{ré}\>\textit{re} \>no\>bis.\\
\end{nstabbing}

\vspace{-0.7\baselineskip}
\newlength{\mystartlength}
\newlength{\mysubtractlength}
\settowidth{\mystartlength}{\textbf{r}}
\settowidth{\mysubtractlength}{\textbf{G}}
\gregorioscore{../litany/Litany-II}
\begin{nstabbing}
\>Sancta Dei \>\>\>\hspace{\mystartlength}\hspace{-\mysubtractlength}\textbf{Gé}-\>ni-trix, \>\>ó\>\textit{ra} \>\textit{pro} \>no\>bis.\\
\>Sancta Virgo \>\>\>\textbf{vír}gi-num, \>\>\>ó\>\textit{ra} \>\textit{pro} \>no\>bis.\\
\settowidth{\mysubtractlength}{\textbf{M}}
\>Sancte \>\>\>\hspace{\mystartlength}\hspace{-\mysubtractlength}\textbf{Mí}cha-\>\>el, \>ó\>\textit{ra} \>\textit{pro} \>no\>bis.\\
\settowidth{\mysubtractlength}{\textbf{G}}
\>Sancte \>\>\>\hspace{\mystartlength}\hspace{-\mysubtractlength}\textbf{Gá}bri-\>\>el, \>ó\>\textit{ra} \>\textit{pro} \>no\>bis.\\
\settowidth{\mysubtractlength}{\textbf{R}}
\>Sancte \>\>\>\hspace{\mystartlength}\hspace{-\mysubtractlength}\textbf{Rá}pha-\>\>el, \>ó\>\textit{ra} \>\textit{pro} \>no\>bis.\\
\end{nstabbing}

\vspace{-0.7\baselineskip}
\gregorioscore{../litany/Litany-III}
\begin{nstabbing}
\>Omnes \>sancti beatórum Spirítuum \>\>\>\textbf{ór}dines, \>\>\>o\>rá\>\textit{te} \>\textit{pro} \>no\>bis.\\
\>Sancte \>Joánnes \>\>Ba-\textbf{ptí}-\>\>\>\hspace{-1ex}sta, \>\>o-\>\textit{ra} \>\textit{pro} \>no\>bis.\\
\>Sancte \>\>\>\>\hspace{-0.85ex}\textbf{Jo}-seph, \>\>\>\>o-\>\textit{ra} \>\textit{pro} \>no\>bis.\\
\>Omnes \>sancti Patriárchæ et Pro-\>\>\>\hspace{-2.5ex}\textbf{phé}-tæ, \>\>\>o\>rá\>\textit{te} \>\textit{pro} \>no\>bis.\\
\end{nstabbing}

\vspace{-0.7\baselineskip}
\gregorioscore{../litany/Litany-IV}%
\vspace{-\baselineskip}
\def\ora{\hfill o\textit{ra}.\\}%
\def\orate{\hfill orá\textit{te}.\\}%
\begin{multicols}{2}%
\noindent
Sancte \textbf{Pau}le, \hfill o\textit{ra pro} \textbf{nó}bis.\\
Sancte And\textbf{ré}a, \ora{}
Sancte Ja\textbf{có}be, \ora{}
Sancte Jo\textbf{án}nes, \ora{}
Sancte \textbf{Thó}ma, \ora{}
Sancte Ja\textbf{có}be, \ora{}
Sancte Phi\textbf{líp}pe, \ora{}
Sancte Bartholo\textbf{mǽ}e, \ora{}
Sancte Mat\textbf{thǽ}e, \ora{}
Sancte \textbf{Sí}mon, \ora{}
Sancte Thad\textbf{dǽ}e, \ora{}
Sancte Ma\textbf{thí}a, \ora{}
Sancte \textbf{Bár}naba, \ora{}
Sancte \textbf{Lú}ca, \ora{}
Sancte \textbf{Már}ce, \ora{}
Omnes sancti Apóstoli et \\
  \hspace*{1em}Evange\textbf{lí}stæ, \orate{}
Omnes sancti Discípuli \\
  \hspace*{1em}\textbf{Dó}mini, \orate{}
Omnes sancti Inno\textbf{cén}tes, \orate{}
Sancte \textbf{Sté}phane,  \ora{}
Sancte Lau\textbf{rén}ti,  \ora{}
Sancte Vin\textbf{cén}ti,  \ora{}
Sancti Fabiáne et Sebasti\textbf{á}ne, \orate{}
Sancti Joánnes et \textbf{Páu}le, \orate{}
Sancti Cósma et Dami\textbf{á}ne, \orate{}
Sancti Gervási et Pro\textbf{tá}si, \orate{}
Omnes sancti \textbf{Má}rtyres,  \orate{}
Sancte Sil\textbf{vé}ster, \ora{}
Sancte Gre\textbf{gó}ri,  \ora{}
Sancte Am\textbf{bró}si, \ora{}
Sancte Augu\textbf{stí}ne, \ora{}
Sancte Hie\textbf{ró}nyme, \ora{}
Sancte Mar\textbf{tí}ne, \ora{}
Sancte Nico\textbf{lá}e, \ora{}
Omnes sancti Pontífices et \\
  \hspace*{1em}Confes\textbf{só}res, \orate{}
Omnes sancti Do\textbf{ctó}res, \orate{}
Sancte An\textbf{tó}ni, \ora{}
Sancte Bene\textbf{dí}cte, \ora{}
Sancte Ber\textbf{nár}de, \ora{}
Sancte Do\textbf{mí}nice, \ora{}
Sancte Fran\textbf{cí}sce, \ora{}
Omnes sancti Sacerdótes et \\
  \hspace*{1em}Le\textbf{ví}tæ, \orate{}
Omnes sancti Mónachi et \\
  \hspace*{1em}Ere\textbf{mí}tæ, \orate{}
Sancta María Magda\textbf{lé}na, \ora{}
Sancta \textbf{A}gatha, \ora{}
Sancta \textbf{Lú}cia, \ora{}
Sancta \textbf{A}gnes, \ora{}
Sancta Cæ\textbf{cí}lia, \ora{}
Sancta Catha\textbf{rí}na, \ora{}
Sancta Anas\textbf{tá}sia, \ora{}
Omnes sanctæ Vírgines et \\
  \hspace*{1em}\textbf{Ví}duæ, \orate{}
Omnes Sancti et Sanctæ \textbf{De}i, \\
  \hspace*{1em}\hfill intercédi\textit{te pro} \textbf{nó}bis.
\end{multicols}


\gregorioscore{../litany/Litany-V}
\begin{nstabbing}
\>Pro\>pí-\>\textit{ti}-\>\textit{us} \>\textbf{és}-\>to, \>exáu-di nos \>\>\>\>Dó\>mi\>ne.\\
\>\>Ab \textit{ómni} \textbf{má}lo, \>\>\>\>\>lí-\>be-ra nos \>\>\>Dó\>mi\>ne.
\end{nstabbing}
%\def\libera{\hfill \emph{líbera\dots{}}\\}%
\begin{parcolumns}[rulebetween,distance=1em]{2}%
\colchunk{\vspace{-12pt}%

\setlength{\parindent}{0cm} % don't indent new paragraphs
Ab om\textit{ni} \textit{pec}\textbf{cá}to, \hfill \emph{líbera nos\dots{}}\par
Ab \textit{i}\textit{ra} \textbf{tú}a,\par
\hangindent=1em % indent all subsequent lines
A subitánea et impro\textit{ví}\textit{sa} \textbf{mór}te,\par
Ab insídi\textit{is} \textit{dí}\textbf{á}boli,\par
\hangindent=1em % indent all subsequent lines
Ab ira, et ódio, et ómnia mala \textit{vo}\textit{lun}\textbf{tá}te,\par
A spíritu forni\textit{ca}\textit{tí}\textbf{ó}nis,\par
A fúlgure et \textit{tem}\textit{pe}\textbf{stá}te,\par
A flagéllo \textit{ter}\textit{ræ}\textbf{mó}tus,\par
A peste, fa\textit{me}, \textit{et} \textbf{bél}lo,\par
Ab imminénti\textit{bus} \textit{per}\textbf{í}culis,\par
A mor\textit{te} \textit{per}\textbf{pé}tua,\par
\hangindent=1em % indent all subsequent lines
Per mystérium sanctæ Incarnatí\textit{ó}\textit{nis} \textbf{tú}æ,\par
Per Ad\textit{vén}\textit{tum} \textbf{tú}um,\par
Per Nativi\textit{tá}\textit{tem} \textbf{tú}am,\par
\hangindent=1em % indent all subsequent lines
Per Baptísmum et sanctum Je\-jú\-\textit{ni}\-\textit{um} \textbf{tú}um,\par
\hangindent=1em % indent all subsequent lines
Per Crucem et Passí\textit{ónem} \textbf{tú}am,\par
\hangindent=1em % indent all subsequent lines
Per Mortem et Sepul\textit{túram} \textbf{tú}am,\par
\hangindent=1em % indent all subsequent lines
Per sanctam Resurrectí\textit{ónem} \textbf{tú}am,\par
\hangindent=1em % indent all subsequent lines
Per admirábilem Ascensí\textit{ó}\textit{nem} \textbf{tú}am,\par
\hangindent=1em % indent all subsequent lines
Per advéntum Spíritus San\textit{cti} \textit{Pa}\textbf{rá}cliti,\par
In di\textit{e} \textit{ju}\textbf{dí}cii,
}
\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\vspace{-3\baselineskip}
\sloppy

\setlength{\parindent}{0cm} % don't indent new paragraphs
\hspace*{2em}Be merciful, \hfill\emph{spare us, O Lord.}\par
\hspace*{2em}Be merciful, \hfill\emph{graciously hear \dots}\par
\hspace*{2em}From all evil, \hfill\emph{deliver us, O \dots}\par
From all sin, \hfill\emph{deliver us, O Lord.}\par
From Thy wrath,\par
\hangindent=1em % indent all subsequent lines
From sudden and unprovided death,\par
From the snares of the devil,\par
From anger, hatred, and all ill will,\\\par
From the spirit of uncleanness,\par
From lightning and tempest,\par
From the scourge of earthquake,\par
From plague, famine, and war,\par
From threatened dangers,\par
From everlasting death,\par
\hangindent=1em % indent all subsequent lines
Through the mystery of Thy holy Incarnation,\par
Through Thy coming,\par
Through Thy Nativity,\par
\hangindent=1em % indent all subsequent lines
Through Thy Baptism and holy fasting,\par
Through Thy Cross and Passion,\par
Through Thy Death and Burial,\par
Through Thy holy Resurrection,\par
Through Thy wonderful Ascension,\par
\hangindent=1em % indent all subsequent lines
Through the coming of the Holy Ghost, the Paraclete,\par
In the day of judgment,
}
\end{parcolumns}

\gregorioscore{../litany/Litany-VI}
%\def\terogamus{\hfill te rogámus audi nos.\\}%
%\def\terogamus{\hfill te\dots{}\\}%
\begin{parcolumns}[rulebetween,colwidths={1=0.49\linewidth},distance=1em]{2}%
\colchunk{\vspace{-12pt}%

\setlength{\parindent}{0cm} % don't indent new paragraphs
Ut no\textit{bis} \textbf{pár}cas,\par
Ut nobis \textit{in}\textbf{dúl}geas,\par
\hangindent=1em % indent all subsequent lines
Ut ad véram pæniténtiam nos per\-dú\-cere \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut Ecclésiam tuam sanctam~\textbf{'} régere et conserváre \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut Dómnum Apostólicum et omnes ecclesiásticos órdines~\textbf{'} in sancta religióne conserváre \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut inimícos sanctæ Ecclésiæ~\textbf{'} humiliáre \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut régibus et princípibus christiánis~\textbf{'} pacem et veram concórdiam donáre \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut cuncto pópulo christiáno~\textbf{'} pacem et unitátem largíri \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut omnes errántes ad unitátem Ec\-clé\-siæ revocáre,~\textbf{'} et infidéles uni\-vér\-sos ad Evangélii lumen perdúcere \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut nosmetípsos in tuo sancto servítio~\textbf{'} confortáre et conserváre \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut mentes nostras~\textbf{'} ad cæléstia de\-si\-dé\-ri\textit{a} \textbf{é}rigas,\par
\hangindent=1em % indent all subsequent lines
Ut ómnibus benefactóribus nostris~\textbf{'} sempitérna bona \textit{re}\textbf{trí}buas,\par
\hangindent=1em % indent all subsequent lines
Ut ánimas nostras~\textbf{'} fratrum, propinquórum et benefactórum nostrórum~\textbf{'} ab ætérna damnatióne \textit{e}\textbf{rí}pias,\par
\hangindent=1em % indent all subsequent lines
Ut fructus terræ~\textbf{'} dare et conserváre \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut ómnibus fidélibus defúnctis~\textbf{'} ré\-qui\-em ætérnam donáre \textit{di}\textbf{gné}ris,\par
\hangindent=1em % indent all subsequent lines
Ut nos exaudíre \textit{di}\textbf{gné}ris,\\\par
Fi\textit{li} \textbf{Dé}i,
}
\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy

\setlength{\parindent}{0cm} % don't indent new paragraphs
\vspace{-\baselineskip}
We sinners, \hfill\emph{beseech Thee, hear us.}\par
That Thou wouldst spare us,\par
That Thou wouldst pardon us,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst bring us to true penance,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst govern and preserve Thy Holy Church,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst preserve our Pope, and all orders of the Church, in holy religion,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst humble the enemies of holy Church,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst give peace and true concord to Christian kings and princes,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst grant peace and unity to all Christian peoples,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst recall all who have wandered from the unity of the Church, and lead all unbelievers to the light of the Gospel,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst confirm and preserve us in Thy holy service,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst lift up our minds to heavenly desires,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst render eternal blessings to all our benefactors,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst deliver our souls, and the souls of our brethren, relations, and benefactors, from eternal damnation,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst give and preserve from harm the fruits of the earth,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst grant eternal rest to all the faithful departed,\par
\hangindent=1em % indent all subsequent lines
That Thou wouldst graciously hear us,\par
Son of God,
}
\end{parcolumns}

\bigskip
\gregorioscore{../litany/Litany-VII}

\bigskip
\begin{centering}

Psalm 69.

\end{centering}

\smallskip
{
\gresetinitiallines{1}
\gregorioscore{../litany/litany-psalm69}
%\printgabc{}{}{D}{../litany/litany-psalm69}
}

{
\setlength{\columnsep}{18pt}
\setlength{\columnseprule}{.4pt}
\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\begin{psalmverses}[1]
\vspace{-\baselineskip}%
\input{../litany/litany-psalm69-verses}
\end{psalmverses}
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\begin{psalmverses}
\vspace{-\baselineskip}%
\input{../litany/litany-psalm69-verses-en}
\end{psalmverses}
}
\selectlanguage{latin}
\end{parcolumns}

\bigskip\bigskip

\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\begin{vrlist}
\vspace{-\baselineskip}%
\input{../litany/litany-vr}
\end{vrlist}
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\begin{vrlist}
\vspace{-\baselineskip}%
\input{../litany/litany-vr-en}
\end{vrlist}
}
\selectlanguage{latin}
\end{parcolumns}
}

\bigskip

\emph{On the day of Deposition there follow here the incensing of the Blessed Sacrament, the Procession, and \emph{Tantum ergo}.  After the \emph{\Vbar{}~Panem de cælo} etc., the Celebrant (omitting \emph{Dóminus vobíscum}) stands and sings the following prayers.

But on the day of Exposition, immediately after \emph{\Vbar{}~Dómine, exáudi} etc. the Celebrant stands and sings~:}

\medskip

\Vbar{}~Dóminus vo\textbf{bís}cum.  \Rbar{}~Et cum spíritu \textbf{tú}o.

\hspace{2em}Orémus.
\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\lettrine[ante=1.]{D}{eus,} qui nobis sub Sa\-cra\-mén\-to mirábili passiónis tuæ memóriam reliquísti~:~\dag{} tríbue, quǽsumus, ita nos Córporis et Sánguinis tui sacra mystéria venerári;~* ut redemptiónis tuæ fructum in nobis júgiter sentiámus.
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\lettrine{O}{ God,} who under a wonderful Sacrament hast left us a memorial of Thy Passion; grant us, we beseech Thee, so to venerate the sacred mysteries of Thy Body and Blood, that we may ever feel within us the fruit of Thy redemption.
}
\selectlanguage{latin}
\end{parcolumns}

\smallskip
\emph{From Advent until Christmas :}
\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\lettrine[ante=2.]{D}{eus,} qui de beátæ Maríæ Vírginis útero Verbum tu\-um, Angelo nuntiánte, carnem suscípere voluísti~:~\dag{} præsta supplícibus tuis;~* ut, qui vere eam Genitrícem Dei crédimus, ejus apud te intercessiónibus adjuvémur.
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\lettrine{O}{ God,} who wast pleased that, at the message of an Angel, Thy Word should take flesh in the womb of the blessed Virgin Mary, grant to us Thy suppliants, that we, who believe her to be truly the Mother of God, may be helped by her intercession with Thee.
}
\selectlanguage{latin}
\end{parcolumns}

\smallskip
\emph{From Christmas to the Purification :}
\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\lettrine{D}{eus,} qui salútis ætérnæ, be\-á\-tæ Maríæ virginitáte fe\-cún\-da, humáno géneri prǽmia præ\-sti\-tí\-sti~:~\dag{} tríbue, quǽsumus; ut ipsam pro nobis intercédere sentiámus,~* per quam merúimus auctórem vitæ suscípere, Dóminum nostrum Jesum Christum Fílium tuum.
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\lettrine{O}{ God,} who through the fruitful virginity of blessed Mary hast given to mankind the rewards of eternal salvation, grant, we beseech Thee, that we may experience her intercession for us through whom we were made worthy to receive the Author of life, our Lord Jesus Christ Thy Son.
}
\selectlanguage{latin}
\end{parcolumns}

\smallskip
\emph{From the Purification until Advent, except during Paschal Time :}
\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\lettrine{C}{oncede} nos fámulos tuos, quǽ\-su\-mus, Dómine Deus, per\-pé\-tua mentis et córporis sanitáte gaudére~:~\dag{} et gloriósa beátæ Maríæ semper Vírginis intercessióne,~* a præsénti liberári tristítia, et ætérna pérfrui lætítia.
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\lettrine{G}{rant} to us Thy servants, we beseech Thee, O Lord God, that we may enjoy perpetual health of mind and body: and through the intercession of blessed Mary ever Virgin be delivered from present sorrow and possess eternal joy.
}
\selectlanguage{latin}
\end{parcolumns}

\smallskip
\oldneedspace{5\baselineskip}
\emph{In Paschal Time :}
\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\lettrine{D}{eus,} qui per resurrectiónem Fílii tui, Dómini nostri Jesu Christi, mundum lætificáre dignátus es~:~\dag{} præsta, quǽsumus; ut, per ejus Genitrícem Vírginem Maríam~* perpétua capiámus gáudia vitæ.
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\lettrine{O}{ God,} who didst vouchsafe to give joy to the world through the Resurrection of Thy Son our Lord Jesus Christ: grant, we beseech Thee, that, through His Mother, the Virgin Mary, we may obtain the joys of everlasting life.
}
\selectlanguage{latin}
\end{parcolumns}


\medskip
\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\lettrine[ante=3.]{O}{mnipotens,} sempitérne De\-us, miserére fámulo tuo Pontífici nostro \emph{N}.,~\dag{} et dírige eum secúndum tuam cleméntiam in viam salútis ætérnæ~:~* ut, te donánte, tibi plácita cúpiat, et tota virtúte perfíciat.
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\lettrine{A}{lmighty,} everlasting God, have mercy upon Thy servant \emph{N}., our Sovereign Pontiff, and direct him according to Thy clemency into the way of eternal salvation, that by Thy grace he may desire those things pleasing to Thee and perform them with all his strength.
}
\selectlanguage{latin}
\end{parcolumns}

\medskip
\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\lettrine[ante=4.]{D}{eus,} refúgium nostrum, et virtus~:~\dag{} adésto piis Ecclésiæ tuæ précibus, auctor ipse pietátis, et præsta;~*  ut, quod fidéliter pétimus, efficáciter consequámur.
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\lettrine{O}{ God,} our refuge and strength, Author of devotedness, give ear to the devoted prayers of Thy Church, and grant: that we may obtain in deed what we ask with faith.
}
\selectlanguage{latin}
\end{parcolumns}

\medskip
\begin{parcolumns}[rulebetween]{2}
\colchunk{\vspace{-12pt}%
\lettrine[ante=5.]{O}{mnipotens,} sempitérne Deus, qui vivórum domináris simul et mortuórum, omniúmque miseréris, quos tuos fide et ópere futúros esse prænó\-scis~:~\dag{} te súpplices exorámus; ut, pro quibus effúndere preces decrévimus, quosque vel præsens sǽculum adhuc in carne rétinet, vel futúrum jam exútos córpore suscépit,~* intercedéntibus ómnibus Sanctis tuis, pietátis tuæ cleméntia ómnium delictórum suórum véniam consequántur. Per Dóminum nostrum Jesum Christum, Fílium tuum~: Qui tecum vivit et regnat in unitáte Spíritus Sancti Deus, per ómnia sǽcula sæculórum. \Rbar{}~Amen.
}

\selectlanguage{american}
\colchunk{\vspace{-12pt}%
\sloppy
\lettrine{A}{lmighty,} everlasting God, who hast dominion over the living and the dead, and art merciful to all, of whom Thou fore-knowest that they will be Thine by faith and good works: we humbly beseech Thee, that they for whom we intend to pour forth our prayers, whether this present world still detain them in the flesh, or the world to come hath already received them out of their bodies, may, through the intercession of all Thy Saints, by the clemency of Thy goodness, obtain the remission of all their sins.  Through our Lord Jesus Christ Thy Son, Who liveth and reigneth with Thee in the unity of The Holy Spirit, God, world without end. \Rbar{}~Amen.
}
\selectlanguage{latin}
\end{parcolumns}

\medskip
\emph{The Celebrant kneels down and sings~:}

\begin{vrlist}
\vspace{-\baselineskip}%
\item Dómine, exáudi oratiónem meam.
\item Et clamor meus ad te véniat.
\end{vrlist}

\medskip
\emph{The Cantors (where it is the custom) sing~:}

\begin{vrlist}
\vspace{-\baselineskip}%
\item Exáudiat nos omnípotens et miséricors Dóminus.
\item Et custódiat nos semper. Amen.
\end{vrlist}

\medskip
\emph{The Celebrant sings on a lower note~:}

\begin{vrlist}
\vspace{-\baselineskip}%
\item Fidélium ánimæ per misericórdiam Dei requiéscant in pace.
\item Amen.
\end{vrlist}

\medskip
\emph{On the day of Exposition, after a short prayer in silence, the Celebrant and Ministers withdraw.

On the day of Deposition, Benediction follows.}
}
\pagebreak
