%all five antiphons
%first four psalms
%hymn

%5th psalm is proper
%versicle is proper
%mag is proper

\newcommand{\predeusinadjutorium}{%
%\smallskip
\large
\setgrefactor{15}
}
\def\deusinadjutoriumsolemn{T}
\def\includelaustibi{F}

\newcommand{\preantone}{\setgrefactor{17}
\large
%\greblockcustos
\medskip
}


\newcommand{\antoneinitialsize}{40}
\newcommand{\antonetex}{an--vidi_turbam_magnam--solesmes}
\newcommand{\antoneinitial}{V}
\newcommand{\antonetranslation}{I saw a great multitude, which no man could number, of all nations, standing before the throne.}
\definepsalm{1}{109}{1}{f}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\setgrefactor{17}
%\greblockcustos
\large
}
\newcommand{\anttwoinitialsize}{40}
\newcommand{\anttwotex}{an--et_omnes_angeli--solesmes}
\newcommand{\anttwoinitial}{E}
\newcommand{\anttwotranslation}{And all the Angels stood round about the throne, and fell before the throne on their faces, and worshipped God.}
\definepsalm{2}{110}{1}{f}
\newcommand{\prepsalmtwo}{%
\normalsize
\greblockcustos
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\setgrefactor{17}
\large
%\greblockcustos
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{an--redemisti_nos--solesmes}
\newcommand{\antthreeinitial}{R}
\newcommand{\antthreetranslation}{Thou, O Lord God, hast redeemed us by thy Blood, out of every tribe, and tongue, and people, and nation, and hast made us a kingdom unto our God.}
\definepsalm{3}{111}{8}{G}
\newcommand{\prepsalmthree}{%
%\greblockcustos
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\setgrefactor{17}
%\greblockcustos
\large
%\normalsize
}
\newcommand{\antfourinitialsize}{40}
\newcommand{\antfourtex}{an--benedicite_dominum_all_saints--solesmes}
\newcommand{\antfourinitial}{B}
\newcommand{\antfourtranslation}{Bless the Lord, all ye His chosen: keep holiday, and extol Him.}
\definepsalm{4}{112}{8}{G}
\newcommand{\prepsalmfour}{%
\gdef\psalmclef{2}
%\vspace{-1ex}
%\setgrefactor{15}
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\def\nopagebreakbeforepsalmfive{T}
%\def\pagebreakafterpsalmfive{T}
\newcommand{\preantfive}{\setgrefactor{17}
%\greblockcustos
\large
}
%\newcommand{\preantfivetwo}{\preantfive}
%\newcommand{\antfivefontsizetwo}{40}

\newcommand{\antfiveinitialsize}{40}
\newcommand{\antfivetex}{an--hymnus_omnibus_sanctis--solesmes}
\newcommand{\antfiveinitial}{H}
\newcommand{\antfivetranslation}{The praise of all His Saints, even of the children of Israel, a people near unto Him; this honour have all His Saints.}
%\definepsalm{5}{115}{8}{G}
\newcommand{\prepsalmfive}{%
%\vspace{-1ex}
%\setgrefactor{15}%
%\normalsize%
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\def\pagebreakbeforehymn{T}

\newcommand{\prehymn}{\normalsize
\setgrefactor{15}
}

\newcommand{\chapter}{\dropcap{latin}{Ecce ego Joánnes vidi álterum Angelum ascendéntem ab ortu solis, habéntem signum Dei} \textbf{ví}\-vi~:~\dag{} et clamávit voce magna quátuor Angelis quibus datum est nocére terræ et mari, dicens~: Nolíte nocére terræ et mari, ne\-\emph{que ar}\-\textbf{bó}\-ri\-bus,~* quoadúsque signémus servos Dei nostri in fróntibus e\-\textbf{ó}rum.}
\newcommand{\chaptertranslation}{And I saw another angel ascending from the rising of the sun, having the sign of the living God; and he cried with a loud voice to the four angels, to whom it was given to hurt the earth and the sea, saying: Hurt not the earth, nor the sea, nor the trees, till we sign the servants of our God in their foreheads.}

\newcommand{\collect}{Omnípotens sempitérne Deus, qui nos ómnium Sanctórum tuórum mérita sub una tribuísti celebritáte venerári~:~\dag{} quæsumus; ut desiderátam nobis tuæ proptiatiónis abundántiam,~* multipicátis intercessóribus, largiáris. Per Dóminum nostrum.}
\newcommand{\collecttranslation}{Almighty, eternal God, Who granted us to honor the merits of all Thy Saints in a single solemn festival, bestow on us, we beseech Thee, through their manifold intercession, that abundance of Thy mercy for which we yearn. Through our Lord.}

\newcommand{\hymnlinetwo}{8.}
\newcommand{\hymntex}{hy--placare_christe_servulis--solesmes}
\newcommand{\hymninitial}{P}
\newcommand{\hymntranslation}{
\item O Christ, thy guilty people spare!
Lo, kneeling at thy gracious throne,
Thy Virgin-Mother pours her prayer,
Imploring pardon for her own.

\item Ye angels, happy evermore!
Who in your circles nine ascend,
As ye have guarded us before,
So still from harm our steps defend.

\item Ye prophets and Apostles high!
Behold our penitential tears;
And plead for us when death is nigh,
Our all-searching judge appears.

\item Ye martyrs all! a purple band,
And confessors, a white-robed train;
Oh, call us to our native land,
From this our exile, back again.

\item And ye, O choirs of virgins chaste!
Receive us to your seats on high;
With hermits whom the desert waste
Sent up of old into the sky.

\item Drive from the flock, O Spirit blest!
The false and faithless race away;
That all within one fold may rest,
Secure beneath one shepherd's sway.

\item To God the Father glory be,
And to his sole-begotten Son;
And glory, Holy Ghost, to thee,
While everlasting ages run.
Amen.%\setgrefactor{15}
}
