\newcommand{\antonetex}{Ant1-CaniteTuba}
\newcommand{\antoneinitial}{C}
\newcommand{\antonetranslation}{Blow ye the trumpet in Sion, for the day of the Lord is near: behold He shall come to save us, alleluia, alleluia.}
\definepsalm{1}{109}{1}{g}

\newcommand{\anttwotex}{Ant2-EcceVeniet}
\newcommand{\anttwoinitial}{E}
\newcommand{\anttwotranslation}{Behold the Desired of all nations shall come: and the house of the Lord shall be filled with glory, alleluia.}
\definepsalm{2}{110}{1}{f}

\newcommand{\antthreetex}{Ant3-EruntPrava}
\newcommand{\antthreeinitial}{E}
\newcommand{\antthreetranslation}{The crooked shall become straight, and the rough ways plain: come, O Lord, and tarry not, alleluia.}
\definepsalm{3}{111}{1}{g}

\newcommand{\antfourtex}{Ant4-DominusVeniet}
\newcommand{\antfourinitial}{D}
\newcommand{\antfourtranslation}{The Lord shall come, go forth to meet Him, saying: Great is His sovereignty, and of His kingdom there shall be no end: God the mighty, the Lord, the Prince of peace, alleluia, alleluia.}
\definepsalm{4}{112}{1}{f}

\newcommand{\antfivetex}{Ant5-Omnipotens}
\newcommand{\antfiveinitial}{O}
\newcommand{\antfivetranslation}{Thine almighty Word, O Lord, shall come forth from Thy royal throne, alleluia.}
\definepsalm{5}{113}{2}{D}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Sic nos exístimet homo ut minístros} \textbf{Chrí}\-sti,~\gredagger{} et dispensatóres mys\-te\-ri\-\emph{ó\-rum} \textbf{Dé}\-i.~* Hic jam quaéritur inter dispensatóres, ut fidélis quis in\-ve\-ni\-\textbf{á}\-tur.}
\newcommand{\chaptertranslation}{Brethren, let a man so account of us as of the ministers of Christ and the dispensers of the mysteries of God.  Here now it is required among the dispensers that a man be found faithful.}

\newcommand{\collect}{Excita, quaésumus Dómine, poténtiam tuam, et veni, et magna nobis virtúte succúrre~:~† ut per auxílium grátiæ tuæ, quod nostra peccáta præpédiunt,~* indulgéntia tuæ propitiatiónis accéleret.  Qui vivis et regnas cum Deo Patre.}
\newcommand{\collecttranslation}{O Lord, we beseech Thee, stir up Thy power, and come, and with great might succour us: that by the help of Thy grace that which is hindered by our sins may be hastened by Thy merciful forgiveness: who livest and reignest.}
