% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}
\sloppy

%commemoration
%\def\pagebreakbeforecommemoration{T}
%\def\commemorationtex{../TimeAfterPentecost/CommemorationPentecost4}
%end commemoration stuff


\newcommand{\heading}{Most Precious Blood of Christ.}

\newcommand{\predeusinadjutorium}{%
%\smallskip
\large
\setgrefactor{15}
}
\def\deusinadjutoriumsolemn{T}

\newcommand{\preantone}{\setgrefactor{17}
\large
%\greblockcustos
}


\newcommand{\antoneinitialsize}{40}
\newcommand{\antonetex}{Ant1-QuisEstIste}
\newcommand{\antoneinitial}{Q}
\newcommand{\antonetranslation}{Who is this that cometh from Edom, with dyed garments from Bosra?  This beautiful one in his robe?}
\definepsalm{1}{109}{7}{a}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\setgrefactor{17}
%\greblockcustos
\large
}
\newcommand{\anttwoinitialsize}{40}
\newcommand{\anttwotex}{Ant2-Ego}
\newcommand{\anttwoinitial}{E}
\newcommand{\anttwotranslation}{I that speak justice, and am a defender to save.}
\definepsalm{2}{110}{8}{c}
\newcommand{\prepsalmtwo}{%
\normalsize
\greblockcustos
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\setgrefactor{17}
\large
\greblockcustos
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{Ant3-VestitusErat}
\newcommand{\antthreeinitial}{V}
\newcommand{\antthreetranslation}{He was clothed in a robe sprinkled with blood, and His name is called the Word of God.}
\definepsalm{3}{111}{4}{A}
\newcommand{\prepsalmthree}{%
%\greblockcustos
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\setgrefactor{17}
%\greblockcustos
\large
%\normalsize
}
\newcommand{\antfourinitialsize}{40}
\newcommand{\antfourtex}{Ant4-QuareErgo}
\newcommand{\antfourinitial}{Q}
\newcommand{\antfourtranslation}{\vspace{0ex minus 3.5ex}Why then is Thine apparel red, and Thy garments like them that tread in the winepress?\vspace{0ex minus 3.5ex}}
\def\psalmclef{2}
\definepsalm{4}{112}{8}{c}
\let\psalmclef=\undefined
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\setgrefactor{15}
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\def\nopagebreakbeforepsalmfive{T}
%\def\pagebreakafterpsalmfive{T}
\newcommand{\preantfive}{\setgrefactor{17}
%\greblockcustos
\large
}
%\newcommand{\preantfivetwo}{\preantfive}
%\newcommand{\antfivefontsizetwo}{40}

\newcommand{\antfiveinitialsize}{40}
\newcommand{\antfivetex}{Ant5-Torcular}
\newcommand{\antfiveinitial}{T}
\newcommand{\antfivetranslation}{\vspace{0pt minus 1ex}I have trodden the winepress alone, and of the Gentiles there is not a man with Me.}
\definepsalm{5}{147}{2}{D}
\newcommand{\prepsalmfive}{%
%\vspace{-1ex}
%\setgrefactor{15}%
%\normalsize%
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Christus assístens póntifex futurórum bonórum, per ámplius et perféctius tabernáculum non manufáctum, id est non hujus} cre\-a\-ti\-\textbf{ó}nis~:~\dag{} neque per sánguinem hircórum aut vitulórum, sed per próprium sánguinem introívit se\-\emph{mel in} \textbf{Sá}ncta,~* ætérna redemptióne in\textbf{vén}ta.}
\newcommand{\chaptertranslation}{Brethren: Christ being come an High Priest of the good things to come, by a greater and more perfect tabernacle, not made with hands, that is, not of this creation: neither by the blood of goats or of calves, but by His own Blood, entered once into the Holies, having obtained eternal redemption.}

\def\pagebreakbeforehymn{T}

\newcommand{\prehymn}{\large
\setgrefactor{17}
}
\newcommand{\hymnlinetwo}{8.}
\def\hymninitialsize{40}
\newcommand{\hymntex}{Hymn-FestivisResonent}
\newcommand{\hymninitial}{F}
\newcommand{\hymntranslation}{
\item In solemn chant and song, as is most meet and right,
Ye citizens of Sion, young and old, unite,
And forth with measur'd step and gleaming tapers' ray
In glad procession wend your way.

\item All mindful of that Blood which Christ, our dying Lord,
Upon the cruel tree from many a wound outpour'd
We bow our knees in worship at the mem'ry dear,
And hold not back the fitting tear.

\item By the first Adam's guilty deed; avenging death
Had pass'd to all on earth who draw this fleeting breath:
The second Adam's innocence then cleans'd us from all stain,
And with His Life all live again.

\item For when the mighty plea of Christ, God's dying Son,
At the great Father's throne on high acceptance won,
His precious Blood, prevail'd to pay the debt of sin,
And pardon from the Judge to win.

\item Who so shall wash his robes, all dark with guilty stain,
In that dear cleansing Blood, shall find them white again;
And deck'd with roseate glory he at length shall stand,
With angels, at the King's right hand.

\item Then from the narrow way let not th'inconstant soul
Turn back, but ever onward press to its desir'd goal,
And God, whose grace doth aid to run the race below,
Shall soon the glorious prize bestow.

\item Almighty Father, now in mercy bend Thine ear,
Through Him whose precious Blood hath bought our ransom dear;
By Thy sweet Spirit's working, grant Thy love and grace,
That we in heav'n may see Thy face.
Amen.%\setgrefactor{15}
}

\newcommand{\vrtex}{vrTeErgo}
\newcommand{\vtranslation}{We therefore pray Thee help Thy servants.}
\newcommand{\rtranslation}{Whom Thou hast redeemed with Thy precious Blood.}

\newcommand{\premag}{
\large
\setgrefactor{17}
%\greblockcustos
}
%\newcommand{\premagtwo}{
%\setgrefactor{16}
%}
\newcommand{\magfontsize}{38}
\def\pagebreakbeforemagnificat{T}
\newcommand{\maganttex}{MagnificatAntiphon}
\newcommand{\magantinitial}{H}
\newcommand{\maganttranslation}{\vspace{-16pt plus 16pt}Ye shall observe this day for a memorial: and ye shall keep it holy unto the Lord, in your generations with an everlasting worship.\vspace{-4pt plus 4pt}}
\def\magsolemn{T}
\def\magoneline{T}
\definemag{1}{D2}
\newcommand{\premagverses}{%
%\greblockcustos
\normalsize
\setgrefactor{14}
%\pagebreak
}

\newcommand{\collect}{Omnípotens sempitérne Deus, qui unigénitum Fílium tuum mundi Redemptórem constituísti, ac ejus sánguine placári voluísti~:~\dag{} concéde, quaésumus, sálutis nostræ prétium solémni cultu ita venerári, atque a præséntis vitæ malis ejus virtúte deféndi in terris;~* ut fructu perpétuo lætémur in cælis. Per eúmdem Dóminum nostrum.}
\newcommand{\collecttranslation}{Almighty everlasting God, who didst appoint Thine only-begotten Son to be Redeemer of the world, and didst vouchsafe to be appeased by His Blood: grant, we beseech Thee, that, by our solemn service, we may so venerate the Price of our redemption, and by its power be so defended from the evils of this present life on earth, that we may enjoy its fruit for evermore in heaven. Through the same our Lord.}

\def\benedicamusdominogrefactor{14}
\definebenedicamusdomino{1}{2}

%\def\includefideliumanimae{T}

\input{../FullVespers}
