% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}
\sloppy

%commemoration for 4th Sunday after Pentecost
\def\pagebreakbeforecommemoration{T}
\def\commemorationtex{../TimeAfterPentecost/CommemorationPentecost4}
%end commemoration stuff


\newcommand{\heading}{Birth of John the Baptist.}

\newcommand{\predeusinadjutorium}{%
%\smallskip
\large
\setgrefactor{15}
}
\def\deusinadjutoriumsolemn{T}

\newcommand{\preantone}{\setgrefactor{17}
\large
%\greblockcustos
}


\newcommand{\antoneinitialsize}{40}
\newcommand{\antonetex}{Ant1-ElisabethZachariae}
\newcommand{\antoneinitial}{E}
\newcommand{\antonetranslation}{Elizabeth, the wife of Zacharias, gave birth to a man of might, the forerunner of the Lord.\vspace{0ex plus 0ex minus 3ex}}
\definepsalm{1}{109}{3}{a}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\setgrefactor{17}
%\greblockcustos
\large
}
\newcommand{\anttwoinitialsize}{40}
\newcommand{\anttwotex}{Ant2-Innuebant}
\newcommand{\anttwoinitial}{I}
\newcommand{\anttwotranslation}{They made signs unto his father, by what name he should be called: and he wrote, saying: His name is John.}
\definepsalm{2}{110}{4}{E}
\newcommand{\prepsalmtwo}{%
\normalsize
\greblockcustos
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\setgrefactor{17}
\large
\greblockcustos
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{Ant3-JoannesVocabitur}
\newcommand{\antthreeinitial}{J}
\newcommand{\antthreetranslation}{His name shall be called John, and many shall rejoice in his birth.}
\definepsalm{3}{111}{1}{f}
\newcommand{\prepsalmthree}{%
%\greblockcustos
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\setgrefactor{17}
%\greblockcustos
\large
%\normalsize
}
\newcommand{\antfourinitialsize}{40}
\newcommand{\antfourtex}{Ant4-InterNatos}
\newcommand{\antfourinitial}{I}
\newcommand{\antfourtranslation}{\vspace{0ex minus 3.5ex}Among those born of women, there hath not risen a greater than John the Baptist.\vspace{0ex minus 3.5ex}}
\definepsalm{4}{112}{3}{b}
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\setgrefactor{15}
\normalsize
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\def\nopagebreakbeforepsalmfive{T}
%\def\pagebreakafterpsalmfive{T}
\newcommand{\preantfive}{\setgrefactor{17}
%\greblockcustos
\large
}
%\newcommand{\preantfivetwo}{\preantfive}
%\newcommand{\antfivefontsizetwo}{40}

\newcommand{\antfiveinitialsize}{40}
\newcommand{\antfivetex}{Ant5-TuPuer}
\newcommand{\antfiveinitial}{T}
\newcommand{\antfivetranslation}{\vspace{0pt minus 1ex}Thou, child, shalt be called the Prophet of the Most High: thou shalt go before the Lord to prepare His ways.}
\definepsalm{5}{116}{3}{b}
\newcommand{\prepsalmfive}{%
%\vspace{-1ex}
%\setgrefactor{15}%
%\normalsize%
}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\chapter}{\dropcap{latin}{Audíte ínsulæ, et atténdite pópuli de} \textbf{lon}ge~:~\dag{} Dóminus ab úte\-\emph{ro vo}\-\textbf{cá}\-vit me,~* de ventre matris meæ recordátus est nóminis \textbf{me}i.}
\newcommand{\chaptertranslation}{Give ear, ye islands, and hearken, ye people from afar.  The Lord hath called me from the womb, from the bowels of my mother He hath been mindful of my name.}

\def\pagebreakbeforehymn{T}

\newcommand{\prehymn}{\large
\setgrefactor{16}
}
\newcommand{\hymnlinetwo}{2.}
\newcommand{\hymntex}{Hymn-UtQueantLaxis}
\newcommand{\hymninitial}{U}
\newcommand{\hymntranslation}{
\item O let thy power, holy John, now loosen
Tongues which are fetter'd, cleanse our lips polluted,
That we thy servants all thy wondrous actions
May sound forth meetly.

\item Lo! a swift herald from the heav'ns descending
Brings to thy father tiding of thy greatness,
Thy name revealing, and thy life's high story
Duly declaring.

\item Doubting in spirit of the heav'nly message,
Straightway his tongue the pow'r of speech forsaketh,
But on the birthday thou his voice restorest
At thine appearing.

\item Thou, while yet hidden, in the womb still cradled,
Knewest thy Monarch, in his bridal chamber:
Whence the two mothers, through their children's merits,
Mysteries utter'd.

\item Glory to God the Father in the highest
And to the Sole-begotten Son be given,
Praise, too, to Thee, O great co-equal Spirit,
One God, for ever.
Amen.%\setgrefactor{15}
}

\newcommand{\vrtex}{vrIstePuerMagnus}
\newcommand{\vtranslation}{This child is great before the Lord.}
\newcommand{\rtranslation}{For in truth His hand is with him.}

\newcommand{\premag}{
\normalsize
\setgrefactor{17}
%\greblockcustos
}
%\newcommand{\premagtwo}{
%\setgrefactor{16}
%}
\newcommand{\magfontsize}{38}
\def\pagebreakbeforemagnificat{T}
\newcommand{\maganttex}{MagnificatAntiphon}
\newcommand{\magantinitial}{P}
\newcommand{\maganttranslation}{\vspace{-16pt plus 16pt}The child that is born to us is more than a prophet; for this is he of whom the Saviour said: Among those born of women there hath not risen a greater than John the Baptist.\vspace{-4pt plus 4pt}}
\def\magsolemn{T}
\def\magoneline{T}
\definemag{7}{d}
\newcommand{\premagverses}{%
%\greblockcustos
\normalsize
\setgrefactor{14}
%\pagebreak
}

\newcommand{\collect}{Deus, qui præséntem diem honorábilem nobis in beáti Joánnis Nativitáte fecísti~:~\dag{} da pópulis tuis spirituálium grátiam gaudiórum;~* et ómnium fidélium mentes dírige in viam salútis ætérnæ. Per Dóminum nostrum.}
\newcommand{\collecttranslation}{O God, who hast made this day worthy of honour by the birth of blessed John: grant to Thy people the grace of spiritual joys, and direct the minds of all the faithful into the way of eternal salvation. Through our Lord.}

\def\benedicamusdominogrefactor{14}
\definebenedicamusdomino{1}{2}

%\def\includefideliumanimae{T}

\input{../FullVespers}
