\newcommand{\antonetex}{an--isti_sunt_sancti--solesmes}
\newcommand{\antoneinitial}{I}
\newcommand{\antonetranslation}{These are the Saints who for God's covenant gave up their bodies, and washed their robes in the Blood of the Lamb.}
\definepsalm{1}{109}{2}{D}

\newcommand{\anttwotex}{an--sancti_per_fidem--solesmes}
\newcommand{\anttwoinitial}{S}
\newcommand{\anttwotranslation}{By faith the Saints overcame kingdoms; they performed what was right, they obtained the promises.}
\definepsalm{2}{110}{2}{D}

\newcommand{\antthreetex}{an--sanctorum_velut_aquilae--solesmes}
\newcommand{\antthreeinitial}{S}
\newcommand{\antthreetranslation}{The youth of the Saints shall be renewed like the eagle's; they shall flower like the lily in the City of God.}
\definepsalm{3}{111}{8}{G}

\newcommand{\antfourtex}{an--absterget_deus--solesmes}
\newcommand{\antfourinitial}{A}
\newcommand{\antfourtranslation}{God shall wipe away every tear from the eyes of the Saints; and no longer shall be any sorrow, or crying, nor any pain; for the former things have passed away.}
\definepsalm{4}{112}{7}{a}

\newcommand{\antfivetex}{an--in_caelestibus_regnis--solesmes}
\newcommand{\antfiveinitial}{I}
\newcommand{\antfivetranslation}{The dwelling of the Saints is in the heavenly kingdoms, and their rest for ever.}
\def\psalmclef{2}
\definepsalm{5}{115}{8}{G}
\let\psalmclef=\undefined

\ifx\vrtex\undefined
	\newcommand{\vrtex}{vrInPatientiaVestra}
	\newcommand{\vtranslation}{In your patience.}
	\newcommand{\rtranslation}{You shall possess your souls.}
\fi

\newcommand{\maganttex}{an--isti_sunt_duae_olivae--solesmes}
\newcommand{\magantinitial}{I}
\newcommand{\maganttranslation}{These are two olive trees and two candlesticks shining before the Lord; they have power to shut heaven with clouds and to open its doors; for their tongues are become keys of heaven.}
\def\magsolemn{F}
\definemag{1}{D}
