\newcommand{\chaptertext}{\dropcap{latin}{Justórum ánimæ in manu Dei sunt, et non tanget illos torméntum} \textbf{mor}\-tis.~\dag{} Visi sunt óculis insipién\-\emph{ti\-um} \textbf{mo}\-ri~:~* illi autem sunt in \textbf{pa}ce.}
\newcommand{\chaptertranslation}{The souls of the just are in the hand of God~: and the torment of death shall not touch them.  In the sight of the unwise they seemed to die~: but they are in peace.}

\newcommand{\hymnlinetwo}{2.}
\newcommand{\hymntex}{hy--sanctorum_meritis--solesmes}
\newcommand{\hymninitial}{S}
\newcommand{\hymntranslation}{
\item By help of Saints, come let our tongues relate
their famous joys and their courageous deeds;
our mind desires in songs to celebrate
their conquest, which all gain exceeds.

\item While here they lived, the world these men abhorred,
for they this withered soil did much despise
whose flowers are barren, and with thee, their Lord,
up to thy heavenly joys did rise.

\item They for thy sake with stout contempt have borne
the causeless rage of men, and torment fierce,
and cruel hooks, which have their bodies torn,
but had not power their soul to pierce.

\item They like mild sheep to slaughter are assigned,
at which they never murmur nor complain,
but with a silent heart and guiltless mind
their constant patience they maintain.

\item What voice, what tongue, those gifts can fitly show
which thou prepar'st for martyrs? Who, once stained
with streams of blood, which from their wounds did flow,
have now bright crown of laurel gained.

\item We thee beseech, one highest Deity,
to wash our sins, to drive our harms away,
to give thy servants peace, that we
to thee may everlasting praise repay.
Amen.\grechangestaffsize{15}}

%\newcommand{\vrtex}{vrAnnuntiaveruntOperaDei}
%\newcommand{\vtranslation}{They declared the works of God.}
%\newcommand{\rtranslation}{And understood His doings.}

%\newcommand{\maganttex}{MagnificatAntiphon}
%\newcommand{\magantinitial}{E}
%\newcommand{\maganttranslation}{Be ye valiant in warfare, and fight with the old serpent: and ye shall receive an everlasting kingdom.}
%\def\magsolemn{T}
%\definemag{1}{g2}
