\newcommand{\antonetex}{Ant1-AssumptaEst}
\newcommand{\antoneinitial}{A}
\newcommand{\antonetranslation}{Mary is taken up into heaven, the Angels rejoice, and bless God with songs of praise.}
\definepsalm{1}{109}{7}{a}

\newcommand{\anttwotex}{Ant2-MariaVirgo}
\newcommand{\anttwoinitial}{M}
\newcommand{\anttwotranslation}{The Virgin Mary is taken up into the bridal chamber of heaven, where the King of kings sitteth on His starry throne.}
\definepsalm{2}{112}{8}{G}

\newcommand{\antthreetex}{Ant3-InOdorem}
\newcommand{\antthreeinitial}{I}
\newcommand{\antthreetranslation}{We run after the odour of Thine ointments.  The young maidens have loved thee exceedingly.}
\definepsalm{3}{121}{4}{A*}

\newcommand{\antfourtex}{Ant4-BenedictaFilia}
\newcommand{\antfourinitial}{B}
\newcommand{\antfourtranslation}{O Daughter, blessed art thou of the Lord, for through thee we have partaken of the fruit of life.}
\definepsalm{4}{126}{7}{c2}

\newcommand{\antfivetex}{Ant5-PulchraEs}
\newcommand{\antfiveinitial}{P}
\newcommand{\antfivetranslation}{Fair and beautiful art thou, O daughter of Jersualem, terrible as an army in battle array.}
\definepsalm{5}{147}{1}{g2}

\newcommand{\chaptertext}{\dropcap{latin}{Benedíxit te Dóminus in virtúte sua, quia per te ad níhilum redégit inimícos} \textbf{nó}\-stros.~\dag{} Benedícta es tu, fília, a Dómino De\-\emph{o ex}\-\textbf{cél}\-so,~* præ ómnibus muliéribus super \textbf{tér}\-ram.}
\newcommand{\chaptertranslation}{The Lord hath blessed thee by His power, because by thee He hath brought our enemies to nought.  Blessed art thou, O daughter, by the Lord the most high God, above all women upon the earth.}

\newcommand{\vrtex}{vrExaltata}
\newcommand{\vtranslation}{The holy Mother of God hath been exalted.}
\newcommand{\rtranslation}{Above the choirs of Angels, into the kingdom of heaven.}

\newcommand{\collect}{Omnípotens sempitérne Deus, qui Immaculátam Vírginem Maríam, Fílii tui Genitrícem, córpore et ánima ad cæléstem glóriam assumpsísti~:~† concéde, quǽsumus; ut ad supérna semper inténti,~* ipsíus glóriæ mereámur esse consórtes.  Per eúmdem Dóminum.}
\newcommand{\collecttranslation}{Almighty everlasting God, who hast taken body and soul into heaven the Immaculate Virgin Mary, Mother of Thy Son: grant, we beseech thee, that by steadfastly keeping heaven as our goal we may be counted worthy to join her in glory.  Through.}
