\newcommand{\antonetex}{an--missus_est_gabriel--solesmes}
\newcommand{\antoneinitial}{M}
\newcommand{\antonetranslation}{The Angel Gabriel was sent to the Virgin Mary espoused to Joseph.}
\definepsalm{1}{109}{8}{G*}

\newcommand{\anttwotex}{an--ave_maria_alleluia--solesmes}
\newcommand{\anttwoinitial}{A}
\newcommand{\anttwotranslation}{Hail, Mary, full of grace, the Lord is with thee; blessed art thou amongst women.}
\definepsalm{2}{112}{1}{g}

\newcommand{\antthreetex}{an--ne_timeas_alleluia--solesmes}
\newcommand{\antthreeinitial}{N}
\newcommand{\antthreetranslation}{Fear not, Mary, thou hast found grace with the Lord; behold, thou shalt conceive, and bring forth a Son.}
\definepsalm{3}{121}{8}{G}

\newcommand{\antfourtex}{an--dabit_ei_dominus--solesmes}
\newcommand{\antfourinitial}{D}
\newcommand{\antfourtranslation}{The Lord shall give unto Him the throne of His father David, and He shall reign forever.}
\definepsalm{4}{126}{1}{f}

\newcommand{\antfivetex}{an--ecce_ancilla_domini--solesmes}
\newcommand{\antfiveinitial}{E}
\newcommand{\antfivetranslation}{Behold the handmaid of the Lord: be it done unto me according to thy word.}
\definepsalm{5}{147}{8}{c}

\newcommand{\chaptertext}{\dropcap{latin}{Ecce virgo concípiet et páriet} \textbf{fí}\-li\-um,~\dag{} et vocábitur nomen e\-\emph{jus Em}\-\textbf{má}\-nu\-el.~* Butýrum et mel cómedet, ut sciat reprobáre malum, et elígere \textbf{bo}num.}
\newcommand{\chaptertranslation}{Behold a virgin shall conceive, and bear a son, and His name shall be called Emmanuel. He shall eat butter and honey, that He may know to refuse the evil, and to choose the good.}

\newcommand{\hymnlinetwo}{1.}
\newcommand{\hymntex}{Hymn-AveMarisStella}
\newcommand{\hymninitial}{A}
\newcommand{\hymntranslation}{
\item Hail, thou star of ocean,
Portal of the sky,
Ever-Virgin Mother,
Of the Lord most High.

\item Oh! by Gabriel's Ave
Uttered long ago
Eva's name reversing
Peace confirm below.

\item Break the captive's fetters,
Light on blindness pour
Chase all evils from us,
Every bliss implore.

\item Show thyself a Mother,
Offer Him our sighs,
Who for us incarnate
Did not thee despise.

\item Virgin all excelling,
Passing meek and lowly,
Freed from guilt, preserve us
Blameless chaste and holy.

\item Still as on we journey
Help our weak endeavour
Till we gaze on Jesus
And rejoice for ever.

\item Father, Son, and Spirit,
Three in One confessing.
Give we equal glory,
Equal praise and blessing.
Amen.%\grechangestaffsize{15}
}

\newcommand{\collect}{Deus, qui de beátæ Maríæ Vírginis útero Verbum tuum, Angelo nuntiánte, carnem suscípere voluísti~:~\dag{} præsta supplícibus tuis; ut qui vere eam Genitrícem Dei crédimus,~* ejus apud te intercessiónibus adjuvémur.  Per eúmdem Dóminum nostrum.}
\newcommand{\collecttranslation}{O God, who didst will that Thy Word should take flesh, at the message of an Angel, in the womb of the Blessed Virgin Mary, grant to Thy suppliant people, that we who believe her to be truly the Mother of God, may be helped by her intercession with Thee.  Through the same our Lord.}

\newcommand{\vrtex}{vrAveMaria}
\newcommand{\vtranslation}{Hail Mary, full of grace.}
\newcommand{\rtranslation}{The Lord is with thee.}
