\newcommand{\antonetex}{Ant1-PostTriduum}
\newcommand{\antoneinitial}{P}
\newcommand{\antonetranslation}{After three days, they found Jesus in the temple, sitting in the midst of the doctors, hearing them and asking them questions.}
\definepsalm{1}{109}{8}{G}

\newcommand{\anttwotex}{Ant2-DixitMaterJesuAdIllum}
\newcommand{\anttwoinitial}{D}
\newcommand{\anttwotranslation}{The Mother of Jesus said to Him: Son, why hast Thou done so to us? Behold Thy father and I have sought Thee sorrowing.}
\definepsalm{2}{112}{4}{E}

\newcommand{\antthreetex}{Ant3-Descendit}
\newcommand{\antthreeinitial}{D}
\newcommand{\antthreetranslation}{Jesus went down with them and came to Nazareth, and was subject to them.}
\definepsalm{3}{121}{8}{G}

\newcommand{\antfourtex}{Ant4-EtJesus}
\newcommand{\antfourinitial}{E}
\newcommand{\antfourtranslation}{And Jesus advanced in wisdom, and age, and grace with God and men.}
\definepsalm{4}{126}{2}{D}

\newcommand{\antfivetex}{Ant5-EtDicebant}
\newcommand{\antfiveinitial}{E}
\newcommand{\antfivetranslation}{And they said: How came this Man by this wisdom and miracles? Is not this the carpenter's son?}
\definepsalm{5}{147}{8}{G}

\newcommand{\chaptertext}{\dropcap{latin}{Descéndit Jesus cum María et Joseph, et} {\emph{ve\-nit} \textbf{Ná}\-za\-reth,~* et erat súbditus \textbf{íl}lis.}}
\newcommand{\chaptertranslation}{Jesus went down with Mary and Joseph, and came to Nazareth, and was subject to them.}

\newcommand{\hymnlinetwo}{2.}
\newcommand{\hymntex}{Hymn-OLuxBeataCaelitum.tex}
\newcommand{\hymninitial}{O}
\newcommand{\hymntranslation}{
\item Thou blessed Light of saints above
And highest Hope of mortals here,
O Jesu, on whose childhood's days
The love of home shone bright and clear:
\item O Mary, who art full of grace,
Whose virgin bosom undefiled,
Gave Jesus nourishment; whose arms
With love embraced the Holy Child:
\item And thou, whom God did choose from all
To guard the spotless Mother-Maid.
On whom God's Son as father called,
A father's love with love repaid:
\item Of Jesse's noble lineage born
To bring earth's nations healing grace,
O hear us as we lowly bow,
And see you in this holy place.
\item The setting sun brings evening near
And dusk veils all things earthly now,
We here abide to pour our prayer,
Our inmost heart's desires we show.
\item In Naz'reth's home all virtues grew
And grace produced its fairest flowers,
O may such grace and virtue sweet
Shine forth in ev'ry home of ours.
\item Obedient to Thy parents made,
All glory Jesu, be to Thee,
With God the Father infinite,
And Holy Ghost, eternally.
Amen.}

\newcommand{\vrtex}{vrPonamUniversos}
\newcommand{\vtranslation}{I will cause all thy children to be taught of the Lord.}
\newcommand{\rtranslation}{And great shall be the peace of thy children.}

\newcommand{\maganttex}{MagnificatAntiphon}
\newcommand{\magantinitial}{M}
\newcommand{\maganttranslation}{Mary kept all these words, and pondered them in her heart.}
\def\magsolemn{T}
\definemag{8}{G}

\newcommand{\collect}{Dómine Jesu Christe, qui Maríæ et Joseph súbditus, domésticam vitam ineffabílibus virtútibus consecrásti~:~\dag{} fac nos, utriúsque auxílio, Famíliæ sanctæ tuæ exémplis ínstrui;~* et consórtium cónsequi sempitérnum~: Qui vivis et regnas cum Deo Patre.}
\newcommand{\collecttranslation}{O Lord Jesus Christ, who, being subject to Mary and Joseph, didst sanctify home life with ineffable virtues: grant that with the aid of both, we may be taught by the example of Thy Holy Family, and attain to eternal fellowship with them: Who livest and reignest with God the Father.}
