\newcommand{\antonetex}{Ant1-VenietDominus}
\newcommand{\antoneinitial}{V}
\newcommand{\antonetranslation}{The Lord will come, and will not tarry, and will bring to light the hidden things of darkness, and will manifest Himself to all the nations, alleluia.}
\definepsalm{1}{109}{1}{a}

\newcommand{\anttwotex}{Ant2-JerusalemGaude}
\newcommand{\anttwoinitial}{J}
\newcommand{\anttwotranslation}{Rejoice, O Jerusalem, with great joy, for there shall come unto thee a Saviour, alleluia.}
\definepsalm{2}{110}{7}{b}

\newcommand{\antthreetex}{Ant3-DaboInSion}
\newcommand{\antthreeinitial}{D}
\newcommand{\antthreetranslation}{I will give salvation in Sion, and my glory in Jerusalem, alleluia.}
\definepsalm{3}{111}{8}{G}

\newcommand{\antfourtex}{Ant4-MontesEtOmnesColles}
\newcommand{\antfourinitial}{M}
\newcommand{\antfourtranslation}{The mountains and all the hills shall be made low: and the crooked shall become straight and the rough ways plain: Come, O Lord, and tarry not, alleluia.}
\definepsalm{4}{112}{5}{a}

\newcommand{\antfivetex}{Ant5-JusteEtPieVivamus}
\newcommand{\antfiveinitial}{J}
\newcommand{\antfivetranslation}{Let us live justly and piously, looking for the blessed hope and the coming of the Lord.\medskip}
\definepsalm{5}{113}{2}{D}

\newcommand{\chaptertext}{\dropcap{latin}{Fratres~: Gaudéte in Dómino semper~: íterum dico,} gau\-\textbf{dé}\-te.~\gredagger{} Modéstia vestra nota sit óm\-ni\-\emph{bus ho}\-\textbf{mí}\-ni\-bus~:~* Dóminus enim \textbf{pró}\-pe est.}
\newcommand{\chaptertranslation}{Brethren, Rejoice in the Lord always: again, I say, rejoice.  Let your modesty be known to all men: for the Lord is nigh.}

\newcommand{\magantinitial}{B}
\newcommand{\maganttex}{MagnificatAntiphon}
\newcommand{\maganttranslation}{Blessed art thou, Mary, that hast believed: those things shall be accomplished in thee, which were spoken to thee by the Lord, alleluia.}
\def\magsolemn{F}
\definemag{8}{G}

\newcommand{\collect}{Aurem tuam, quaésumus Dómine, précibus nostris accómmoda~:~† et mentis nostræ ténebras~* grátia tuæ visitatiónis illústra.  Qui vivis et regnas.}
\newcommand{\collecttranslation}{Incline Thine ear, we beseech Thee, O Lord, to our petitions: and, by the grace of Thy visitation, enlighten the darkness of our minds: Who livest and reignest.}
