% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\newcommand{\comheadingtext}{Commemoration of Immaculate Conception I Vespers}

\newcommand{\latincomcollect}{Deus, qui per Immaculátam Vírginis Conceptiónem dignum Fílio tuo habitáculum præparásti~:~\dag{} quaésumus; ut qui ex morte ejúsdem Fílii tui prævísa, eam ab omni labe præservásti,~* nos quoque mundos ejus intercessióne ad te perveníre concédas.  Per eúmdem Dominum.}
\newcommand{\englishcomcollect}{O God, who, by the Immaculate Conception of the Virgin, didst prepare for Thy Son a worthy habitation, we beseech Thee, that as Thou didst preserve her from every stain by the foreseen death of this Thy Son, so Thou wouldst grant that we also being cleansed from guilt by her intercession, may come to Thee.  Through the same Lord.}


\newcommand{\englishcommagantiphon}{All generations shall call me blessed, because he that is mighty, hath done great things for me, alleluia.}

\newcommand{\commagantlinetwo}{Ant. 8. G}
\newcommand{\commaganttex}{MagnificatAntiphon1-noEuouae}
\newcommand{\commagantinitial}{B}
\newcommand{\commagantinitialsize}{35}

\newcommand{\commvrtex}{vrImmaculataConceptio-commemoration}
\newcommand{\commvlatin}{Immaculáta Concéptio est hódie sanctæ Maríæ \textbf{Vír}ginis.}
\newcommand{\commrlatin}{Quæ serpéntis caput virgíneo pede con\textbf{trí}vit.}
\newcommand{\commvtranslation}{Today is the Immaculate Conception of the holy Virgin Mary.}
\newcommand{\commrtranslation}{Who with her virginal foot crushed the head of the serpent.}
