\newcommand{\antonetex}{ant1-Domine}
\newcommand{\antoneinitial}{D}
\newcommand{\antonetranslation}{Lord, thou didst deliver to me five talents. Behold I have gained other five over and above.}
\definepsalm{1}{109}{1}{g2}

\newcommand{\anttwotex}{ant2-Euge-serve-bone}
\newcommand{\anttwoinitial}{E}
\newcommand{\anttwotranslation}{Well done, good servant, because thou hast been faithful in a little, enter into the joy of thy Lord.}
\definepsalm{2}{110}{1}{f}

\newcommand{\antthreetex}{ant3-fidelis-servus-et-prudens}
\newcommand{\antthreeinitial}{F}
\newcommand{\antthreetranslation}{That is a faithful and wise servant, whom his Lord hath appointed over his family.}
%\def\psalmclef{2}
\definepsalm{3}{111}{3}{a}
%\let\psalmclef=\undefined

\newcommand{\antfourtex}{ant4-beatus-ille-servus}
\newcommand{\antfourinitial}{B}
\newcommand{\antfourtranslation}{Blessed are those servants whom the lord, when he cometh and knocketh, shall find watching.}
\definepsalm{4}{112}{7}{a}

\newcommand{\antfivetex}{ant5-serve-bone-et-fidelis}
\newcommand{\antfiveinitial}{S}
\newcommand{\antfivetranslation}{Good and faithful servant, enter thou into the joy of thy Lord.}
\definepsalm{5}{116}{7}{c2}


\newcommand{\chaptertext}{\dropcap{latin}{Beátus vir, qui invéntus est sine} \textbf{má}\-cu\-la,~\dag{} et qui post aurum non ábiit, nec sperávit in pecúnia \emph{et the}\-\textbf{sáu}\-ris.~* Quis est hic, et laudábimus eum? fecit enim mirabília in vita \textbf{su}a.}
\newcommand{\chaptertranslation}{Blessed is the man that is found without blemish, and that hath not gone after gold, nor put his trust in money nor in treasures. Who is he, and we will praise him? for he hath done wonderful things in his life.}

\newcommand{\hymnlinetwo}{2.}
\newcommand{\hymntex}{Hymn-IsteConfessorDominiColentes}
\newcommand{\hymninitial}{I}
\newcommand{\hymninitialsize}{33}
\newcommand{\hymntranslation}{
\item The faithful servant who confessed his Lord,
whose feast the Church's annual joys record,
this day in recompense is called to be
before thy Father, Lord, confessed by thee.
\item His humble prudence and his thoughts on high,
his pure and unpretending piety, by
blameless steps a sober life conveyed
till last it centred where it first was made.
\item Within his tomb lies all that heaven can spare;
hither the deaf, the blind, and lame repair;
his kind protection each disease restrains,
restores their losses, and relieves their pains.
\item Justly may then his praise bespeak our voice,
to join in consort, and with heaven rejoice.
So may we hope to have an equal share,
of his protection here, and merit there.
\item To God, in nature one, in persons three,
eternal glory, power and jubilee,
whose sovereign and universal throne
disposes all things with his word alone.
Amen.}
