% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\heading}{Vesper hymn for Advent.}
\def\hymninitialsize{37}
\def\hymnlinetwo{\oldstylenums{4.}}
\def\hymntex{hymn-CreatorAlmeSiderum}
\def\hymninitial{C}
\def\hymntranslation{\item Creator of the stars of night
Thy people's everlasting light,
Jesu, Redeemer, save us all,
And hear Thy servants when they call.

\item Thou, lest the demon's ancient curse
Should doom to death a universe,
In love wast made, Thyself alone,
The means to save a world undone.

\item Towards the Cross Thou wentest forth,
That Thou might'st heal the crimes of earth;
Proceeding from a virgin shrine,
The spotless Victim all divine.

\item At whose dread Name, majestic now,
All knees must bend, all hearts must bow;
And things celestial Thee shall own,
And things terrestrial, Lord alone.

\item O Thou, whose coming is with dread,
To judge and doom the quick and dead.
Thy heavenly grace on us bestow,
To shield us from our ghostly foe.

\item To God the Father, God the Son,
And God the Spirit, Three in One,
Laud, honour, might, and glory be
From age to age eternally.
Amen.\setgrefactor{15}}
\def\prehymn{\large\setgrefactor{16}\vspace*{-20pt plus 20pt}}

\def\vrtex{vr}
\def\vrnospace{F}
\def\vtranslation{Ye heavens, drop down dew from above, and let the clouds rain down the Just One.}
\def\rtranslation{Let the earth open and bud forth the Saviour.}

%\definebenedicamusdomino{lent}{2}
\input{../hymn-template}