\newcommand{\printpsalmwithtranslation}[3]{
	% #1 psalm number
	% #2 ending
	% #3 0 to start on 1st verse, 1 for second
	\setlength{\columnsep}{18pt}
	\setlength{\columnseprule}{.4pt}
	\beginpsalmcols
	\colchunk{\vspace{-12pt}%
	\begin{psalmverses}[#3]
	\vspace{-\baselineskip}%
	\input{psalms/Psalm#1-#2-verses}
	\end{psalmverses}
	}

	\selectlanguage{american}
	\colchunk{\vspace{-12pt}%
	\sloppy
	\begin{psalmverses}
	\vspace{-\baselineskip}%
	\input{psalms/Psalm#1-verses-en}
	\end{psalmverses}
	}
	\selectlanguage{latin}
	\endpsalmcols
}

\renewcommand{\printpsalm}[3]{
  % #1 psalm number
  % #2 ending
  % #3 0 to start on 1st verse, 1 for second
  \setlength{\columnsep}{18pt}
  \setlength{\columnseprule}{.4pt}
  \setlength\multicolsep{0pt}%
  \begin{multicols*}{2}
  \begin{psalmverses}[#3]
  \input{psalms/Psalm#1-#2-verses}
  \end{psalmverses}
  \end{multicols*}
}



\newcommand{\printpsalmtranslation}[3]{
  % #1 psalm number
  % #2 ending
  % #3 0 to start on 1st verse, 1 for second
  \setlength{\columnsep}{18pt}
  \setlength{\columnseprule}{.4pt}
  \setlength\multicolsep{0pt}%
  \begin{multicols*}{2}
  \begin{psalmverses}[#3]
  \input{psalms/Psalm#1-verses-en}
  \end{psalmverses}
  \end{multicols*}
}

\def\beginchaptercols{\begin{parcolumns}[rulebetween]{2}}
\newcommand{\printchapternew}[4]{
	% #1 ref
	% #2 latin first words
	% #3 latin remaining
	% #4 english text
	{\noindent\hspace{3em}Chapter.\hfill\emph{#1}\hspace{3em}}
    \beginchaptercols{}
    \colchunk{\sloppy\dropcap{latin}{#2} #3\hfill{}\Rbar{}~Deo~grátias.}
    \colchunk{\sloppy \dropcap{american}{#4}}
    \end{parcolumns}
}
\newcommand{\printvrwithtranslation}{
    {\normalsize
    \ifx\beginvrcols\undefined\def\beginvrcols{\begin{parcolumns}[rulebetween]{2}}\fi
    \beginvrcols
    \colchunk{
      \par\vspace{-\baselineskip}\noindent\selectlanguage{latin}%
      \Vbar{}~\vlatin{}
    }
    \colchunk{%
      \par\vspace{-\baselineskip}\noindent\selectlanguage{american}%
      \Vbar{}~\vtranslation{}
    }%
    \colplacechunks%
    \ifx\rlatin\undefined\else
    \colchunk{
      \par\vspace{-\baselineskip}\noindent\selectlanguage{latin}%
      \Rbar{}~\rlatin{}%
    }
    \colchunk{%
      \par\vspace{-\baselineskip}\noindent\selectlanguage{american}%
      \Rbar{}~\rtranslation{}%
    }%
    \colplacechunks%
    \fi
    \end{parcolumns}
    }
}
{
  \label{sunday}
  \chapter{Sunday at Terce}
  \phantomsection
  \sectionmark{Sunday at Terce throughout the year}
  \addcontentsline{toc}{section}{Sunday at Terce throughout the year}

  {\centering Oratio ante officium.\par}
  {\centering \emph{Aperi. Pater. Ave.}\par}
  \begin{columns}
  \colchunk{\selectlanguage{latin}Aperi, Domine, os meum ad benedicendum nomen
sanctum tuum: munda quoque cor meum ab omnibus
vanis, perversis et alienis cogitationibus; intellectum
illumina, affectum inflamma, ut digne, attente ac
devote hoc Officium recitare valeam, et exaudiri
merear ante conspectum divinae Majestatis tuae. Per
Christum Dóminum nostrum. \Rbar{}~Amen.}
  \colchunk{\selectlanguage{american}Open, O Lord, my mouth to bless Thy holy name;
cleanse my heart from all vain, evil, and
wandering thoughts; enlighten my understanding
and kindle my affections; that I may worthily,
attentively, and devoutly say this Office, and so
deserve to be heard before the presence of Thy
divine Majesty. Through Christ our Lord. \Rbar{}~Amen.}
  \colplacechunks{}
  \colchunk{\selectlanguage{latin}Domine, in unione illius divinae intentionis, qua ipse
in terries laudes Deo persolvisti, hanc tibi
Horam persolvo.}
  \colchunk{\selectlanguage{american}O Lord, in union with that divine intention, with
which Thou didst praise God upon earth, I render
this Hour to Thee.}
  \colplacechunks{}
  \end{columns}
  \medskip

  %\oldneedspace{6\baselineskip}
  \emph{The Ferial Tone is used except before Pontifical Mass.}

  \printgabc{\Vbar}{}{D}{deus-in-adjutorium}\label{deusinadjutorium}
  \medskip

  %\oldneedspace{6\baselineskip}
  \emph{The Festal Tone is used only before Pontifical Mass.}

  {\def\gabcfolder{..}
    \printgabc{\Vbar}{}{D}{DeusInAdjutorium_laustibi}\label{deusinadjutorium-festal}
  }

  \medskip\vfill
  {\centering Hymn.\par}%
  %\vspace{-0.5\baselineskip}
  \def\dotting{\leaders\hbox to 1em{\hfil.\hfil}\hfill}
  %\def\dotting{\hfill}
  \setlength\parsep{0pt}%
  \setlength\topsep{0pt}%
  \setlength\partopsep{0pt}%
  \setlength\multicolsep{0pt}%
  \begin{multicols}{2}%
  \noindent{}\emph{In Advent},\dotting p.~\pageref{hymn-advent}\\
  \emph{Christmas},\dotting p.~\pageref{hymn-christmas}\\
  \emph{Epiphany},\dotting p.~\pageref{hymn-epiphany}\\
  \emph{Holy Family},\dotting p.~\pageref{hymn-holyfamily}\\
  \emph{In Lent},\dotting p.~\pageref{hymn-lent}\\
  \emph{In Passiontide},\dotting p.~\pageref{hymn-passiontide}\\
  \emph{In Paschaltide},\dotting p.~\pageref{hymn-paschaltide}\\
  \emph{Ascension},\dotting p.~\pageref{hymn-ascension}\\
  \emph{Pentecost},\dotting p.~\pageref{hymn-pentecost}\\
  \emph{Christ the King},\dotting p.~\pageref{hymn-oct-last-sunday}%\\
  %\emph{Corpus Christi},\dotting p.~\pageref{hymn-corpus-christi}\\
  %\emph{Sacred Heart},\dotting p.~\pageref{hymn-sacred-heart}
  \end{multicols}%

  \bigskip
  %\oldneedspace{4\baselineskip}
  {\centering 1.~On Ordinary Sundays.\par}\label{hymn-sunday}

  \printgabc{Hymn.}{2.}{N}{hy--nunc_sancte_nobis_(in_dominicis_per_annum)--solesmes_1961}
  \bigskip

  \oldneedspace{4\baselineskip}
  {\centering 2.~On Solemn Feasts.\par}\label{hymn-feast}

  \printgabc{Hymn.}{8.}{N}{hy--nunc_sancte_nobis_(in_festis)--solesmes_1961}
  \bigskip

  \oldneedspace{4\baselineskip}\vfill
  {\centering 3.~On Feasts of the Blessed Virgin Mary.\par}\label{hymn-bvm}

  \printgabc{Hymn.}{2.}{N}{hy--nunc_sancte_nobis_(in_festis_bmv)--solesmes_1961}

  \begin{multicols}{2}
  \begin{psalmverses}
\item Come Holy Ghost, who ever One
Art with the Father and the Son,
It is the hour, our souls possess
With thy full flood of holiness.

\item Let flesh and heart and lips and mind
Sound forth our witness to mankind;
And love light up our mortal frame,
Till others catch the living flame.

\item Almighty Father, hear our cry,
Through Jesus Christ, our Lord most High,
Who, with the Holy Ghost and thee,
Doth live and reign eternally.
Amen.
  \end{psalmverses}
  \end{multicols}

\bigskip

% print antiphon
%    \printgabc[\preant]{\antlineone}{\antlinetwo}{\antinitial}{\anttex}
  \printgabc{Ant.}{2. D}{A}{an--alleluia._(sund._at_terce)--solesmes}
% print translation
  \translation[]{Alleluia, Lead me into the path of thy commandments, alleluia, alleluia.}

  { \def\printrepeatantiphon{\emph{Repeat antiphon, \emph{p.~\pageref{ant2-sunday}.}}}
    \printtercepsalms{2D}%
  }

  \printtercepsalmstranslation{}

% \printpsalm{118.3}{2D}{1}
% \printpsalmtitle{118. IV.}
% \printpsalm{118.4}{2D}{0}
% \printpsalmtitle{118. V.}
% \printpsalm{118.5}{2D}{0}

% print antiphon
%    \printgabc[\preant]{\antlineone}{\antlinetwo}{\antinitial}{\anttex}
  \bigskip\oldneedspace{8\baselineskip}\label{ant2-sunday}
  \printgabc{Ant.}{2. D}{A}{an--alleluia._(sund._at_terce)--solesmes}
% print translation
  %\translation[]{Alleluia, Lead me into the path of thy commandments, alleluia, alleluia.}

\medskip\oldneedspace{6\baselineskip}
\printchapternew{1. John 4.}{Deus cáritas}{est~:~\dag{} et qui manet in caritáte, in Deo manet,~* et Deus in eo.}{God is charity: and he that abideth in charity, abideth in God, and God in him.}

\medskip\label{shortresp-sunday}
\printgabc{Short}{Resp.}{I}{re--inclina_cor_meum--solesmes}

\translation[]{\Vbar{}~Incline my heart into thy testimonies.
\Rbar{}~Incline\dots{}
\Vbar{}~Turn away my eyes that they may not behold vanity: quicken me in thy way.
\Rbar{}~Into thy testimonies.
\Vbar{}~Glory be\dots{}
\Vbar{}~Incline\dots{}}

\bigskip\label{vr-sunday}
\gresetinitiallines{0}
\gregorioscore{vr-ego-dixi}
\newlength{\myhwidth}
\settowidth{\myhwidth}{tib}
\begin{nstabbing}
\>\Rbar{}~Sana ánimam meam, quia peccávi \>\hspace{-\myhwidth}tibi.
\end{nstabbing}

\translation[]{\Vbar{}~I said: O Lord, be thou merciful to me.\\
\Rbar{}~Heal my soul, for I have sinned against thee.}

\bigskip
%\def\beginvrcols{\begin{parcolumns}[rulebetween,colwidths={1=0.48\linewidth}]{2}}
\def\vlatin{Dóminus vobíscum.}
\def\rlatin{Et cum spíritu tuo.}
\def\vtranslation{The Lord be with you.}
\def\rtranslation{And with thy spirit.}
{\centering Collect.\par}
\printvrwithtranslation{}

\bigskip
    %\def\dotting{\leaders\hbox to 1em{\hfil.\hfil}\hfill}
    \def\dotting{\hfill}
    \begin{multicols}{2}%
    %\printnote{Advent,\dotting \emph{p.~\pageref{advent1-collect} to \pageref{advent4-collect}}}

    %\printnote{Christmas,\dotting \emph{p.~\pageref{christmas-eve-collect} to \pageref{holyfamily-collect}}}

    \noindent\emph{Time after Epiphany},\dotting p.~\pageref{epiphany2-collect} to \pageref{epiphany6-collect}\\
    \emph{Septuagesima},\dotting p.~\pageref{septuagesima-collect} to \pageref{quinquagesima-collect}\\
    %\emph{Easter to Pentecost},\dotting p.~\pageref{easter1-collect} to \pageref{pentecost-collect}\\
    \emph{Time after Pentecost},\dotting p.~\pageref{pentecost2-collect} to \pageref{pentecost24-collect}
    \end{multicols}

\bigskip
\printvrwithtranslation{}
\bigskip

\printnote{Except before Pontifical Mass, the Officiant chants the \emph{\Vbar{}~Benedicámus Dómino} to the following tone.}
\medskip
\gresetinitiallines{0}\label{benedicamus-domino-sunday}
\gregorioscore{vr-benedicamus-domino}
\bigskip

%\def\beginvrcols{\begin{parcolumns}[rulebetween,colwidths={1=0.44\linewidth}]{2}}
\def\vlatin{Fidélium ánimæ per misericórdiam Dei requiéscant in pace.\hfill{}Amen.}
\let\rlatin=\undefined
\def\vtranslation{May the souls of the faithful departed through the mercy of God rest in peace.\hfill{}Amen.}
\let\rtranslation=\undefined
\printvrwithtranslation{}

\bigskip
\printnote{If Pontifical Mass is to follow, the \emph{\Vbar{}~Benedicámus Dómino} is sung by the Cantors in one of the following tones; and the \emph{\Vbar{}~Fidelium} is not said.}
\medskip
\input{inc-benedicamus-domino}

}