{
	\label{pentecost}
  \chapter{Proper of the Time -- Pentecost Octave}
  \section{Pentecost Sunday}
  {
    \def\printhymn{.
      \label{hymn-pentecost}
      {\def\gabcfolder{../Pentecost}
        \printgabc{Hymn}{8.}{V}{Hymn-VeniCreatorSpiritus}

        \renewcommand{\hymntranslation}{
          \item Thou, Holy Ghost, Creater, come,
          and make Thy people's souls Thy home:
          with grace celestial animate
          the hearts Thou didst Thyself create.

          \item The Paraclete from God above,
          Thou art His gift, Thou art His love:
          the fount of life and burning zeal
          and of our souls th'anointing seal.

          \item As sevenfold Thy gifts expand,
          the finger Thou of God's right hand:
          the Father's promise well fulfilled,
          Thy truths in us Thou hast instilled.

          \item Our minds enkindle with Thy light,
          within our hearts Thy love excite:
          do Thou endue our members frail
          with strength of Thine that ne'er can fail.

          \item Far keep from us our ancient foe,
          without delay Thy peace bestow:
          be Thou our guide: do Thou forestall
          the many ills our path entrall.

          \item Through Thee may we the Father know,
          the Son's effulgence deign to show:
          in blessing Thee from either sent,
          may our eternal years be spent!

          \item To God the Father, to God the Son,
          Who over death the vistory won,
          to both and to the Paraclete,
          we raise our hearts with thanks replete.
          Amen.%\grechangestaffsize{15}
        }

        \selectlanguage{american}\vspace{-0.5\baselineskip}
        \begin{multicols}{2}
        \begin{psalmverses}
        {\hymntranslation}
        \end{psalmverses}
        \end{multicols}

      }

      %\printrefshymn{ant}
      \bigskip
    }
    \def\printshortresp{%
      \label{shortresp-pentecost}%
      {\def\gabcfolder{.}
      \printgabc{Short}{Resp.}{S}{re--spiritus_domini--solesmes_1961.gabc}}

      \translation[]{\Vbar{}~The Spirit of the Lord filleth the world. Alleluia, Alleluia.
        \Rbar{}~The Spirit\dots{}
        \Vbar{}~And That Which containeth all things hath knowledge of the voice.
        \Rbar{}~Alleluia, alleluia.
        \Vbar{}~Glory be\dots{}
        \Rbar{}~The Spirit\dots{}
      }

      \bigskip
      \gresetinitiallines{0}\label{vr-pentecost}
      \gregorioscore{vr-spiritus-paraclitus}
      \let\myhwidth\relax
      \let\myhhwidth\relax
      \newlength{\myhwidth}
      \settowidth{\myhwidth}{allelui} %this is what precedes the last vowel in the response
      \newlength{\myhhwidth}
      \settowidth{\myhhwidth}{i} %this is what preceded the last vowel in the verse
      \addtolength{\myhhwidth}{-\myhwidth}
      \def\myhspace{\hspace{1.4ex}}
      \begin{nstabbing}
      \>\Rbar{}~Docébit vos ómnia, \>\hspace{\myhhwidth}allelúia.
      \end{nstabbing}

      \translation[]{\Vbar{}~The Comforter, Which is the Holy Ghost, alleluia.\\
        \Rbar{}~Shall teach you all things, alleluia.}

      \bigskip
    }
    \printterce[../Pentecost]{inc-PentecostVespers}{pentecost}
  }
  {
    \let\printhymn=\printhymnfeastref
    \def\printshortresp{%
      \label{shortresp-trinity}%
      {\def\gabcfolder{.}
      \printgabc{Short}{Resp.}{B}{re--benedicamus_patrem--solesmes_1961.gabc}}

      \translation[]{\Vbar{}~Bless we the Father, and the Son, and the Holy Ghost.
        \Rbar{}~Bless\dots{}
        \Vbar{}~Let us praise and exalt Him above all for ever.
        \Rbar{}~And the Holy Ghost.
        \Vbar{}~Glory be\dots{}
        \Rbar{}~Bless\dots{}
      }

      \bigskip
      \gresetinitiallines{0}\label{vr-trinity}
      \gregorioscore{vr-benedictus-es}
      \let\myhwidth\relax
      \let\myhhwidth\relax
      \newlength{\myhwidth}
      \settowidth{\myhwidth}{sǽcul} %this is what precedes the last vowel in the response
      \newlength{\myhhwidth}
      \settowidth{\myhhwidth}{t} %this is what preceded the last vowel in the verse
      \addtolength{\myhhwidth}{-\myhwidth}
      \def\myhspace{\hspace{2.4ex}}
      \begin{nstabbing}
      \>\Rbar{}~Et\myhspace{} laudábilis\myhspace{} et\myhspace{} gloriósus\myhspace{} in \>\hspace{\myhhwidth}sǽcula.
      \end{nstabbing}

      \translation[]{\Vbar{}~Blessed art Thou, O Lord, in the firmament of heaven.\\
        \Rbar{}~And to be praised and glorified for ever.}

      \bigskip
    }
    \section{Trinity Sunday}
    \printterce[../TrinitySunday]{inc-TrinitySunday-Vespers}{trinity}
  }

}