{
  \section{1 July: The Precious Blood of our Lord Jesus Christ}
  \def\gabcfolder{.}
  \def\printshortresp{%
    \label{shortresp-jul1}%
    {\def\gabcfolder{.}
      \printgabc{Short}{Resp.}{R}{rb--redemisti_nos_domine--solesmes_1961}
    
      \translation[]{\Vbar{}~Lord, Thou hast redeemed us * by Thy Blood.
        \Rbar{}~Lord,~\dots
        \Vbar{}~Out of every kindred, and tongue, and people.
        \Rbar{}~By Thy Blood.
        \Vbar{}~Glory be\dots{}
        \Rbar{}~Lord,~\dots
      }
    }

    \bigskip
    \gresetinitiallines{0}\label{vr-jul1}
    \gregorioscore{vr-sanguis}
    \let\myhwidth\relax
    \let\myhhwidth\relax
    \newlength{\myhwidth}
    \settowidth{\myhwidth}{peccát}
    \newlength{\myhhwidth}
    \settowidth{\myhhwidth}{}
    \addtolength{\myhhwidth}{-\myhwidth}
    \def\myhspace{\hspace{0.7ex}}
    \begin{nstabbing}
    %\>\Rbar{}~Et\myhspace{} omnes\myhspace{} reges\myhspace{} terræ\myhspace{} glóriam \>\hspace{\myhhwidth}tuam.
    \>\Rbar{}~Emúndat\myhspace{} nos\myhspace{} ab\myhspace{} omni \>\hspace{\myhhwidth}peccáto.
    \end{nstabbing}

    \translation[]{\Vbar{}~The Blood of Jesus Christ, the Son of God\\
      \Rbar{}~Cleanseth us from all sin.}

    \bigskip
  }
  \newcommand{\anttwotex}{an--hi_sunt_qui_venerunt--solesmes_1961}
  \newcommand{\anttwoinitial}{H}
  \newcommand{\anttwotranslation}{These are they which came out of great tribulation, and have washed their robes and made them white in the Blood of the Lamb.}
  \definepsalm{2}{109}{1}{a3}
  \newcommand{\chaptertext}{\dropcap{latin}{Fratres~: Christus assístens póntifex futurórum bonórum, per ámplius et perféctius tabernáculum non manufáctum, id est non hujus} cre\-a\-ti\-\textbf{ó}nis~:~\dag{} neque per sánguinem hircórum aut vitulórum, sed per próprium sánguinem introívit se\-\emph{mel in} \textbf{Sá}ncta,~* ætérna redemptióne in\textbf{vén}ta.}
  \newcommand{\chaptertranslation}{Brethren: Christ being come a High Priest of the good things to come, by a greater and more perfect tabernacle, not made with hands, that is, not of this creation: neither by the blood of goats or of calves, but by His own Blood, entered once into the Holies, having obtained eternal redemption.}
  \newcommand{\collect}{Omnípotens sempitérne Deus, qui unigénitum Fílium tuum mundi Redemptórem constituísti, ac ejus sánguine placári voluísti~:~\dag{} concéde, quǽsumus, sálutis nostræ prétium solémni cultu ita venerári, atque a præséntis vitæ malis ejus virtúte deféndi in terris;~* ut fructu perpétuo lætémur in cælis. Per eúmdem Dóminum nostrum.}
  \newcommand{\collecttranslation}{Almighty everlasting God, who didst appoint Thine only-begotten Son to be Redeemer of the world, and didst vouchsafe to be appeased by His Blood: grant, we beseech Thee, that, by our solemn service, we may so venerate the Price of our redemption, and by its power be so defended from the evils of this present life on earth, that we may enjoy its fruit for evermore in heaven. Through the same our Lord.}


  \printterce{}{jul1}
}