% !TEX TS-program = lualatex
% !TEX encoding = UTF-8
\usepackage{../definepsalms}

\newcommand{\predeusinadjutorium}{%
\smallskip
\large
\setgrefactor{15}
}
\def\deusinadjutoriumsolemn{T}
\def\includelaustibi{F}

\newcommand{\preantone}{\setgrefactor{17}
\large
%\greblockcustos
}
\newcommand{\antoneinitialsize}{40}
\newcommand{\antonetex}{Ant1-AnteLuciferumGenitus}
\newcommand{\antoneinitial}{A}
\newcommand{\antonetranslation}{The Lord our Saviour, begotten before the day-star, and before the ages, is this day made manifest in the world.}
\definepsalm{1}{109}{2}{D}
\newcommand{\prepsalmone}{%
%\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\setgrefactor{17}
%\greblockcustos
\large
}
\newcommand{\anttwoinitialsize}{40}
\newcommand{\anttwotex}{Ant2-VenitLumenTuum}
\newcommand{\anttwoinitial}{V}
\newcommand{\anttwotranslation}{O Jerusalem, thy light is come, and the glory of the Lord is risen upon thee, and the Gentiles shall walk in thy light, alleluia.}
\definepsalm{2}{110}{1}{g2}
\newcommand{\prepsalmtwo}{%
\normalsize
\greblockcustos
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\setgrefactor{17}
\large
%\greblockcustos
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{Ant3-ApertisThesaurisSuis}
\newcommand{\antthreeinitial}{A}
\newcommand{\antthreetranslation}{When the wise men had opened their treasures, they presented unto the Lord gold, frankincense, and myrrh, alleluia.}
\definepsalm{3}{111}{1}{g2}
\newcommand{\prepsalmthree}{%
\normalsize
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\setgrefactor{17}
%\greblockcustos
\large
}
\newcommand{\antfourinitialsize}{26}
\newcommand{\antfourtex}{Ant4-MariaEtFlumina}
\newcommand{\antfourinitial}{M}
\newcommand{\antfourtranslation}{O ye seas and floods, bless ye the Lord. O ye wells, bless ye the Lord, alleluia.}
\newcommand{\psalmfourtranslationsmall}{T}
\definepsalm{4}{112}{4}{E}
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\setgrefactor{15}
\normalsize
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfive}{\setgrefactor{17}
%\greblockcustos
\large
}
%\newcommand{\preantfivetwo}{\preantfive}
%\newcommand{\antfivefontsizetwo}{34}

\newcommand{\antfiveinitialsize}{34}
\newcommand{\antfivetex}{Ant5-StellaIsta}
\newcommand{\antfiveinitial}{S}
\newcommand{\antfivetranslation}{This star shineth as a flame of fire, and pointeth out God, the King of kings: the Wise Men beheld it, and offered gifts unto the great King.}
%\definepsalm{5}{113}{7}{c2}
\newcommand{\prepsalmfive}{%
%\vspace{-1ex}
%\setgrefactor{15}%
\normalsize%
}
%\newcommand{\dontrepeatantiphon}{T}
%\newcommand{\prepsalmfiveverses}{
%\vspace{-10pt}
%}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\hymn}{Crudelis Herodes}
\newcommand{\hymnlinetwo}{3.}
\newcommand{\hymninitial}{C}
\newcommand{\prehymn}{%
\setgrefactor{17}
\normalsize
}
\newcommand{\hymntex}{hymn-CrudelisHerodes}
\newcommand{\hymntranslation}{%
\item Why, impious Herod, vainly fear
That Christ the Saviour cometh here?
He takes no earthly realms away
Who gives the crown that lasts for aye.

\item To greet His birth the Wise Men went,
Led by the star before them sent;
Called on by light, towards light they pressed,
And by their gifts their God confessed.

\item In holy Jordan's purest wave
The heavenly Lamb vouchsafed to lave;
That He, to Whom was sin unknown,
Might cleanse His people from their own.

\item New miracle of power divine!
The water reddens into wine:
He spake the word: and poured the wave
In other streams than nature gave.

\item All glory, Lord, to Thee we pay
For Thine Epiphany to-day:
All glory, as is ever meet,
To Father and to Paraclete.
Amen.\setgrefactor{15}
}

\newcommand{\chapter}{\dropcap{latin}{Surge, illumináre Jerúsalem, quia venit} \emph{lumen} \textbf{tú}\-um,~* et glória Dómini super te \textbf{ór}ta est.}
\newcommand{\chaptertranslation}{Arise, be enlightened, O Jerusalem, for thy light is come, and the glory of God is risen upon thee.}

\newcommand{\vrtex}{vrRegesTharsis}
\newcommand{\vtranslation}{The kings of Tarshish and of the isles shall bring presents.}
\newcommand{\rtranslation}{The kings of Arabia and Saba shall offer gifts.}
\def\vrnospace{F}

%\newcommand{\premagtwo}{
%\setgrefactor{16}
%}
\newcommand\pagebreakbeforemagnificat{T}
\newcommand{\magfontsize}{33}
\def\magsolemn{T}

\newcommand{\collect}{Deus, qui hodiérna die Unigénitum tuum géntibus stella duce revelásti~:~\dag{} concéde propítius; ut qui jam te ex fide cognóvimus,~* usque ad contemplándam spéciem tuæ celsitúdinis perducámur. Per eúmdem Dóminum.}
\newcommand{\collecttranslation}{O God, Who by the leading of a star didst, as on this day, manifest Thine Only-begotten Son to the Gentiles, mercifully grant that we, who know Thee now by faith, may after this life have the fruition of Thy glorious Godhead.  Through the same Jesus Christ our Lord.}
