%\pagebreak
\bigskip\bigskip
\def\matinsnocturn{3rd Nocturn}
\label{friday-3}
\writeheading{In the 3rd Nocturn}
%
\large
%\printgabc{1. Ant.}{8. c.}{Z}{an--zelus_domus_tuae--solesmes}
{
\def\preant{\setgrefactor{17}\large}
%\def\preantafter{\setgrefactor{17}\normalsize}
\def\dontrepeatantiphon{T}
\def\prerepeatantiphon{\vspace{-12pt}}
\def\prepsalm{\greblockcustos\normalsize\setgrefactor{15}}
\def\anttranslation{From them that rise up against me deliver me, O Lord: for they have seized my soul.}
\def\psalmtranslationsmall{T}
%\def\lalinebreakaftereighteen{T}
%\def\lalinebreakafterverse{18}
%\def\enlinebreakaftereighteen{T}
\printpsalm{1}{58}{1f}{an--ab_insurgentibus--solesmes}{A}
\let\prepsalm=\undefined
}
%
%\medskip
%\hfill\rule{3in}{0.5pt}\hfill
%\printseparation
\smallskip
{
\def\preant{\setgrefactor{17}\large}
\def\preantafter{\setgrefactor{15}\normalsize}
\def\prepsalm{\normalsize\setgrefactor{15}}
\def\prepsalmverses{\vspace{-8pt}}
%\def\dontrepeatantiphon{T}
%\def\prerepeatantiphon{\vspace{-20pt}}
\def\psalmtranslationsmall{T}
\def\anttranslation{Thou hast put away mine acquaintance far from me; I was delivered up, and came not forth.}
%\def\enlinebreakaftertwelve{T}
\printpsalm{2}{87}{8G}{an--longe_fecisti--solesmes}{L}
\let\prepsalm=\undefined
}
%
\printseparation{}
{
\def\preant{\setgrefactor{17}\large}
\def\prepsalm{\normalsize\setgrefactor{15}}
\def\psalmtranslationsmall{T}
\def\dontrepeatantiphon{T}
\def\anttranslation{They shall conspire against the soul of the just, and condemn the innocent blood.}
\printpsalm{3}{93}{8G}{an--captabunt--solesmes}{C}
}%
%
%\bigskip%\bigskip
{
\printvr[\setgrefactor{14}\normalsize]{vr-locutiSunt}
{They have spoken against me with a deceitful tongue.}
{And with words of hatred they encompassed me, and fought against me without cause.}
}

\bigskip
Pater noster. \emph{in silence.}

\begin{center}
De Epístola beáti Pauli Apóstoli ad Hebrǽos
%\translation{From the letter of the blessed Apostle Paul to the Jews}
\end{center}
\hspace{10ex}\textsc{lesson vii}\hfill\emph{Chap. 4, 11-16 et 5, 1-10}\hspace{10ex}
\begin{parcolumns}[rulebetween,colwidths={1=0.5\linewidth}]{2}
\lesson[\normalsize]{Festinémus íngredi in illam réquiem~: ut ne in idípsum quis íncidat incredulitátis exémplum.
Vivus est enim sermo Dei, et éfficax, et penetrabílior omni gládio ancípiti~: et pertíngens usque ad divisiónem ánimæ ac spíritus, compágum quoque ac medullárum, et discrétor cogitatiónum et intentiónum cordis.
Et non est ulla creatúra invisíbilis in conspéctu ejus~: ómnia autem nuda et apérta sunt óculis ejus, ad quem nobis sermo.
Habéntes ergo Pontíficem magnum, qui penetrávit cælos, Jesum Fílium Dei~: teneámus confessiónem.
Non enim habémus Pontíficem qui non possit cómpati infirmitátibus nostris~: tentátum autem per ómnia pro}{similitúdine \textbf{abs}que pec\textbf{cá}to.}
{Let us hasten therefore to enter into that rest; lest any man fall into the same example of unbelief.
For the word of God is living and effectual, and more piercing than any two edged sword; and reaching unto the division of the soul and the spirit, of the joints also and the marrow, and is a discerner of the thoughts and intents of the heart.
Neither is there any creature invisible in his sight: but all things are naked and open to his eyes, to whom our speech is.
Having therefore a great high priest that hath passed into the heavens, Jesus the Son of God: let us hold fast our confession.
For we have not a high priest, who cannot have compassion on our infirmities: but one tempted in all things like as we are, yet without sin.}
\end{parcolumns}

\medskip

\bigskip\bigskip
%\pagebreak

\setgrefactor{17}
\printgabc{Resp. 7}{5.}{T}{re--tradiderunt--solesmes}

{
\translationcolumns[\normalsize]{\Rbar{}~They delivered Me into the hands of the impious, and cast me out among the wicked, and spared not My life: the mighty gathered together against Me
* And stood up against Me like giants.
\Vbar{}~Strangers rose up against Me, and the mighty sought My soul.
\Rbar{}~And stood up against Me like giants.}
}

\needspace{2\baselineskip}
\begin{center}{\textsc{lesson viii}}\end{center}

\begin{parcolumns}[rulebetween,colwidths={1=0.5\linewidth}]{2}
\lesson[\normalsize]{Adeámus ergo cum fidúcia ad thronum grátiae~: ut misericórdiam consequámur, et grátiam inveniámus in auxílio opportúno.
Omnis namque Póntifex, ex homínibus assúmptus, pro homínibus constitúitur in iis, quæ sunt ad Deum, ut ófferat dona et sacrifícia pro peccátis~:
qui condolére possit iis qui ignórant et errant~: quóniam et ipse circúmdatus est infirmitáte~:
et proptérea debet, quemádmodum pro pópulo, ita étiam pro semetípso}{offérre \textbf{pro} pec\textbf{cá}tis.}
{Let us go therefore with confidence to the throne of grace: that we may obtain mercy, and find grace in seasonable aid.
For every high priest taken from among men, is ordained for men in things pertaining to God, that he may offer up gifts and sacrifices for sins:
Who can have compassion on them that are ignorant and that err: because he himself also is compassed with infirmity.
And therefore he ought, as for the people, so also for himself, to offer for sins.}
\end{parcolumns}

\bigskip\bigskip
%\pagebreak

\printgabc{Resp. 8}{8.}{J}{re--jesum_tradidit--solesmes}

{
\translationcolumns[\normalsize]{\Rbar{}~An impious man betrayed Jesus to the chief priests and elders of the people
* But Peter followed Him from afar, to see the end.
\Vbar{}~And they led Him away to Caiphas the High Priest, where the Scribes and Pharisees were assembled.
\Rbar{}~But Peter followed~\dots}
}

%\pagebreak
\begin{center}{\textsc{lesson ix}}\end{center}

\begin{parcolumns}[rulebetween,colwidths={1=0.5\linewidth}]{2}
\lesson[\normalsize]{Nec quisquam sumit sibi honórem, sed qui vocátur a Deo, tamquam Aaron.
Sic et Christus non semetípsum clarificávit ut Póntifex fíeret~: sed qui locútus est ad eum~: Fílius meus es tu, ego hódie génui te.
Quemádmodum et in álio loco dicit~: Tu es sacérdos in ætérnum secúndum órdinem Melchísedech.
Qui in diébus carnis suæ, preces supplicationésque ad eum, qui possit illum salvum fácere a morte, cum clamóre válido et lácrimis, ófferens, exaudítus est pro sua reveréntia.
Et quidem cum esset Fílius Dei, dídicit ex iis quæ passus est, obediéntiam~:
et consummátus, factus est ómnibus obtemperántibus sibi causa salútis ætérnæ,
appellátus a Deo Póntifex}{juxta órdi\textbf{nem} Mel\textbf{chí}sedech.}
{Neither doth any man take the honour to himself, but he that is called by God, as Aaron was.
So also Christ glorified not himself to be made a high priest: but he that said unto him: Thou art my Son, today have I begotten thee.
As he saith also in another place: Thou art a priest for ever, according to the order of Melchisedech.
Who in the days of his flesh, with a strong cry and tears, offering up prayers and supplications to him that was able to save him from death, was heard for his reverence.
And whereas indeed he was the Son of God, he learned obedience by the things which he suffered:
And being consummated, he became, to all that obey him, the cause of eternal salvation.
Called by God a high priest according to the order of Melchisedech.}
\end{parcolumns}

\bigskip\bigskip
\bigskip\bigskip
%\pagebreak

\printgabc{Resp. 9}{5.}{C}{re--caligaverunt--solesmes}

\translationcolumns[\normalsize]{\Rbar{}~Mine eyes do fail with tears, for He is far from Me that comforted Me. Behold, all ye peoples
* If there be any sorrow like unto my sorrow.
\Vbar{}~O all ye that pass by, behold, and see.
\Rbar{}~If there be~\dots{}
\Rbar{}~Mine eyes~\dots}
\pagebreak