%\pagebreak
%\needspace{4\baselineskip}
\writeheading{In the 2nd Nocturn}
\def\matinsnocturn{2nd Nocturn}
%
\large
%\printgabc{1. Ant.}{8. c.}{Z}{an--zelus_domus_tuae--solesmes}
\def\nogloriapatri{T}
{
\def\preant{\setgrefactor{17}\large}
\def\prepsalm{\setgrefactor{14}\normalsize}
\def\prepsalmverses{\vspace{-10pt}}
%\def\dontrepeatantiphon{T}
\def\psalmtranslationsmall{T}
%\def\lalinebreakafterverse{16}
%\def\enlinebreakaftersixteen{T}
\def\anttranslation{They used violence that sought my soul.}
\printpsalm{1}{37}{8G}{an--vim_faciebant--solesmes}{V}
}
%
\printseparation
\bigskip
{
\def\preant{\setgrefactor{17}\large}
\def\preantafter{\setgrefactor{17}\normalsize}
\def\psalmtranslationsmall{T}
\def\prepsalm{\normalsize}
%\def\enlinebreakafternine{T}
\def\anttranslation{Let them be confounded and put to shame, that seek after my soul, to take it.}
\printpsalm{2}{39}{4A}{an--confundantur_et_revereantur--solesmes}{C}
}
%
\printseparation
%\pagebreak
{
\def\preant{\setgrefactor{17}\large}
\def\prepsalm{\normalsize\setgrefactor{15}}
\def\prepsalmverses{\vspace{-14pt}}
%\def\dontrepeatantiphon{T}
\def\psalmtranslationsmall{T}
\def\anttranslation{Strangers have risen up against me, and the mighty have sought after my soul.}
\printpsalm{3}{53}{4A}{an--alieni_insurrexerunt--solesmes}{A}
\let\prepsalm=\undefined
}
%psalm 70 - In te, Domine, speravi

\medskip
{\def\vrnospace{T}
\printvr[\setgrefactor{15}\normalsize]{vr-insurrexerunt}
{False witnesses are risen up against me.}
{And iniquity hath belied itself.}
}

\bigskip
Pater noster. \emph{in silence.}

\pagebreak
\begin{center}
Ex Tractátu sancti Augustíni Epíscopi super Psalmos
%\translation{From the treatise of St Augustine, Bishop, upon the psalms}
\end{center}
\hspace{10ex}\textsc{lesson iv}\hfill\emph{On Ps. 63, at verse 2}\hspace{10ex}

\ifnotsmallbook{
\ifx\undefined\useparacol
\begin{parcolumns}[rulebetween,colwidths={1=240pt}]{2}
\else
\begin{columns}
\fi
}
\ifsmallbook{\begin{columns}}
\lesson[\normalsize]{Protexísti me, Deus, a convéntu malignántium, a multitúdine operántium iniquitátem. Jam ipsum caput nostrum intueámur. Multi mártyres tália passi sunt, sed nihil sic elúcet, quómodo caput mártyrum~: ibi mélius intuémur, quod illi expérti sunt. Protéctus est a multitúdine malignántium, protegénte se Deo, protegénte carnem suam ipso Fílio, et hómine, quem gerébat~: quia fílius hóminis est, et Fílius Dei est~: Fílius Dei, propter formam Dei~: fílius hóminis, propter formam servi, habens in potestáte pónere ánimam suam, et recípere eam. Quid ei potuérunt}{fácere in\-\emph{imíci}? Occidérunt corpus, ánimam non occidérunt. Inténdite. Parum ergo erat, Dóminum hortári mártyres verbo, nisi fir\textbf{má}ret ex\textbf{émp}lo.}
{Thou hast protected me, O God, from the counsel of the wicked, from the insurrection of the workers of iniquity. Now let us contemplate our Head himself. Many martyrs have suffered like things, but naught shineth out in such wise as the Head of the Martyrs; in Him we best perceive what they endured. He was protected from the counsel of the wicked; God protected himself; the Very Son, with the manhood which he took upon him, protected his own flesh; because He is the Son of man, and the Son of God; Son of God, being in the form of God; Son of man, being in the form of a servant, having power to lay down his life, and to take it up again. What then could his enemies do against him? They killed the Body, the Soul they killed not. Give heed: It had been a small thing for the Lord to encourage Martyrs by His word, if He had not also strengthened them by His example.}
\ifnotsmallbook{
\ifx\undefined\useparacol
\end{parcolumns}
\else
\end{columns}
\fi
}
\ifsmallbook{\end{columns}}
\medskip

\bigskip\bigskip
%\pagebreak

\setgrefactor{17}
\printgabc{Resp. 4}{8.}{T}{re--tamquam_ad_latronem--solesmes}

{\translationcolumns[\normalsize]{\Rbar{}~Ye are come out, as against a thief, with swords and clubs to take Me:
* I was daily with you, teaching in the Temple, and ye laid no hold on Me; and, now when ye have scourged Me, ye lead Me away to crucify Me.
\Vbar{}~And when they had laid hands on Jesus, and taken Him, He said unto them:
\Rbar{}~I was daily with you~\dots}}

\bigskip\bigskip
\needspace{2\baselineskip}
\begin{center}{\textsc{lesson v}}\end{center}

\begin{columns}
\lesson[\normalsize]{Nostis qui convéntus erat malignántium Judæórum, et quæ multitúdo erat operántium iniquitátem.}{Quam ini\-\emph{quitátem}? Quia voluérunt occídere Dóminum Jesum Christum. Tanta ópera bona, inquit, osténdi vobis~: propter quod horum me vultis oc\-\emph{cídere}? Pértulit omnes infírmos eórum, curávit omnes lánguidos eórum, prædicávit regnum cælórum, non tácuit vítia eórum, ut ipsa pótius eis displicérent, non médicus, a quo sanabántur. His ómnibus curatiónibus ejus ingráti, tamquam multa febre phrenétici, insaniéntes in médicum qui vénerat curáre eos, excogitavérunt consílium perdéndi eum~: tamquam ibi voléntes probáre, utrum vere homo sit, qui mori possit, an áliquid super hómines sit, et mori se non permíttat. Verbum ipsórum agnóscimus in Sapiéntia Salomónis~: Morte turpíssima, ínquiunt, condemnémus eum. Interrogémus eum~: erit enim respéctus in sermónibus illíus. Si enim vere Fílius Dei est, \textbf{lí}beret \textbf{e}um.}
{Ye know what the counsel was of the wicked Jews, and what that insurrection was of the workers of iniquity. What was their iniquity? That they wanted to kill the Lord Jesus Christ. Many good works, saith He, have I showed you; for which of them do you want to kill Me? He had borne with all their weaknesses: He had healed all their diseases: He had preached unto them the kingdom of heaven: He held not his peace at their iniquities, that they might hate them rather than the Physician That came to cure them. And now at last, without gratitude for all the tenderness of His healing love, like men raging in an high delirium, throwing themselves madly on the Physician, Who had come to cure them, they took counsel together how they might kill Him, as if to see if He were a Man and could die, or Something more than a man that would not let Himself die. In the Wisdom of Solomon we recognize their words: Let us condemn Him with a shameful death. Let us examine Him; for, by His own saying, He shall be respected. If He be the Son of God, let Him help Him.}
\end{columns}

\bigskip\bigskip
\pagebreak

\printgabc{Resp. 5}{7.}{T}{re--tenebrae--solesmes}

{\translationcolumns[\normalsize]{\Rbar{}~Darkness covered the land when the Jews crucified Jesus: and about the ninth hour Jesus cried with a loud voice: My God, why hast Thou forsaken Me?
* And He bowed His Head, and gave up the Ghost.
\Vbar{}~Jesus, crying with a loud voice, said: Father, into thy hands I commend My Spirit.
\Rbar{}~And He bowed~\dots}}

%\needspace{2\baselineskip}
\pagebreak
\begin{center}{\textsc{lesson vi}}\end{center}
\begin{columns}
\lesson[\normalsize]{Exacuérunt tamquam gládium linguas suas. Non dicant Judǽi~: Non occídimus Christum. Etenim proptérea eum dedérunt júdici Piláto, ut quasi ipsi a morte ejus videréntur immúnes. Nam cum dixísset eis Pilátus~: Vos eum occídite, respondérunt~: Nobis non licet occídere quemquam. Iniquitátem facínoris sui in júdicem hóminem refúndere volébant~: sed numquid Deum}{júdicem \emph{fallébant}? Quod fecit Pilátus, in eo ipso quod fecit, aliquántum párticeps fuit~: sed in comparatióne illórum, multo ipse innocéntior. Institit enim quantum pótuit, ut illum ex eórum mánibus liberáret~: nam proptérea flagellátum prodúxit ad eos. Non persequéndo Dóminum flagellávit, sed eórum furóri sa\-tis\-fá\-ce\-re volens~: ut vel sic jam mitéscerent, et desínerent velle occídere, cum flagellátum vidérent. Fecit et hoc. At ubi perseveravérunt, nostis illum lavísse manus, et dixísse, quod ipse non fecísset, mundum se esse a morte illíus. Fecit tamen. Sed si reus, quia fecit vel invítus~: illi innocéntes, qui coëgérunt ut \emph{fáceret}? Nullo modo. Sed ille dixit in eum senténtiam, et jussit eum crucifígi, et quasi ipse occídit~: et vos, o Judǽi, occidístis. Unde oc\-\emph{cidístis}? Gládio línguæ~: acuístis enim linguas vestras. Et quando percussístis, nisi quando clamástis~: Crucifíge, \textbf{cru}ci\textbf{fí}ge?}
{They whetted their tongue like a sword. Let not the Jews say: We did not kill Christ. For they gave Him over to Pilate the judge, that they themselves might seem free of His death. For when Pilate said unto them, Take ye Him: and kill Him, they answered, It is not lawful for us to put any man to death. They desired to cast the injustice of their wicked deed upon a human judge: but did they deceive God the Judge? In that which Pilate did, he was their accomplice, but in comparison with them, he was much more innocent. Pilate strove as far as he could, to deliver Him out of their hands and therefore ordered Him to be scourged and brought before them. He scourged not the Lord in persecution, but to satisfy their rage: that, perchance, even they might be touched with compassion, and cease to lust for His death, when they saw What He was after the flagellation. Even this effort he made! But when they persisted, ye know how he washed his hands and said that he did it not himself, the he was innocent of His death. Nevertheless he did do it. But if he were guilty who did it against his will, were they innocent who goaded him on to it? No. Pilate gave sentence against Him and commanded Him to be crucified, and thus in a manner slew him. But ye, O ye Jews, ye have killed Him! How did ye kill him? With the sword of the tongue, for ye had whet your tongues. And when smote ye? But when ye cried, Crucify Him! Crucify Him!}
\end{columns}

\bigskip\bigskip
%\needspace{2\baselineskip}
\pagebreak
\printgabc{Resp. 6}{8.}{A}{re--animam_meam--solesmes}

{\translationcolumns[\normalsize]{\Rbar{}~I have delivered my dearly-beloved soul into the hands of the wicked, and Mine inheritance is become unto Me as a lion in the forest; the enemy cried out against Me, saying: Assemble yourselves together, hasten to devour Him: they have placed Me in a desolate wilderness, and the whole land mourned for Me:
* Because there was none found that would know Me, and do well.
\Vbar{}~Men without mercy rose up against Me, and spared not my soul.
\Rbar{}~Because there was none~\dots{}
\Rbar{}~I have delivered~\dots}}
\pagebreak