%\pagebreak
%\medskip
\needspace{4\baselineskip}
%\bigskip\bigskip
\label{thursday-lauds}
\writeheading{At Lauds}
\global\let\matinsnocturn=\undefined
\gdef\officehour{Lauds}
%
\myantsize
\def\nogloriapatri{T}
%\def\preant{\myantsize}
\let\preantafter=\undefined
\def\psalmtranslationsmall{F}
%\def\lalinebreakafterverse{5}
{\def\anttranslation{Be Thou justified in Thy words, O Lord, and do Thou overcome when judged.}
\def\lalinebreakafterverse{11}
\printpsalm{1}{50}{8G}{an--justificeris_domine--solesmes}{J}}
%
\printseparation
\pagebreak
%\needspace{12\baselineskip}
{\def\dontrepeatantiphon{T}
\def\anttranslation{The Lord was led as a sheep to the slaughter, and opened not His mouth.\bigskip}
\def\prepsalmverses{\medskip}
\printpsalm{2}{89}{2D}{an--dominus_tamquam_ovis--solesmes}{D}
}%
%\printseparation
%\pagebreak
{%\def\prepsalm{\mypsalmsize}
%\def\dontrepeatantiphon{T}
\def\anttranslation{My heart is broken within me: all my bones have trembled.}
\printpsalm{3}{35}{8G}{an--contritum_est_cor_meum--solesmes}{C}
}%
\needspace{8\baselineskip}
\printseparation
\bigskip\bigskip
{
	\def\anttranslation{Thou hast spoken unto us in Thy strength, and in Thy Holy Banquet, O Lord.}
	\def\canticleof{Moses}
	\def\canticleverses{Exod. 15, 1-19}
	%\def\prepsalm{\greseteolcustos{manual}} %15
	%\def\prepsalmtitle{\vspace*{-0.5\baselineskip}}
	\def\postpsalmtitle{}%\vspace{-0.5\baselineskip}}
	\def\prepsalmverses{\smallskip}
	\def\lalinebreakafterverse{12}
	%\def\lalinebreakafterversex{14}
	\printpsalm{4}{exod15}{4A}{an--exhortatus_es--solesmes}{E}
	\let\canticleof=\undefined
	\let\canticleverses=\undefined
	\let\prepsalm=\undefined
}
%
\printseparation
\pagebreak
{%\def\prepsalm{\mypsalmsize}%\vspace{-0.5\baselineskip}}
\def\anttranslation{He was offered up because He willed it and He bore our sins.}
%\def\lalinebreakafterverse{3}
%\def\lalinebreakafterversex{3}
%\def\prerepeatantiphon{}
\def\dontrepeatantiphon{T}
\printpsalm{5}{146}{2D}{an--oblatus_est--solesmes}{O}
}\bigskip%\bigskip
\pagebreak
\myvrsize
{
%\def\vrnospace{T}
%\pagebreak
\greseteolcustos{manual}
\printvr{vr-HomoPacisMeae}{The man of my peace, in whom I trusted:} %15
{Who ate my bread, hath treacherously plotted against me.}
}

%\bigskip
%\pagebreak
%\printgabc{At Bened.}{Ant. 1. g}{T}{an--traditor_autem--solesmes}
\myantsize
{\def\magsolemn{T}
\def\premagtexverses{\vspace{-0.5\baselineskip}}
\def\prerepeatantiphon{}
%\def\preant{\myantsize}
%\def\premagtexverses{\vspace{-\baselineskip}}
\def\anttranslation{The traitor gave them a sign, saying: He whom I shall kiss, That Same is He: hold Him fast.}
\printmag[Benedictus]{1g}{T}{an--traditor_autem--solesmes}
}
%\emph{The candles on the triangular candlestick having been extinguished as has already been explained, the one at the top of the triangle alone remains lighted.  During the Canticle \emph{Benedíctus.} the candles on the altar are likewise extinguished one by one, from each side alternately, at every second verse, so that by the last verse all are extinguished.  All other lights and lamps in the church are also put out.}
\bigskip\bigskip
\myantsize
\emph{After the repetition of the Antiphon at the \emph{Benedíctus}, all kneel and sing :}
\medskip
\myrespsize
{\printgabc{Ant.}{5.}{C}{../Tenebrae/an--christus_factus_est--solesmes_thursday}
}%
\bigskip
%
\emph{When the antiphon \emph{Christus fáctus est} is finished, \emph{Páter nóster} is said, in silence throughout.}

\printpsalmrecto{50}

\emph{Then is sung, without \emph{Orémus}, to the ferial tone \emph{B} (or the ancient simple tone) :}
%
\bigskip

{\columnratio{0.5}
\begin{paracol}{2}
\begin{leftcolumn}%
	\mydropcap[latin]{Respice,}{quǽsumus, Dómine, super hanc famíliam tuam,~† pro qua Dóminus noster Jesus Christus non dubitávit mánibus tradi nocéntium,~* et crucis subíre torméntum.}
	\emph{And in silence~:}
	Qui tecum vivit et regnat\dots{}
\end{leftcolumn}
\begin{rightcolumn}%
	\mydropcap[american]{Look}{down, we beseech thee, O Lord, on this thy family, for which our Lord Jesus Christ did not hesitate to be delivered up into the hands of wicked men, and to suffer the torment of the Cross.}
\end{rightcolumn}
\end{paracol}
}

\bigskip

\prefiftyfiverubric{\emph{Strepitus, started by celebrant, until candle is brought out.}}

\emph{All then rise and retire in silence.}

\myantsize
