%\bigskip
%\pagebreak
\gdef\matinsnocturn{3rd Nocturn}
\label{thursday-3}
\writeheading[]{In the 3rd Nocturn}
%
\myantsize
\def\nogloriapatri{T}
\def\psalmtranslationsmall{F}
%\def\preant{\myantsize}
\let\preantafter=\undefined
%\def\prepsalmverses{\vspace{-0.5\baselineskip}}
{%\def\prepsalm{\vspace{-0.5\baselineskip}}
\def\dontrepeatantiphon{T}
\def\anttranslation{I said unto the wicked: Speak not wickedness against God.\vspace{-0.5\baselineskip}}
\printpsalm{1}{74}{7c}{an--dixi_iniquis--solesmes}{D}
}%
\printseparation
%\pagebreak
{%\def\prepsalm{\vspace{-0.5\baselineskip}}
%\def\prerepeatantiphon{}
\def\dontrepeatantiphon{T}
\def\anttranslation{The earth trembled and was still, when God arose in judgment.\vspace{-0.5\baselineskip}}
\printpsalm{2}{75}{8c}{an--terra_tremuit--solesmes}{T}
}%
\printseparation
%\pagebreak
%\def\lalinebreakafterverse{17}
%\def\dontrepeatantiphon{T}
\def\anttranslation{In the day of my tribulation I sought God with my hands.}
\printpsalm{3}{76}{7a}{an--in_die_tribulationis--solesmes}{I}

\bigskip%\pagebreak
\bigskip

%\def\vrnospace{T}
\myvrsize
{
	\printvr{vr-ExsurgeDomine}{Arise, O Lord.}{And judge my cause.}
}

\bigskip
Pater noster. \emph{in silence.}

\bigskip
\pagebreak
\mylessonsize
{\begin{center}
De Epístola prima beáti Pauli Apóstoli ad Corínthios
%\translation{From the first epistle of St Paul the Apostle to the Corinthians}
\end{center}

\hspace{10ex}\textsc{lesson vii}\hfill\emph{Chap. 11, 17-34}\hspace{10ex}
%\begin{parcolumns}[rulebetween,colwidths={1=0.45\linewidth}]{2}
\tenebraelesson{Hoc}{autem præcípio~: non laudans quod non in mélius, sed in detérius convenítis.
Primum quidem conveniéntibus vobis in Ecclésiam, áudio scissúras esse inter vos, et ex parte credo.
Nam opórtet et hǽreses esse, ut et qui probáti sunt, manifésti fiant in vobis.
Conveniéntibus ergo vobis in unum, jam non est Domínicam cenam manducáre.
Unusquísque enim suam cenam præsúmit ad manducándum, Et álius quidem ésurit, álius autem ébrius est.
Numquid domos non habétis ad manducándum, et \emph{bibéndum}? aut Ecclésiam Dei contémnitis, et confúnditis eos, qui \emph{non habent}? Quid di\-\emph{cam vobis}? \emph{Laudo vos}? In \textbf{hoc} non \textbf{lau}do.}
{Now this I ordain: not praising you, that you come together not for the better, but for the worse.
For first of all I hear that when you come together in the church, there are schisms among you; and in part I believe it.
For there must be also heresies: that they also, who are approved, may be made manifest among you.
When you come therefore together into one place, it is not now to eat the Lord's supper.
For every one taketh before his own supper to eat. And one indeed is hungry and another is drunk.
What, have you not houses to eat and to drink in? Or despise ye the church of God; and put them to shame that have not? What shall I say to you? Do I praise you? In this I praise you not.}
%\end{parcolumns}
%14
}
\medskip

\bigskip\bigskip

\myrespsize
{\label{resp7_eram_quasi_agnus}
\printgabc{Resp. 7}{7.}{E}{re--eram_quasi_agnus--solesmes}

\translationcolumns[\mytranslationsize]{\Rbar{}~I was like an innocent lamb: I was led to the sacrifice and I knew it not; mine enemies conspired against me, saying
* Come, let us put (poison of a deadly) tree into his bread, and root him out of the land of the living.
\Vbar{}~All mine enemies devised my hurt against me: they uttered a wicked speech against me, saying:
\Rbar{}~Come, let us put (poison of a deadly) tree into his bread, and root him out of the land of the living.}
}

\bigskip\bigskip
\mylessonsize
\begin{center}{\textsc{lesson viii}}\end{center}
%\begin{parcolumns}[rulebetween,colwidths={1=0.45\linewidth}]{2}
\tenebraelesson{Ego}{enim accépi a Dómino quod et trádidi vobis, quóniam Dóminus Jesus, in qua nocte tradebátur, accépit panem,
et grátias agens fregit, et dixit~: «Accípite et manducáte~: hoc est corpus meum, quod pro vobis tradétur~: hoc fácite in meam commemoratiónem».
Simíliter et cálicem, postquam cenávit, dicens~: «Hic calix novum testaméntum est in meo sánguine~: hoc fácite, quotiescúmque bibétis, in meam commemoratiónem».
Quotiescúmque enim manducábitis panem hunc, et cálicem bibétis~: mortem Dómini annuntiábitis, \textbf{do}nec \textbf{vé}niat.}
{For I have received of the Lord that which also I delivered unto you, that the Lord Jesus, the same night in which he was betrayed, took bread.
And giving thanks, broke, and said: Take ye, and eat: this is my body, which shall be delivered for you: this do for the commemoration of me.
In like manner also the chalice, after he had supped, saying: This chalice is the new testament in my blood: this do ye, as often as you shall drink, for the commemoration of me.
For as often as you shall eat this bread, and drink the chalice, you shall show the death of the Lord, until he come.}
%\end{parcolumns}

\bigskip\bigskip

\myrespsize
{\label{resp8_una_hora}
\printgabc{Resp. 8}{7.}{U}{re--una_hora--solesmes}

\translationcolumns[\mytranslationsize]{\Rbar{}~Could ye not watch with Me one hour, ye that called one on the other to die for Me?
* Or see ye not Judas, how he sleepeth not, but maketh haste to betray Me to the Jews?
\Vbar{}~Why sleep ye? Rise, and pray, lest ye enter into temptation.
\Rbar{}~Or see ye not Judas, how he sleepeth not, but maketh haste to betray Me to the Jews?}%
}%
\vspace{-6pt}
%\pagebreak
\bigskip\bigskip
\mylessonsize
\begin{center}{\textsc{lesson ix}}\end{center}
%\begin{parcolumns}[rulebetween,colwidths={1=0.44\linewidth}]{2}
\tenebraelesson{Itaque}{quicúmque manducáverit panem hunc vel bíberit cálicem Dómini indígne, reus erit córporis et sánguinis Dómini.
Probet autem seípsum homo~: et sic de pane illo edat et de cálice bibat.
Qui enim mandúcat et bibit indígne, judícium sibi mandúcat et bibit; non dijúdicans corpus Dómini.
Ideo inter vos multi infírmi et imbecílles, et dórmiunt multi.
Quod si nosmetípsos dijudicarémus, non útique judicarémur.
Dum judicámur autem, a Dómino corrípimur, ut non cum hoc mundo damnémur.
Itaque, fratres mei, cum convenítis ad manducándum, ínvicem exspectáte.
Si quis ésurit, domi mandúcet~: ut non in judícium conveniátis. Cétera autem, cum véne\textbf{ro}, dis\textbf{pó}nam.}
{Therefore whosoever shall eat this bread, or drink the chalice of the Lord unworthily, shall be guilty of the body and blood of the Lord.
But let a man prove himself: and so let him eat of that bread, and drink of the chalice.
For he that eateth and drinketh unworthily, eateth and drinketh judgment to himself, not discerning the body of the Lord.
Therefore are there many infirm and weak among you, and many sleep.
But if we would judge ourselves, we should not be judged.
But whilst we are judged, we are chastised by the Lord, that we be not condemned with this world.
Wherefore, my brethren, when you come together to eat, wait for one another.
If any man be hungry, let him eat at home; that you come not together unto judgment. And the rest I will set in order, when I come.}
%\end{parcolumns}\vspace*{-20pt}
%\pagebreak
\bigskip\bigskip

\needspace{4\baselineskip}
\myrespsize
{\label{resp9_seniores}
\printgabc{Resp. 9}{1.}{S}{re--seniores--solesmes}
}
\vspace{-0.5\baselineskip}
{
\translationcolumns[\mytranslationsize]{\Rbar{}~The elders of the people consulted
* That they might take Jesus by subtlety, and kill Him: they came out, as against a thief, with swords and clubs.
\Vbar{}~The chief Priests and the Pharisees gathered a council.
\Rbar{}~That they might take Jesus by subtlety, and kill Him: they came out, as against a thief, with swords and clubs.
\Rbar{}~The elders of the people~\dots}
}
\pagebreak
\myantsize
