% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Christus assístens póntifex futurórum bonórum, per ámplius et perféctius tabernáculum non manufáctum, id est, non hujus} creati\textbf{ó}\-nis~:~\dag{} neque per sánguinem hircórum aut vitulórum, sed per próprium sánguinem introívit se\emph{mel in} \textbf{San}\-cta,~* ætérna redemptióne in\textbf{vén}ta.}
\newcommand{\chaptertranslation}{Brethren: Christ being come, a High Priest of the good things to come, by a greater and more perfect tabernacle, not made by hands, that is, not of this creation: neither by the blood of goats or of calves, but by His own Blood, entered once into the Holies, having obtained eternal redemption.}

\newcommand{\hymn}{Vexílla Régis}
\newcommand{\vr}{Eripe me, Dómine}

\newcommand{\headingtext}{Passion Sunday.}
\newcommand{\maganttex}{MagnificatAntiphonPassion1.tex}

\newcommand{\latincollect}{Quaésumus, omnípotens Deus, famíliam tuam propítius réspice~:~\dag{} ut, te largiénte, regátur in córpore;~* et te servánte, custodiátur in mente. Per Dóminum nostrum.}
\newcommand{\englishcollect}{We beseech Thee, O almighty God, look mercifully upon Thy family: that by Thy bounty it may be governed in body, and by Thy keeping be guarded in mind. Through our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
%\vspace{-3ex}%
Abraham your father rejoiced that he might see My day: he saw it and was glad.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{A}
%\newcommand{\psalmclef}{c3}
\definemag{2}{D}

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 1 accent.}{Termination of 1 accent with 1 preperatory syllable.}}

\newcommand{\premagant}{%
\setgrefactor{17}
\normalsize
%\large
\greblockcustos
}

\newcommand{\magantinitialsize}{35}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{14}}

\definebenedicamusdomino{lent}{2}
\input{../vespersmagnificat}
