% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Hortámur vos, ne in vácuum grátiam Dei} recipi\textbf{á}\-tis.~\dag{} Ait enim~: Témpore accépto \emph{exau}\textbf{dí}\-vi te,~* et in die salútis ad\textbf{jú}vi te.}
\newcommand{\chaptertranslation}{Brethren: We exhort you that you receive not the grace of God in vain, For He saith: In an accepted time have I heard thee, and in the day of salvation have I helped thee.}

\newcommand{\hymn}{Audi, benígne Cónditor}
\newcommand{\vr}{Angelis súis}

\newcommand{\headingtext}{1st Sunday of Lent.}
\newcommand{\maganttex}{MagnificatAntiphonLent1.tex}

\newcommand{\latincollect}{Deus, qui Ecclésiam tuam ánnua Quadragesimáli observatióne puríficas~:~\dag{} præsta famíliæ tuæ~; ut quod a te obtinére abstinéndo nítitur,~* hoc bonis opéribus exsequátur. Per Dóminum nostrum.}
\newcommand{\englishcollect}{O God, who dost purify Thy Church by the yearly observance of Lent: grant to Thy household, that what we strive to obtain from Thee by abstinence, we may achieve by good works. Through our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
%\vspace{-3ex}%
Behold now is the acceptable time, behold now is the day of salvation: let us therefore exhibit ourselves as the ministers of God, in much patience, in fastings, in watchings, and in charity unfeigned.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{E}
\def\psalmclef{c3}
\definemag{8}{G*}
\let\psalmclef=\undefined

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 1 accent.}{Termination of 1 accent with 2 preparatory syllables.}}

\newcommand{\premagant}{%
%\normalsize
\large%\greblockcustos
}

\newcommand{\magantinitialsize}{35}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{15}}

\input{../vespersmagnificat}
