% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% page 604 in liber (750 in pdf)

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Hoc enim sentíte in vobis quod et in Christo Jesu~: qui cum in forma Dei esset, non rapínam arbitrátus est esse se æquálem} \textbf{De}\-o~:~\dag{} sed semetípsum exinanívit, formam servi accípiens, in similitúdinem hó\emph{minum} \textbf{fa}\-ctus,~* et hábitu invéntus ut \textbf{ho}mo.}
\newcommand{\chaptertranslation}{Brethren: Let this mind be in you which was also in Christ Jesus: who being in the form of God, thought it not robbery to be equal with God; but emptied Himself, taking the form of a servant, being made in the likeness of men, and in habit found as a man.}

\newcommand{\hymn}{Vexílla Régis}
\newcommand{\vr}{Eripe me, Dómine}

\newcommand{\headingtext}{Palm Sunday.}
\newcommand{\maganttex}{MagnificatAntiphonPassion2.tex}

\newcommand{\latincollect}{Omnípotens sempitérne Deus, qui humáno géneri, ad imitándum humilitátis exémplum, Salvatórem nostrum carnem súmere, et crucem subíre fecísti~:~\dag{} concéde propítius; ut et patiéntiæ ipsíus habére documénta,~* et resurrectiónis consórtia mereámur. Per eúmdem Dóminum nostrum.}
\newcommand{\englishcollect}{O Almighty and everlasting God, who didst cause our Saviour to take upon Him our flesh and to undergo the cross, for an example of humility to be imitated by mankind: mercifully grant that we may deserve to possess not only the lesson of His patience, but also the fellowship of His Resurrection. Through the same our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
%\vspace{-3ex}%
For it is written: I will strike the Shepherd, and the sheep of the flock shall be dispersed; but after I shall be risen again, I will go before you into Galilee: there you shall see me, saith the Lord.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{S}
%\newcommand{\psalmclef}{c3}
\definemag{8}{G*}

%\newcommand{\magmedianttermination}{\medianttermination{Mediant of 1 accent.}{Termination of 1 accent with 2 preparatory syllables.}}

\newcommand{\premagant}{%
\setgrefactor{15}
\normalsize
%\large
%\greblockcustos
}

\newcommand{\magantinitialsize}{35}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{15}}

\definebenedicamusdomino{lent}{2}
\input{../vespersmagnificat}
