% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Si linguis hóminum loquar, et} Ange\textbf{ló}\-rum,~\dag{} caritátem au\emph{tem non} \textbf{há}\-be\-am,~* factus sum velut æs sonans, aut cýmbalum \textbf{tín}niens.}
\newcommand{\chaptertranslation}{Brethren: If I speak with the tongues of men and of Angels, and have not charity, I am become as sounding brass, or a tinkling cymbal.}

\newcommand{\hymn}{Lúcis Creátor}
\newcommand{\vr}{Dirigátur}

\newcommand{\headingtext}{Quinquagesima.}
\newcommand{\maganttex}{MagnificatAntiphonQuinquagesima.tex}

\newcommand{\latincollect}{Preces nostras, quaésumus Dómine, cleménter exáudi~:~\dag{} atque a peccatórum vínculis absolútos,~* ab omni nos adversitáte custódi. Per Dóminum nostrum.}
\newcommand{\englishcollect}{Mercifully hear our prayers, we beseech Thee, O Lord: and releasing us from the fetters of our sins, guard us from every adversity. Through our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
\vspace{-3ex}%
And Jesus standing, commanded the blind man to be brought to Him, and He said to him: What wilt thou that I do to thee? Lord, that I may see. And Jesus said to him: Receive thy sight; thy faith hath made thee whole. And immediately he saw, and followed Him, glorifying God.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{S}
\definemag{1}{D}

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 2 accents.}{Termination of 1 accent with 2 preperatory syllables.}}

\newcommand{\premagant}{%
%\normalsize
\large%\greblockcustos
}

\newcommand{\magantinitialsize}{35}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{14}}

\input{../vespersmagnificat}
