% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% page 564 in liber (710 in pdf)

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Scriptum est quóniam Abraham duos fílios hábuit~: unum de ancílla, et unum de} \textbf{lí}\-be\-ra~:~\dag{} sed qui de ancílla, secúndum carnem natus est~: qui autem de líbera, per repro\emph{missi}\textbf{ó}\-nem~:~* quæ sunt per allegoríam \textbf{di}cta.}
\newcommand{\chaptertranslation}{Brethren: It is written that Abraham had two sons; the one by a bondwoman, and the other by a free woman.  But he who was of the bondwoman was born according to the flesh; but he of the free woman was by promise; which things are said by an allegory.}

\newcommand{\hymn}{Audi, benígne Cónditor}
\newcommand{\vr}{Angelis súis}

\newcommand{\headingtext}{4th Sunday of Lent.}
\newcommand{\maganttex}{MagnificatAntiphonLent4.tex}

\newcommand{\latincollect}{Concéde, quaésumus omnípotens Deus~:~\dag{} ut, qui ex mérito nostræ actiónis afflígimur,~* tuæ grátiæ consolatióne respirémus. Per Dóminum nostrum.}
\newcommand{\englishcollect}{Grant, we beseech Thee, almighty God, that we who are justly afflicted for our deeds, may be relieved by the consolation of Thy grace. Through our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
%\vspace{-3ex}%
Jesus therefore went up on a mountain, and there He sat with His disciples.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{S}
%\newcommand{\psalmclef}{c3}
\definemag{1}{g}

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 2 accents.}{Termination of 1 accent with 2 preparatory syllables.}}

\newcommand{\premagant}{%
\setgrefactor{16}
\normalsize
%\large
%\greblockcustos
}

\newcommand{\magantinitialsize}{35}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{15}}

\input{../vespersmagnificat}
