% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Libénter suffértis insipiéntes, cum sitis ipsi} sapi\-\textbf{én}\-tes~:~\dag{} sustinétis enim si quis vos in servitútem rédigit, si quis dévorat, si quis áccipit, si \emph{quis ex}\textbf{tól}\-li\-tur,~* si quis in fáciem vos \textbf{cæ}dit.}
\newcommand{\chaptertranslation}{Brethren: You gladly suffer the foolish: whereas yourselves are wise.  For you suffer if a man bring you into bondage, if a man devour you, if a man take from you, if a man be lifted up, if a man strike you in the face.}

\newcommand{\hymn}{Lúcis Creátor}
\newcommand{\vr}{Dirigátur}

\newcommand{\headingtext}{Sexagesima.}
\newcommand{\maganttex}{MagnificatAntiphonSexagesima.tex}

\newcommand{\latincollect}{Deus, qui cónspicis quia ex nulla nostra actióne confídimus~:~\dag{} concéde propítius; ut contra advérsa ómnia,~* Doctóris géntium protectióne muniámur. Per Dóminum nostrum.}
\newcommand{\englishcollect}{O God, who seest that we put not our trust in anything that we do: mercifully grant, that by the protection of the Doctor of the Gentiles we may be defended against all adversities. Through our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
%\vspace{-3ex}%
To you it is given to know the mystery of the kingdom of God, but to the rest, in parables, said Jesus to His disciples.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{V}
\definemag{6}{F}

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 1 accent with 1 preperatory syllable.}{Termination of 1 accent with 2 preperatory syllables.}}

\newcommand{\premagant}{%
%\normalsize
\large%\greblockcustos
}

\newcommand{\magantinitialsize}{35}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{16}}

\input{../vespersmagnificat}
