% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Estóte imitatóres Dei, sicut fílii} ca\textbf{rís}\-si\-mi~:~\dag{} et ambuláte in dilectióne, sicut et Christus diléxit nos, et trádidit semetíp\emph{sum pro} \textbf{no}\-bis,~* oblatiónem et hóstiam Deo in odórem suavi\textbf{tá}tis.}
\newcommand{\chaptertranslation}{Brethren: Be ye followers of God, as most dear children: and walk in love, as Christ also hath loved us and hath delivered Himself for us, an oblation and a sacrifice to God for an odour of sweetness.}

\newcommand{\hymn}{Audi, benígne Cónditor}
\newcommand{\vr}{Angelis súis}

\newcommand{\headingtext}{3nd Sunday of Lent.}
\newcommand{\maganttex}{MagnificatAntiphonLent3.tex}

\newcommand{\latincollect}{Quaésumus omnípotens Deus, vota humílium réspice~:~\gredagger{} atque ad defensiónem nostram,~* déxteram tuæ majestátis exténde. Per Dóminum nostrum.}
\newcommand{\englishcollect}{We beseech Thee, O almighty God, look upon the desires of the humble: and stretch forth the right hand of Thy Majesty to be our defence. Through our Lord.}

\newcommand{\englishmagantiphon}{%
%do this negative vspace if the last line on the antiphon gabc extends to the end
\vspace{-3ex}%
A certain woman from the crowd, lifting up her voice, said to Him: Blessed is the womb that bore thee and the paps that gave Thee suck. But Jesus said to her: Yea, rather, blessed are they who hear the word of God and keep it.}

\def\magsolemn{F}
\def\magoneline{T}
\newcommand{\magantinitial}{E}
\newcommand{\psalmclef}{c3}
\definemag{8}{G}

\newcommand{\magmedianttermination}{\medianttermination{Mediant of 1 accent.}{Termination of 1 accent with 2 preperatory syllables.}}

\newcommand{\premagant}{%
%\normalsize
\large%\greblockcustos
}

\newcommand{\magantinitialsize}{35}

\newcommand{\pretranslation}{%
%\bigskip
%\vspace{-4ex}
}

\newcommand{\premagverses}{\normalsize
%\greblockcustos
\setgrefactor{15}}

\input{../vespersmagnificat}
