\newcommand{\antonetex}{an--simeon_justus--solesmes}
\newcommand{\antoneinitial}{S}
\newcommand{\antonetranslation}{Simeon, just and devout, waited for the redemption of Israël, and the Holy Ghost was upon him.}
\definepsalm{1}{109}{3}{b}

\newcommand{\anttwotex}{an--responsum_accepit--solesmes}
\newcommand{\anttwoinitial}{R}
\newcommand{\anttwotranslation}{Simeon received an answer from the Holy Ghost, that he should not see death before he had seen the Christ of the Lord.}
\definepsalm{2}{112}{7}{a}

\newcommand{\antthreetex}{an--accipiens_simeon--solesmes}
\newcommand{\antthreeinitial}{A}
\newcommand{\antthreetranslation}{Taking the Child in his arms, Simeon gave thanks and blessed the Lord.}
\definepsalm{3}{121}{3}{b}

\newcommand{\antfourtex}{an--lumen_ad_revelationem_c4_clef--solesmes}
\newcommand{\antfourinitial}{L}
\newcommand{\antfourtranslation}{A light to the revelation of the gentiles, and the glory of thy people Israël.}
\definepsalm{4}{126}{8}{c}

\newcommand{\antfivetex}{an--obtulerunt_pro_eo--solesmes}
\newcommand{\antfiveinitial}{O}
\newcommand{\antfivetranslation}{They offered for him to the Lord, a pair of turtle doves, or two young pigeons.}
\definepsalm{5}{147}{8}{G}

\newcommand{\chaptertext}{\dropcap{latin}{Ecce ego mitto Angelum meum, en præparábit viam ante fáciem} \textbf{me}\-am.~\gredagger{} Et statim véniet ad templum sanctum suum Dominátor, \emph{quem vos} \textbf{quǽ}\-ri\-tis,~* et Angelus testaménti, quem vos \textbf{vul}\-tis.}
\newcommand{\chaptertranslation}{Behold I send my Angel, and he shall prepare the way before my face; and presently the Lord, whom you seek, and the Angel of the testament, whom you desire, shall come to his temple.}

% hymn Ave Maris Stella
\newcommand{\hymnlinetwo}{1.}
\newcommand{\hymntex}{Hymn-AveMarisStella}
\newcommand{\hymninitial}{A}
\newcommand{\hymntranslation}{
\item Hail, thou star of ocean,
Portal of the sky,
Ever-Virgin Mother,
Of the Lord most High.

\item Oh! by Gabriel's Ave
Uttered long ago
Eva's name reversing
Peace confirm below.

\item Break the captive's fetters,
Light on blindness pour
Chase all evils from us,
Every bliss implore.

\item Show thyself a Mother,
Offer Him our sighs,
Who for us incarnate
Did not thee despise.

\item Virgin all excelling,
Passing meek and lowly,
Freed from guilt, preserve us
Blameless chaste and holy.

\item Still as on we journey
Help our weak endeavour
Till we gaze on Jesus
And rejoice for ever.

\item Father, Son, and Spirit,
Three in One confessing.
Give we equal glory,
Equal praise and blessing.
Amen.%\grechangestaffsize{15}
}

\newcommand{\vrtex}{vrResponsumAccepit}
\newcommand{\vtranslation}{Simeon received an answer from the Holy Ghost.}
\newcommand{\rtranslation}{That he should not see death before he had seen the Christ of the Lord.}

\def\magsolemn{T}

\newcommand{\collect}{Omnípotens sempitérne Deus, majestátem tuam súpplices exorámus~:~\dag{} ut sicut unigénitus Fílius tuus hodiérna die cum nostræ carnis substántia in templo est præsentátus;~* ita nos fácias purificátis tibi méntibus præsentári. Per eúmdem Dóminum.}
\newcommand{\collecttranslation}{Almighty and everliving God, we humbly beseech thy Majesty, that as Thine Only-begotten Son was this day presented in the temple in substance of our flesh, so we may be presented unto Thee with pure and clean hearts. Through the same.}
