% !TEX TS-program = lualatex
% !TEX encoding = UTF-8

% This is a simple template for a LuaLaTeX document using gregorio scores.

\documentclass[letterpaper,12pt]{article} % use larger type; default would be 10pt
\usepackage{../definepsalms}
\sloppy

\newcommand{\heading}{Feast of Our Lord Jesus Christ, King.}

\newcommand{\predeusinadjutorium}{\smallskip
\large
\setgrefactor{15}
}
\def\printsolemnorfestaltone{T}
\def\deusinadjutoriumsolemn{T}

\newcommand{\preantone}{\setgrefactor{15}
\large
}
\newcommand{\antoneinitialsize}{33}
\newcommand{\antonetex}{Ant1-Pacificus}
\newcommand{\antoneinitial}{P}
\newcommand{\antonetranslation}{He shall be called the Peaceful One, and His throne shall be established for ever.}
\definepsalm{1}{109}{8}{G}
\newcommand{\prepsalmone}{%
\vspace{-1.5ex}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preanttwo}{\setgrefactor{17}
\large
}
\newcommand{\anttwoinitialsize}{40}
\newcommand{\anttwotex}{Ant2-RegnumEjus}
\newcommand{\anttwoinitial}{R}
\newcommand{\anttwotranslation}{His kingdom is a kingdom of all ages, and all kings shall serve and obey him.}
\def\psalmclef{2}
\definepsalm{2}{110}{8}{c}
\let\psalmclef=\undefined
\newcommand{\prepsalmtwo}{%
\normalsize
\greblockcustos
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantthree}{\setgrefactor{17}
\large
}
\newcommand{\antthreeinitialsize}{40}
\newcommand{\antthreetex}{Ant3-EcceVirOriens}
\newcommand{\antthreeinitial}{E}
\newcommand{\antthreetranslation}{Behold a Man, the Daystar is His name: He shall sit and rule, and shall speak peace unto the Gentiles.}
\definepsalm{3}{111}{7}{a}
\newcommand{\prepsalmthree}{%
\normalsize
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfour}{\setgrefactor{17}
\large
}
\newcommand{\antfourinitialsize}{40}
\newcommand{\antfourtex}{Ant4-Dominus}
\newcommand{\antfourinitial}{D}
\newcommand{\antfourtranslation}{The Lord is our Judge, the Lord is our Lawgiver; the Lord is our King, He will save us.}
\definepsalm{4}{112}{3}{a}
\newcommand{\prepsalmfour}{%
%\vspace{-1ex}
%\setgrefactor{15}
\normalsize
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\preantfive}{\setgrefactor{17}
\greblockcustos
\large
}
\newcommand{\antfiveinitialsize}{40}
\newcommand{\antfivetex}{Ant5-EcceDediTe}
\newcommand{\antfiveinitial}{E}
\newcommand{\antfivetranslation}{Behold I have given thee for a light of the Gentiles, that thou mayest be my salvation unto the ends of the earth.}
\definepsalm{5}{116}{8}{G}
\newcommand{\prepsalmfive}{%
%\setgrefactor{15}%
\normalsize%
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\chapter}{\dropcap{latin}{Fratres~: Grátias ágimus Deo Patri, qui dignos nos fecit in partem sortis sanctórum in} \textbf{lú}\-mi\-ne~:~\gredagger{} qui erípuit nos de potestáte \emph{te\-ne}\-\textbf{brá}\-rum,~* et tránstulit in regnum Fílii dilectiónis \textbf{su}\-æ.}
\newcommand{\chaptertranslation}{Brethren: We give thanks to God the Father, who hath made us worthy to be partakers of the lot of the saints in light, who hath delivered us from the power of darkness, and hath translated us into the kingdom of the Son of His love.}

\newcommand{\prehymn}{\normalsize
\setgrefactor{15}
}
\newcommand{\hymnlinetwo}{1.}
\newcommand{\hymntex}{Hymn-TeSaeculorumPrincipem}
\newcommand{\hymninitial}{T}
\newcommand{\hymntranslation}{
\item Thee, Christ, the Angels' Lord we sing,
Thee, Christ, of all the nations King;
Sole Lord and Judge, whose will doth bind
The hearts and minds of all mankind.

\item Through evil crowds cry once again
With frenzied will, ``Christ shall not reign,''
Yet our exulting voices sing,
And hail Thee, universal King.

\item O Christ, the Prince of Peace, recall
All rebel wills to own Thy thrall;
And let Thy love lead back and keep
Within one fold Thy scattered sheep.

\item For this, upon the bloodstained Tree,
Thou spreadst Thine arms unweariedly,
And show'st Thine Heart to our amaze
With spear transfixed, with love ablaze.

\item For this on Altar Thou dost bide,
In forms of wine and feast dost hide,
That from that pierced breast may flow
Salvation's stream on us below.

\item The rulers of the nations all
Shall at Thy feet adoring fall,
All judges magnify Thy name,
All laws and arts show forth Thy fame.

\item Let kingly crowns more glorious shine
When consecrated, Lord, as Thine:
Place Thou our land and homes today
Beneath Thy mild and gracious sway.

\item O Jesus, praise to Thee we yield,
Who dost Thy guiding sceptre wield,
With Father and with Holy Ghost,
Reigning for aye o'er heaven's host.  Amen.
}

\newcommand{\vrtex}{vr}
\newcommand{\vtranslation}{His dominion shall be increased.}
\newcommand{\rtranslation}{And of peace there shall be no end.}

\newcommand{\pagebreakbeforemagnificat}{T}
\newcommand{\premag}{
\large
\setgrefactor{17}
}
%\newcommand{\premagtwo}{
%\setgrefactor{16}
%}
\newcommand{\magfontsize}{38}
\newcommand{\magantinitial}{H}
\newcommand{\maganttranslation}{He hath on His garment and on His thigh written: King of kings and Lord of lords.  To Him be glory and empire for ever and ever.}
\def\magsolemn{T}
\def\magoneline{T}
\definemag{7}{a}

\newcommand{\premagverses}{\greblockcustos\setgrefactor{14}
\normalsize
}


\newcommand{\collect}{Omnípotens sempitérne Deus, qui in dilécto Fílio tuo, universórum Rege, ómnia instauráre voluísti~:~† concéde propítius; ut cunctæ famíliæ Géntium, peccáti vúlnere disgregátæ,~* ejus suavíssimo subdántur império~: Qui tecum vivit et regnat.}
\newcommand{\collecttranslation}{Almighty and everlasting God, who in Thy beloved Son, the King of the whole world, hast willed to restore all things, mercifully grant that all the families of nations now kept apart by the wound of sin, may be brought under the sweet yoke of His rule: Who with Thee liveth and reigneth.}

%\def\benedicamusdominogrefactor{14}
\definebenedicamusdomino{1}{2}

\input{../fullvespers}
